### 2012-09-04 paper.tex
Outline of the paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Neuroimage-like layout
\documentclass[5p]{elsarticle}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{bm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}
\usepackage[breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage[table]{xcolor}

\definecolor{deep_blue}{rgb}{0,.2,.5}
\definecolor{dark_blue}{rgb}{0,.15,.5}

\hypersetup{pdftex,  % needed for pdflatex
  breaklinks=true,  % so long urls are correctly broken across lines
  colorlinks=true,
  linkcolor=dark_blue,
  citecolor=deep_blue,
  }

% Float parameters, for more full pages.
\renewcommand{\topfraction}{0.9}        % max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}     % max fraction of floats at bottom
\renewcommand{\textfraction}{0.07}      % allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.6}  % require fuller float pages
%    % N.B.: floatpagefraction MUST be less than topfraction !!

\def\B#1{\mathbf{#1}}
%\def\B#1{\bm{#1}}
\def\trans{^\mathsf{T}}
% A compact fraction
\def\slantfrac#1#2{\kern.1em^{#1}\kern-.1em/\kern-.1em_{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%\title{Comparing Connectomes Between Populations}
\title{Learning and comparing functional connectomes between populations}

\author[parietal,unicog,cea]{Ga\"el Varoquaux\corref{corresponding}}
\author[child_institute]{Cameron Craddock}

\cortext[corresponding]{Corresponding author}

\address[parietal]{Parietal project-team, INRIA Saclay-\^ile de France}
\address[unicog]{INSERM, U992}
\address[cea]{CEA/Neurospin b\^at 145, 91191 Gif-Sur-Yvette}
\address[child_institute]{Child Institute, New York}

\begin{abstract}
    We are the champion... of the world
\end{abstract}

\begin{keyword}
    Functional connectivity, connectome, group study, effective
    connectivity
\end{keyword}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sloppy % Fed up with messed-up line breaks
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Estimating functional connectomes}

\subsection{Defining regions}

\subsection{Estimating connections}

\section{Comparing connections}

\subsection{Mass-univariate approaches}

\subsection{Modeling between-connection dependences}

\section{Comparing Network Summary Statistics}

\section{Predictive Modeling}

\section{Functional and effective connectivity}

\subsection{From correlations to structural equation modeling}

\cite{mcintosh1994}

\subsection{Matching model complexity to data}

Diatribe: all model are wrong, but some are useful

Setting the cursor between bio-physical models

\cite{mcintosh2010}

\section{Conclusion}

{
%\clearpage
\section*{References} \small \bibliographystyle{elsarticle-num-names}
\bibliography{biblio} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2012-09-04 paper.tex
Take notes to fill in outline

@@
     We are the champion... of the world
+
+    Scope: rest and task-based studies. But focusing on fMRI.
 \end{abstract}
@@
     Functional connectivity, connectome, group study, effective
-    connectivity
+    connectivity, fMRI, resting-state
 \end{keyword}
@@
 
+Review paper giving technical guidelines.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%------------------------------------------------------------------------------
 \subsection{Defining regions}
 
+Different strategies: 
+dense/sparse: covering a large fraction of the
+brain or not, hard vs soft boundaries.
+
+\paragraph{Regions from atlases}
+
+AAL, Harvard-oxford
+
+\paragraph{Defining regions from the literature}
+Meta-analysis
+
+\paragraph{FMRI-based function definition}
+Distinction between activation and rest.
+Activation: thresholding GLM maps, or using spheres around the activation
+peak.
+Rest: ICA-based approaches \cite{kiviniemi2009} XXX: cite Grecius paper.
+\cite{varoquaux2011}
+
+%------------------------------------------------------------------------------
 \subsection{Estimating connections}
+
+% Disclaimer: focus on correlation/second order statistics?
+
+\paragraph{Signal extraction}
+
+Once again separate task from rest
+
+Task: beta time-series, and more recent stuff, \emph{e.g.} by Mumford and
+Poldrack.
+
+Rest: importance of confounds. Filtering + and detrending.
+
+\paragraph{Correlation and partial correlations}
+
+Correlation, shrinkage of correlation, partial correlation, sparse iCov.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%------------------------------------------------------------------------------
 \subsection{Mass-univariate approaches}
 
+%------------------------------------------------------------------------------
 \subsection{Modeling between-connection dependences}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Predictive Modeling}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%------------------------------------------------------------------------------
 \subsection{From correlations to structural equation modeling}
@@
 
+%------------------------------------------------------------------------------
 \subsection{Matching model complexity to data}
@@
 \cite{mcintosh2010}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2012-09-04 paper.tex
More iteration

@@
 
-AAL, Harvard-oxford
+AAL \cite{tzourio-mazoyer2002a}, Harvard-oxford, sulci-based atlas.
+Personal bias against the AAL.
 
@@
 
+FMRI signals contributing to functional connectivity
+have been found to lie in frequencies below 0.1 Hz \cite{cordes2000}
+XXX: but cite recent work that shows that there is info at higher
+frequency.
+
 \paragraph{Correlation and partial correlations}
 
-Correlation, shrinkage of correlation, partial correlation, sparse iCov.
+Correlation, shrinkage of correlation \cite{ledoit2004,varoquaux2012},
+
+Remark: difference between covariance and correlation matrix.
+
+partial correlation, sparse iCov. \cite{smith2011,varoquaux2010b}.
+
+Give intuition on partial correlation/inverse covariance.
+
+Variety
+of estimation strategies for sparse iCov, that have an impact on the
+resulting network \cite{varoquaux2012}\footnote{Better estimation
+algorithm is recent Honorio paper.}. Discuss setting the regularization
+parameter.
 
@@
 
+Boils down to a standard linear model => t-tests and co.
+Stress that to have Gaussian-distributed correlations, a Fisher Z
+transform is required.
+
+Multiple comparison problem is quite an issue (scales a $p^2$) =>
+permutation and max-T approach XXX: cite Ge
+"resampling-based multiple testing for microarray data analysis", and
+Nichols multiple comparison paper.
+
 %------------------------------------------------------------------------------
 \subsection{Modeling between-connection dependences}
+
+Show that correlations co-fluctuation with images.
+
+Ad-hoc model: network-based statistics \cite{zalesky2010}
+
+Discuss the 'residual' strategy?
+\cite{varoquaux2010b}
 
@@
 \section{Comparing Network Summary Statistics}
+
+Small world networks, transport properties, resilient...
+
+Warning note that correlation matrices have long-tailed degree
+distribution by definition (cite recent Bullmore paper showing that).
 
@@
 \cite{mcintosh1994}
+\cite{marrelec2007}
+\cite{marrelec2009}
 
@@
 
-Setting the cursor between bio-physical models
+Setting the cursor between complex models based on a bio-physical
+description, and simple phenomenological models such as correlation
+matrices.
 

### 2012-09-05 paper.tex
Iterate

@@
 dense/sparse: covering a large fraction of the
-brain or not, hard vs soft boundaries.
+brain or not == tradeoff between functional specificity and covering the
+full brain
+, hard vs soft boundaries.
 
@@
 AAL \cite{tzourio-mazoyer2002a}, Harvard-oxford, sulci-based atlas.
-Personal bias against the AAL.
+Personal bias against the AAL, but note that it is widely used because of
+SPM toolbox.
 
@@
 peak.
-Rest: ICA-based approaches \cite{kiviniemi2009} XXX: cite Grecius paper.
+Rest: ICA-based approaches \cite{kiviniemi2009} \cite{shirer2012}
 \cite{varoquaux2011}
+
+Clustering approaches, \cite{craddock2011}.
 
@@
 
-Rest: importance of confounds. Filtering + and detrending.
+Rest: importance of confounds. Filtering + and detrending. Importance of
+preprocessing.
+Compcorr \cite{behzadi2007}
+\cite{chai2011}
 
@@
 Give intuition on partial correlation/inverse covariance.
+
+Remark that partial correlations consistently have no negative values.
 

### 2012-09-09 paper.tex
Iterate
added a few lines of text

@@
 \author[parietal,unicog,cea]{Ga\"el Varoquaux\corref{corresponding}}
-\author[child_institute]{Cameron Craddock}
+\author[cmi,nki]{R. Cameron Craddock}
 
@@
 \address[cea]{CEA/Neurospin b\^at 145, 91191 Gif-Sur-Yvette}
-\address[child_institute]{Child Institute, New York}
+\address[cmi]{Child Mind Institute, New York, New York}
+\address[nki]{Nathan Kline Institute for Psychiatric Research, Orangeburg, New York}
 
@@
 full brain
-, hard vs soft boundaries.
+, hard vs soft boundaries (spatial regression?).
 
@@
 \paragraph{Defining regions from the literature}
-Meta-analysis
+Meta-analysis \cite{dosenbach}, DMN/TPN ROIs (Cameron, who is that guy?)
 
@@
 peak.
+
 Rest: ICA-based approaches \cite{kiviniemi2009} \cite{shirer2012}
-\cite{varoquaux2011}
+\cite{varoquaux2011} \cite{yeo}, cite Power?
+Maybe use the ICA from the Smith 2009 paper
 
-Clustering approaches, \cite{craddock2011}.
+Clustering approaches, \cite{craddock2011}, \cite{bellec}, \cite{flandin}, \cite{poline}, \cite{thirion}
 
@@
 % Disclaimer: focus on correlation/second order statistics?
+Mutual information? Entropy correlation? MI as measure of integration (Marralec)
 
@@
 
-Once again separate task from rest
+Once again separate task from rest (explain the difference between
+\emph{ongoing} and \emph{evoked} activity at some point (intro?)
 
@@
 \cite{chai2011}
+power, van dijk
+\cite{satterthwaite2012}
 
@@
 XXX: but cite recent work that shows that there is info at higher
-frequency.
+frequency.  Regressing out task??
 
@@
 
+Family (Cameron, is that the correct name?) FWE?
+
 %------------------------------------------------------------------------------
@@
 
-Show that correlations co-fluctuation with images.
+Show that correlations co-fluctuation with images, spatial correlations between correlations.
 
@@
 \section{Predictive Modeling}
+craddock 2009, Dosenbach 2010, lord 2011, deshpande,
+
+1. importance of interpretation!
+2. the need for feature extraction
+3. the need for feature selection
+4. setting parameters.
+5. different methods have different interpretations
+
+\emph{ --- CC text from TICS paper, do not use without modification!}
+Multivariate Prediction Analysis. When applied to the study of intrinsic activity, the goal of discovery
+science is to identify models that relate measures of that activity (such as iFC) to phenotypic variables.
+Prediction analysis provides a means for measuring how well these models generalize to independent data.
+This is complementary to inferential statistics, which measure the likelihood of such relationships
+arising by chance. In the prediction analysis framework, a model relating iFC to a phenotype is learned 
+from a training dataset. This model is then applied to an independent test dataset to predict phenotypes.
+The resultant predictions are compared to the true phenotypes to estimate how well the model generalizes
+to the tese dataset. Thus, prediction analysis provides a natural framework for evaluating biomarkers [21],
+performing real-time fMRI [88], and evaluating experimental tradeoffs [89].
+
+Prediction analysis has been applied to functional neuroimaging data since the early 90’s [90], and more
+recently to IFC data [91]. Most, if not all, analysis methods can be applied in a predictive modeling
+framework but the majority of methods that have been applied to iFC are multivariate classification and
+regression methods (referred to as MVPA; multivariate prediction analysis). Multivariate methods are more
+sensitive to distributed patterns of iFC than their univariate counterparts. Additionally they provide a
+means for evaluating the significance of an entire pattern using a single statistic, obviating the need
+to correct for multiple comparisons.
+
+Although there are many circumstances in which high prediction accuracy is the ultimate goal of an
+analysis (e.g. predicting treatment outcome), in general it is desirable that the model also be
+interpretable. Identifying the iFC measures (features) that are most important to the model is
+problematic and an open issue for MVPA research. Several feature selection algorithms have been proposed
+to address this issue, but there is no consensus on which is best [21]. We note that feature selection
+methods that rely on feature-by-feature statistical tests require correction for multiple comparisons.
+
+MVPA classification has already been successfully used to identify potential iFC biomarkers of Alzheimer’s
+disease [92], major depression [93], schizophrenia [94], and autism [47], among others. MVPA
+classification and regression techniques have also been applied to identify biomarkers of age [95,96]
+and recent work has shown the utility of MVPA methods for deriving iFC models at the individual
+level [97]. An in-depth overview of the statistical pattern recognition methods underlying MVPA
+techniques can be found in [98].
+\emph{ --- END CC text from TICS paper, do not use without modification!}
 
@@
 \section{Functional and effective connectivity}
+
+Effective connectivity does not have to be causal => but a precise mathematical
+definition of the relationship => BCI workshop reports
+
+Fucntional connectivity is a statistical relationship, instead of precise mathematical
+relationship
 
@@
 
-Diatribe: all model are wrong, but some are useful
+Diatribe: all model are wrong, but some are useful => a cat is a model of a cat
 
@@
 \cite{mcintosh2010}
+
+Cross validation???
 

### 2012-12-08 paper.tex
Pretty picture
ENH: add figures

@@
 
+\begin{figure}
+\includegraphics[width=.5\linewidth]{aal_atlas.pdf}%
+\hfill%
+\includegraphics[width=.5\linewidth]{ncuts_atlas.pdf}%
+
+\includegraphics[width=.5\linewidth]{ho_atlas.pdf}%
+\hfill%
+\includegraphics[width=.5\linewidth]{sulci_atlas.pdf}%
+
+\includegraphics[width=.5\linewidth]{smith_atlas.pdf}%
+\hfill%
+\includegraphics[width=.5\linewidth]{msdl_atlas.pdf}%
+
+\caption{
+Different regions
+}
+\end{figure}
+
 %------------------------------------------------------------------------------
@@
 parameter.
+
+\begin{figure}
+\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
+{\color{black!70}\fbox{#1}\color{black}}}%
+\begin{minipage}{.66\linewidth}%
+    \includegraphics[width=\linewidth]{group_emp_cov.pdf}%
+    \raisebox{.606\linewidth}{%
+	\hspace*{-.462\linewidth}%
+	\photoframe{%
+	%\setlength\fboxsep{1pt}%
+	\colorbox{white}{%
+	\raisebox{.003\linewidth}{%
+	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_crop}}%
+	\rule{0pt}{.387\linewidth}%
+	}}%
+    }
+\end{minipage}%
+\hspace*{1pt}%
+\begin{minipage}{.32\linewidth}%
+    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds.pdf}%
+
+    \includegraphics[width=\linewidth]{group_emp_cov_global_mean.pdf}%
+\end{minipage}%
+
+\caption{
+Correlation matrices
+Note that no filter was applied. Filtering low frequencies diminishes the
+impact of some confounds that are removed ...
+}
+\end{figure}
+
+\begin{figure}
+\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
+{\color{black!70}\fbox{#1}\color{black}}}%
+\begin{minipage}{.66\linewidth}%
+    \includegraphics[width=\linewidth]{group_l21_prec.pdf}%
+    \raisebox{.606\linewidth}{%
+	\hspace*{-.462\linewidth}%
+	\photoframe{%
+	%\setlength\fboxsep{1pt}%
+	\colorbox{white}{%
+	\raisebox{.003\linewidth}{%
+	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_crop}}%
+	\rule{0pt}{.387\linewidth}%
+	}}%
+    }
+\end{minipage}%
+\hspace*{1pt}%
+\begin{minipage}{.32\linewidth}%
+    \includegraphics[width=\linewidth]{group_emp_prec.pdf}%
+
+    \includegraphics[width=\linewidth]{group_emp_prec_global_mean.pdf}%
+\end{minipage}%
+
+\caption{
+Inverse-covariance matrices
+}
+\end{figure}
 

### 2012-12-08 paper.tex
Progress on the parcellation part

@@
 
+Define what we call a functional connectome, and the term \emph{graph},
+as well as its relation with an adjacency matrix.
+
+Define a functional network
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Here we discuss strategies to infer connectomes from functional brain
+imaging data. We start with the choice of nodes \emph{i.e.} regions,
+followed by signal extraction, and the estimation of graphs.
+
 %------------------------------------------------------------------------------
@@
 
-Different strategies: 
-dense/sparse: covering a large fraction of the
-brain or not == tradeoff between functional specificity and covering the
-full brain
-, hard vs soft boundaries (spatial regression?).
+The choice of regions of interests (ROIs) that defines the nodes of the
+graphs can be very important both in the estimation of connectomes and
+for group comparison \cite{wang2009}. Unsurprisingly, simulations have
+shown that extracting signal from ROIs that did not match functional
+units would lead to incorrect graph extraction \cite{smith2011}.
+%
+Different strategies coexist. While dense parcellations approaches cover
+a large fraction of the brain \cite{achard2006, varoquaux2010c,
+wang2009}, this coverage can be traded off to focus on some specific
+regions, in favor of increased functional specificity and thus better
+differentiation across networks \cite{greicius2003, fair2009,
+varoquaux2010b, lewis2009, fransson2008, shirer2012}. In addition, while
+ROIs and most often defined as a hard selection of voxels, it is also
+possible to use a \emph{soft} definition, attributing weights as with
+probabilistic atlases, or spatial maps of functional networks extracted
+from techniques such as independent component analysis (ICA).
 
 \paragraph{Regions from atlases}
-
-AAL \cite{tzourio-mazoyer2002a}, Harvard-oxford, sulci-based atlas.
-Personal bias against the AAL, but note that it is widely used because of
-SPM toolbox.
+%
+Atlases can be used to define full-brain parcellations. The most popular
+choice is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
+benefits from an SPM toolbox. However, it suffers from major
+shortcomings; namely that \emph{i)} it was defined on a single subject
+and thus does does not reflect inter-subject variability and \emph{ii)}
+focuses on labeling large anatomical structures and does not match
+functional layout --for instance only two regions describe the medial
+part of the frontal lobe. Multi-subject probabilistic altases such as the
+Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
+sulci-based structural atlas used in \cite{varoquaux2010c} mitigate the
+first problem, and the high number of regions defined using sulci also
+somewhat circumvent the second problem (see
+fig.\,\ref{fig:parcellations}).
 
 \paragraph{Defining regions from the literature}
-Meta-analysis \cite{dosenbach}, DMN/TPN ROIs (Cameron, who is that guy?)
+%
+Regions can be defined from previous studies, informally or with
+systematic meta-analysis. This strategy is used to define the main
+resting-state networks, such as the default mode network, but may also be
+useful to study connectivity in task-specific networks
+\cite{grillon2012}. The common practice is to place balls of a given
+radius, 5 or 10\,mm, centered at the coordinates of interest. Given that
+functional networks are tightly interleaved in some parts of the cortex,
+such as the parietal lobe, care must be taken not to define too many
+regions that would overlap and lead to mixing of the signal.
 
 \paragraph{FMRI-based function definition}
-Distinction between activation and rest.
-Activation: thresholding GLM maps, or using spheres around the activation
-peak.
-
-Rest: ICA-based approaches \cite{kiviniemi2009} \cite{shirer2012}
-\cite{varoquaux2011} \cite{yeo}, cite Power?
-Maybe use the ICA from the Smith 2009 paper
-
-Clustering approaches, \cite{craddock2011}, \cite{bellec}, \cite{flandin}, \cite{poline}, \cite{thirion}
+%
+Defining regions directly from the fMRI signal brings many benefits.
+First, it can capture subject-specific functional information. Second, it
+also adapts to the signal at hand and it's limitations, such as
+EPI-specific warps or vascular and movement artifacts that are isolated
+in ICA-like approaches. The simplest approach to define task-specific
+regions is to use activation maps derived from standard GLM-based
+analysis in a task-driven study (see for instance \cite{poldrack2011}).
+Regions are extracted by thresholding the maps, or using balls around the
+activation peaks. For resting-state studies, unsupervised multivariate
+analysis techniques are necessary. Clustering approaches extract
+full-brain parcellations \cite{craddock2011, bellec2010, yeo2011,
+thirion2006}, and have been shown to extract well-known functional
+structures from rest data \cite{yeo2011}. Alternatively, decompositions
+methods, such as ICA \cite{beckmann2004}, can unmixing linear
+combinations of multiple effects and separate out multiple spatial maps
+capturing functional networks or confounding effects. At high model
+order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
+Extracting regions from these maps requires additional effort as they can
+display fragmented spatial features and structured background noise, but
+incorporating sparsity and spatial constraints in the decomposition
+techniques leads to contrasted maps that outline many different
+structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
 
@@
 \caption{
-Different regions
+Different full-brain parcellation: the AAL atlas
+\cite{tzourio-mazoyer2002a}, regions extracted by Ncuts
+\cite{craddock2011}, the Harvard-Oxford atlas, the sucli atlas used in
+\cite{varoquaux2010c}, the resting-state networks extracted in
+\cite{smith2009} by ICA, and in \cite{varoquaux2011} by sparse dictionary
+learning.
+\label{fig:parcellations}
 }
@@
 % Disclaimer: focus on correlation/second order statistics?
-Mutual information? Entropy correlation? MI as measure of integration (Marralec)
 
@@
 
+Mutual information? Entropy correlation? MI as measure of integration (Marralec)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2012-12-09 paper.tex
iterate

@@
 
+BOLD signal during rest is typically just 5-10\% lower than during task-based
+experiments (cite Raichle,  Mintun, Annu. Rev. Neurosci. 29, 449–476 (2006).)
+
 Define what we call a functional connectome, and the term \emph{graph},
@@
 Define a functional network
+
+Define on-going vs evoked activity
 
@@
 from techniques such as independent component analysis (ICA).
+
+% XXX: discuss tradeoffs in the number of regions
 
@@
 
+%{{{------ Parcellation figure -----------------------------------------------
 \begin{figure}
@@
 \hfill%
+\includegraphics[width=.5\linewidth]{ho_atlas.pdf}%
+
+\includegraphics[width=.5\linewidth]{sulci_atlas.pdf}%
+\hfill%
 \includegraphics[width=.5\linewidth]{ncuts_atlas.pdf}%
-
-\includegraphics[width=.5\linewidth]{ho_atlas.pdf}%
-\hfill%
-\includegraphics[width=.5\linewidth]{sulci_atlas.pdf}%
 
@@
 \caption{
-Different full-brain parcellation: the AAL atlas
-\cite{tzourio-mazoyer2002a}, regions extracted by Ncuts
-\cite{craddock2011}, the Harvard-Oxford atlas, the sucli atlas used in
-\cite{varoquaux2010c}, the resting-state networks extracted in
+Different full-brain parcellations: the AAL atlas
+\cite{tzourio-mazoyer2002a}, the Harvard-Oxford atlas, the sucli atlas used in
+\cite{varoquaux2010c}, regions extracted by Ncuts
+\cite{craddock2011}, the resting-state networks extracted in
 \cite{smith2009} by ICA, and in \cite{varoquaux2011} by sparse dictionary
@@
 \end{figure}
+%---------------------------------------------------------------------------}}}
 
@@
 
-% Disclaimer: focus on correlation/second order statistics?
+The concept of functional connectivity has be called elusive
+\cite{horwitz2003}: it has many mathematical instantiations although in
+essence they all strive to extract simple statistics from functional
+imaging to characterize synchrony and communication between large
+ensembles of neurons. Here we choose to focus on second order statistics
+that can be related to Gaussian models, the simplest of which being the
+correlation matrix of the signals of the different ROIs.
 
-\paragraph{Signal extraction}
-
-Once again separate task from rest (explain the difference between
-\emph{ongoing} and \emph{evoked} activity at some point (intro?)
-
-Task: beta time-series, and more recent stuff, \emph{e.g.} by Mumford and
-Poldrack.
-
-Rest: importance of confounds. Filtering + and detrending. Importance of
-preprocessing.
-Compcorr \cite{behzadi2007}
-\cite{chai2011}
-power, van dijk
-\cite{satterthwaite2012}
-
-FMRI signals contributing to functional connectivity
-have been found to lie in frequencies below 0.1 Hz \cite{cordes2000}
-XXX: but cite recent work that shows that there is info at higher
-frequency.  Regressing out task??
-
-\paragraph{Correlation and partial correlations}
-
-Correlation, shrinkage of correlation \cite{ledoit2004,varoquaux2012},
-
-Remark: difference between covariance and correlation matrix.
-
-partial correlation, sparse iCov. \cite{smith2011,varoquaux2010b}.
-
-Give intuition on partial correlation/inverse covariance.
-
-Remark that partial correlations consistently have no negative values.
-
-Variety
-of estimation strategies for sparse iCov, that have an impact on the
-resulting network \cite{varoquaux2012}\footnote{Better estimation
-algorithm is recent Honorio paper.}. Discuss setting the regularization
-parameter.
-
+%{{{------ Correlation matrices figure ---------------------------------------
 \begin{figure}
@@
 
+% XXX: need to give details on the dataset used here
+
 \caption{
-Correlation matrices
-Note that no filter was applied. Filtering low frequencies diminishes the
-impact of some confounds that are removed ...
+Correlation matrices of rest time-series extracted from the 39 main
+regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation -- 
+Upper left: regressing out CompCorr signals, as well as white matter and
+CSF average signals and movement parameters. The insert shows the
+connections restricted to the default mode network.
+% XXX: should I outline the default mode network on the main matrix?
+-- Upper right: regressing out only movement parameters. -- Lower right:
+regressing out movement parameters and global signal mean.
+% XXX: should this remark go here?
+No frequency filtering was applied here.
+\label{fig:correlation_matrices}
 }
 \end{figure}
+%---------------------------------------------------------------------------}}}
 
+% The following paragraph is convoluted: we start to say that rest is
+% from time-series, and task from beta, we go on discussing about beta
+% maps, and then we move back to rest. It might need restructuring
+
+% Horrible sentence below
+
+\paragraph{Signal extraction}
+%
+Given ROIs, the next step is to extract from them a summary measure. To
+study \emph{on-going} activity, \emph{e.g.} with rest data, signal
+extraction is performed from the EPI time series; however, to study
+\emph{evoked} activity with task-driven studies it can be beneficial to
+run a first-level analysis, enforcing specificity of the measure
+extracted to the task. With slow event-related design, task-specific
+functional connectivity can be captured in trial-to-trial fluctuations in
+the BOLD response, estimated using a GLM analysis with one regressor per
+trial \cite{grillon2012,rissman2004}. This approach, known as beta-series
+regression, has been adapted for rapid event-related designs, using
+multiple GLMs to optimize deconvolution of each trial \cite{mumford2012}.
+With rest datasets, it is important to regress out time series capturing
+movement and other sources of structured noise, to separate on-going
+activity from confounding signals. In addition to removing movement
+parameters estimated during preprocessing, removing linear trends, signal
+extracted from the white matter and the CSF \cite{chang2009}, as well as
+using the CompCor \cite{behzadi2007} procedure gives more contrasted
+correlation matrices that outline functional structures better
+(fig.\,\ref{fig:correlation_matrices}). Filtering high frequencies is
+often recommended, based on the initial observation that neural-related
+signal are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
+high-pass and low-pass filtering decrease the impact of some confounds,
+recent studies have shown that information on neural processes is present
+in the full spectrum of frequencies observed
+\cite{smith2012,vanoort2012}. Regressing out a good choice of confound
+signals is more specific than frequency filter, and in our experience
+gives more contrasted correlation matrices\footnote{Note that naive use
+of filtering can induce spurious correlations \cite{davey2012}.}.
+
+Finally, it is important to keep in mind that using resting-state to
+study on-going activity is fragile to confounds such as movement
+\cite{vandijk2012,power2011} or scanner noise, probably more so than
+activation studies as it is harder to control the specificity of the
+signal extracted. Special care must be taken in preprocessing strategies
+\cite{vandijk2010,satterthwaite2012}.
+%
+In addition, improved specificity to BOLD signal can be enforced by
+summarizing the signal in an ROI by a mean of the different voxels
+weighted by the subject-specific grey matter probabilistic segmentation,
+as output by \emph{e.g.} SPM's segmentation tool \cite{ashburner2005}, .
+
+% Regressing out task?? Skipping for lack of space
+
+\paragraph{Correlation and partial correlations}
+
+Correlation, shrinkage of correlation \cite{ledoit2004,varoquaux2012},
+
+Remark: difference between covariance and correlation matrix.
+
+partial correlation, sparse iCov. \cite{smith2011,varoquaux2010b}.
+
+Give intuition on partial correlation/inverse covariance.
+
+Remark that partial correlations consistently have no negative values.
+
+Variety
+of estimation strategies for sparse iCov, that have an impact on the
+resulting network \cite{varoquaux2012}\footnote{Better estimation
+algorithm is recent Honorio paper.}. Discuss setting the regularization
+parameter.
+
+%{{{------ Precision matrices figure -----------------------------------------
 \begin{figure}
@@
 \end{figure}
+%---------------------------------------------------------------------------}}}
+
+% XXX: should we have a summary paragraph commenting on the structure of
+% the graphs and correlation matrices extracted.
+% And also commenting on the meaning of regressions and sign of
+% correlation coefficients (the whole global mean debate).
+\cite{chai2011} (note: chai2011 used compcor)
 

### 2012-12-24 paper.tex
Iter on paper

@@
 regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation -- 
-Upper left: regressing out CompCorr signals, as well as white matter and
+Upper left: regressing out CompCor signals, as well as white matter and
 CSF average signals and movement parameters. The insert shows the
@@
 study on-going activity is fragile to confounds such as movement
-\cite{vandijk2012,power2011} or scanner noise, probably more so than
+\cite{vandijk2012,power2011} or scanner noise, and probably more so than
 activation studies as it is harder to control the specificity of the
@@
 In addition, improved specificity to BOLD signal can be enforced by
-summarizing the signal in an ROI by a mean of the different voxels
-weighted by the subject-specific grey matter probabilistic segmentation,
-as output by \emph{e.g.} SPM's segmentation tool \cite{ashburner2005}, .
+using only signal in voxels near gray-matter tissues. For this purpose,
+we suggest summarizing the signal in an ROI by a mean of the different voxels
+weighted by the subject-specific gray matter probabilistic segmentation,
+as output by \emph{e.g.} SPM's segmentation tool \cite{ashburner2005}.
 
@@
 \paragraph{Correlation and partial correlations}
+%
+Functional connectivity between the ROIs can be measured by computing the
+correlation matrix of the extracted signals. An important and often
+neglected point is that the sample correlation matrix, \emph{i.e.} the
+correlation matrix obtained by plugging the observed signal in the
+correlation matrix formula, is not the population correlation matrix,
+\emph{i.e.} the correlation matrix of the data-generating process. If the
+number of measurements was infinite, the two would coincide, however if
+this number is not large compared to the number of connection (that
+scales as the square of the number of ROIs), the sample correlation
+matrix is a poor estimate of the underlying population correlation matrix.
+In other words, the sample correlation matrix captures a lot of sampling
+noise, intrinsic randomness that arises in the estimation of correlations
+from short time series. Conclusions drawn from the sample correlation
+matrix can easily reflect this estimation error.
 
-Correlation, shrinkage of correlation \cite{ledoit2004,varoquaux2012},
+Varoquaux \emph{et al.} \cite{varoquaux2010c} and Smith \emph{et al.}
+\cite{smith2011} have shown respectively on rest fMRI and on realistic
+simulations that a good choice of correlation matrix estimator could
+recover the connectivity structure, where the sample correlation matrix
+would fail. In general, the choice of a better estimate depends on the
+settings and the end goals \cite{varoquaux2012,varoquaux2010b}, however
+the Ledoit-Wolf shrinkage estimate \cite{ledoit2004} is a simple,
+computationally-efficient, and parameter-less alternative that performs
+uniformly better than the sample correlation matrix
+\cite{varoquaux2012,varoquaux2010c} and should always be prefered.
 

### 2012-12-24 paper.tex
ENH: paragraph on covariance/correlation matrix

@@
 regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation -- 
-Upper left: regressing out CompCor signals, as well as white matter and
+\textbf{Upper left}: regressing out CompCor signals, as well as white matter and
 CSF average signals and movement parameters. The insert shows the
@@
 % XXX: should I outline the default mode network on the main matrix?
--- Upper right: regressing out only movement parameters. -- Lower right:
+-- \textbf{Upper right}: regressing out only movement parameters. -- 
+\textbf{Lower right}:
 regressing out movement parameters and global signal mean.
@@
 scales as the square of the number of ROIs), the sample correlation
-matrix is a poor estimate of the underlying population correlation matrix.
-In other words, the sample correlation matrix captures a lot of sampling
-noise, intrinsic randomness that arises in the estimation of correlations
-from short time series. Conclusions drawn from the sample correlation
-matrix can easily reflect this estimation error.
-
-Varoquaux \emph{et al.} \cite{varoquaux2010c} and Smith \emph{et al.}
-\cite{smith2011} have shown respectively on rest fMRI and on realistic
-simulations that a good choice of correlation matrix estimator could
-recover the connectivity structure, where the sample correlation matrix
-would fail. In general, the choice of a better estimate depends on the
-settings and the end goals \cite{varoquaux2012,varoquaux2010b}, however
-the Ledoit-Wolf shrinkage estimate \cite{ledoit2004} is a simple,
+matrix is a poor estimate of the underlying population correlation
+matrix. In other words, the sample correlation matrix captures a lot of
+sampling noise, intrinsic randomness that arises in the estimation of
+correlations from short time series. Conclusions drawn from the sample
+correlation matrix can easily reflect this estimation error.
+%
+Varoquaux \emph{et al.}~\cite{varoquaux2010c} and Smith \emph{et
+al.}~\cite{smith2011} have shown respectively on rest fMRI and on
+realistic simulations that a good choice of correlation matrix estimator
+could recover the connectivity structure, where the sample correlation
+matrix would fail. In general, the choice of a better estimate depends on
+the settings and the end goals \cite{varoquaux2012,varoquaux2010b},
+however the Ledoit-Wolf shrinkage estimate \cite{ledoit2004} is a simple,
 computationally-efficient, and parameter-less alternative that performs
 uniformly better than the sample correlation matrix
-\cite{varoquaux2012,varoquaux2010c} and should always be prefered.
-
-Remark: difference between covariance and correlation matrix.
-
-partial correlation, sparse iCov. \cite{smith2011,varoquaux2010b}.
-
-Give intuition on partial correlation/inverse covariance.
-
-Remark that partial correlations consistently have no negative values.
-
-Variety
-of estimation strategies for sparse iCov, that have an impact on the
-resulting network \cite{varoquaux2012}\footnote{Better estimation
-algorithm is recent Honorio paper.}. Discuss setting the regularization
-parameter.
+\cite{varoquaux2012,varoquaux2010c} and should always be preferred.
 
@@
 
-    \includegraphics[width=\linewidth]{group_emp_prec_global_mean.pdf}%
+    \includegraphics[width=\linewidth]{group_l21_prec_global_mean.pdf}%
 \end{minipage}%
@@
 \caption{
-Inverse-covariance matrices
+Inverse-covariance matrices:
+\label{fig:icov}
 }
@@
 %---------------------------------------------------------------------------}}}
+
+For the problem of recovering the functional-connectivity
+\emph{structure}, \emph{i.e.}\ finding which region is connected to
+which, sparse inverse covariance estimators have been found to be
+efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
+inverse covariance rather than correlation stems from that fact that
+standard correlation (marginal correlation) between two variables $a$ and
+$b$ also capture the effects of other variables -- strong correlation of
+$a$ and $b$ with a third variable $c$ will induce a correlation between
+$a$ and $b$. On the opposite, the inverse covariance\footnote{Covariance
+and correlation matrices differ simply by the fact that a covariance
+matrix captures the amplitude of a signal, via its variance, while a
+correlation matrix is computed on normalized signals.}
+matrix captures
+partial correlations, removing the effect of other variables
+\cite{marrelec2006a}. In the small sample limit, this removal is
+challenging from the statistical standpoint, and assumption of sparsity,
+\emph{i.e.}\ that only few variables need to be considered at a time, is
+important to estimate a good inverse covariance. Various estimation
+strategies exist for sparse inverse covariance, and have an impact on the
+resulting networks \cite{varoquaux2012,varoquaux2010c}. The
+graphical-lasso ($\ell_1$-penalized maximum-likelihood estimator)
+\cite{friedman2008} is a good general-purpose approach. In group studies,
+the $\ell_{21}$ estimator \cite{varoquaux2010c,honorio2012} is useful to
+impose a common sparsity structure across different subjects and achieve
+better recovery of this common structure. Simply put, these approaches
+are necessary because estimation noise creates a background structure
+(see Fig\,\ref{fig:icov}); however, unlike in a univariate situation, the
+parameters are not independent, and the spurious background connections
+degrade the estimation of the actual connections. The sparse estimators
+make a compromise between imposing simpler models, \emph{i.e.}\ with less
+connections, and fitting well the data. This compromise is set via a
+regularization parameter which controls the sparsity of the estimate. A
+good rule of thumb to set this parameter is via cross-validation
+\cite{varoquaux2010c}.
 
@@
 % correlation coefficients (the whole global mean debate).
-\cite{chai2011} (note: chai2011 used compcor)
+% \cite{chai2011} (note: chai2011 used compcor)
+% Remark that partial correlations consistently have no negative values.
 

### 2012-12-24 paper.tex
iter

@@
 Here we discuss strategies to infer connectomes from functional brain
-imaging data. We start with the choice of nodes \emph{i.e.} regions,
+imaging data. We start with the choice of nodes \emph{i.e.}\ regions,
 followed by signal extraction, and the estimation of graphs.
@@
 \hspace*{1pt}%
-\begin{minipage}{.32\linewidth}%
+\begin{minipage}{.327\linewidth}%
     \includegraphics[width=\linewidth]{group_emp_cov_no_confounds.pdf}%
@@
 Correlation matrices of rest time-series extracted from the 39 main
-regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation -- 
-\textbf{Upper left}: regressing out CompCor signals, as well as white matter and
+regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation with
+different choices of confound regressors -- 
+\textbf{Left}: regressing out CompCor signals, as well as white matter and
 CSF average signals and movement parameters. The insert shows the
@@
 Given ROIs, the next step is to extract from them a summary measure. To
-study \emph{on-going} activity, \emph{e.g.} with rest data, signal
+study \emph{on-going} activity, \emph{e.g.}\ with rest data, signal
 extraction is performed from the EPI time series; however, to study
@@
 weighted by the subject-specific gray matter probabilistic segmentation,
-as output by \emph{e.g.} SPM's segmentation tool \cite{ashburner2005}.
+as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
 
@@
 correlation matrix of the extracted signals. An important and often
-neglected point is that the sample correlation matrix, \emph{i.e.} the
+neglected point is that the sample correlation matrix, \emph{i.e.}\ the
 correlation matrix obtained by plugging the observed signal in the
 correlation matrix formula, is not the population correlation matrix,
-\emph{i.e.} the correlation matrix of the data-generating process. If the
+\emph{i.e.}\ the correlation matrix of the data-generating process. If the
 number of measurements was infinite, the two would coincide, however if
@@
 \hspace*{1pt}%
-\begin{minipage}{.32\linewidth}%
+\begin{minipage}{.327\linewidth}%
     \includegraphics[width=\linewidth]{group_emp_prec.pdf}%
 
-    \includegraphics[width=\linewidth]{group_l21_prec_global_mean.pdf}%
+    \includegraphics[width=\linewidth]{group_l1_prec.pdf}%
 \end{minipage}%
@@
 \caption{
-Inverse-covariance matrices:
-\label{fig:icov}
+Different inverse-covariance matrices estimates corresponding to
+Fig.\,\ref{fig:correlation_matrices} -- \textbf{Left}: group-sparse estimate
+using the $\ell_{21}$ estimator \cite{varoquaux2010c}.
+The insert shows the
+connections restricted to the default mode network. -- \textbf{Upper
+right}: non-sparse estimate: inverse of the sample correlation matrix. --
+\textbf{Lower right}: sparse estimate using the Graph Lasso
+\cite{friedman2008}.
+\label{fig:icov_estimators}
 }
@@
 %---------------------------------------------------------------------------}}}
+
+%{{{------ Regressor in precision matrix -------------------------------------
+\begin{figure}
+\includegraphics[width=.495\linewidth]{group_l21_prec_no_confounds.pdf}%
+\hspace*{1pt}%
+\includegraphics[width=.495\linewidth]{group_l21_prec_global_mean.pdf}%
+
+\caption{Different choice of confound regressors --
+\label{fig:icov_regressors}
+\textbf{Left}: regressing out only movement parameters --
+\textbf{Right}: removal of the global mean,
+instead of the white matter, CSF, and CompCor time courses. 
+}
+\end{figure}
+%---------------------------------------------------------------------------}}}
+
+% XXX: in the figures, the inserts must be commented.
+
+% XXX: idea: use the same regions as in the Fransson/Marrelec paper on
+% the role of the PCC
 

### 2012-12-25 paper.tex
Redo figures

@@
 \begin{figure}
-\includegraphics[width=.495\linewidth]{group_l21_prec_no_confounds.pdf}%
+\includegraphics[height=.482\linewidth]{group_l21_prec_no_confounds.pdf}%
 \hspace*{1pt}%
-\includegraphics[width=.495\linewidth]{group_l21_prec_global_mean.pdf}%
+\includegraphics[height=.482\linewidth]{group_l21_prec_global_mean.pdf}%
+\hspace*{1pt}%
+\includegraphics[height=.482\linewidth]{cmap.pdf}%
 
@@
 resulting networks \cite{varoquaux2012,varoquaux2010c}. The
-graphical-lasso ($\ell_1$-penalized maximum-likelihood estimator)
+Graph Lasso ($\ell_1$-penalized maximum-likelihood estimator)
 \cite{friedman2008} is a good general-purpose approach. In group studies,
@@
 are necessary because estimation noise creates a background structure
-(see Fig\,\ref{fig:icov}); however, unlike in a univariate situation, the
+(see Fig.\,\ref{fig:icov_estimators}); however, unlike in a univariate situation, the
 parameters are not independent, and the spurious background connections

### 2012-12-25 paper.tex
Iter on covariance estimation paragraph

@@
 {\color{black!70}\fbox{#1}\color{black}}}%
-\begin{minipage}{.66\linewidth}%
+\begin{minipage}{.666\linewidth}%
     \includegraphics[width=\linewidth]{group_emp_cov.pdf}%
@@
 	\raisebox{.003\linewidth}{%
-	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_crop}}%
+	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_labels}}%
 	\rule{0pt}{.387\linewidth}%
@@
 \hspace*{1pt}%
-\begin{minipage}{.327\linewidth}%
+\begin{minipage}{.33\linewidth}%
     \includegraphics[width=\linewidth]{group_emp_cov_no_confounds.pdf}%
@@
 CSF average signals and movement parameters. The insert shows the
-connections restricted to the default mode network.
-% XXX: should I outline the default mode network on the main matrix?
+connections restricted to the .
 -- \textbf{Upper right}: regressing out only movement parameters. -- 
@@
 regressing out movement parameters and global signal mean.
-% XXX: should this remark go here?
 No frequency filtering was applied here.
 \label{fig:correlation_matrices}
+When no confounding brain signals are regressed, all regions are heavily
+correlated. Regressing out common signal, in the form of well-identified
+confounds or a global mean, teases out the structure.
 }
@@
 
+%{{{------ Precision matrices figure -----------------------------------------
+\begin{figure}
+\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
+{\color{black!70}\fbox{#1}\color{black}}}%
+\begin{minipage}{.666\linewidth}%
+    \includegraphics[width=\linewidth]{group_l21_prec.pdf}%
+    \raisebox{.606\linewidth}{%
+	\hspace*{-.462\linewidth}%
+	\photoframe{%
+	%\setlength\fboxsep{1pt}%
+	\colorbox{white}{%
+	\raisebox{.003\linewidth}{%
+	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_labels}}%
+	\rule{0pt}{.387\linewidth}%
+	}}%
+    }
+\end{minipage}%
+\hspace*{1pt}%
+\begin{minipage}{.33\linewidth}%
+    \includegraphics[width=\linewidth]{group_emp_prec.pdf}%
+
+    \includegraphics[width=\linewidth]{group_l1_prec.pdf}%
+\end{minipage}%
+
+\caption{
+Different inverse-covariance matrices estimates corresponding to
+Fig.\,\ref{fig:correlation_matrices} -- \textbf{Left}: group-sparse estimate
+using the $\ell_{21}$ estimator \cite{varoquaux2010c}.
+The insert shows the
+connections restricted to the default mode network. -- \textbf{Upper
+right}: non-sparse estimate: inverse of the sample correlation matrix. --
+\textbf{Lower right}: sparse estimate using the Graph Lasso
+\cite{friedman2008}.
+\label{fig:icov_estimators}
+}
+\end{figure}
+%---------------------------------------------------------------------------}}}
+
 \paragraph{Correlation and partial correlations}
@@
 
-%{{{------ Precision matrices figure -----------------------------------------
-\begin{figure}
-\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
-{\color{black!70}\fbox{#1}\color{black}}}%
-\begin{minipage}{.66\linewidth}%
-    \includegraphics[width=\linewidth]{group_l21_prec.pdf}%
-    \raisebox{.606\linewidth}{%
-	\hspace*{-.462\linewidth}%
-	\photoframe{%
-	%\setlength\fboxsep{1pt}%
-	\colorbox{white}{%
-	\raisebox{.003\linewidth}{%
-	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_crop}}%
-	\rule{0pt}{.387\linewidth}%
-	}}%
-    }
-\end{minipage}%
-\hspace*{1pt}%
-\begin{minipage}{.327\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_prec.pdf}%
-
-    \includegraphics[width=\linewidth]{group_l1_prec.pdf}%
-\end{minipage}%
-
-\caption{
-Different inverse-covariance matrices estimates corresponding to
-Fig.\,\ref{fig:correlation_matrices} -- \textbf{Left}: group-sparse estimate
-using the $\ell_{21}$ estimator \cite{varoquaux2010c}.
-The insert shows the
-connections restricted to the default mode network. -- \textbf{Upper
-right}: non-sparse estimate: inverse of the sample correlation matrix. --
-\textbf{Lower right}: sparse estimate using the Graph Lasso
-\cite{friedman2008}.
-\label{fig:icov_estimators}
-}
-\end{figure}
-%---------------------------------------------------------------------------}}}
-
 %{{{------ Regressor in precision matrix -------------------------------------
@@
 
-\caption{Different choice of confound regressors --
+\caption{Inverse covariance matrices for different choice of
+confound regressors --
 \label{fig:icov_regressors}
@@
 %---------------------------------------------------------------------------}}}
-
-% XXX: in the figures, the inserts must be commented.
-
-% XXX: idea: use the same regions as in the Fransson/Marrelec paper on
-% the role of the PCC
 
@@
 Graph Lasso ($\ell_1$-penalized maximum-likelihood estimator)
-\cite{friedman2008} is a good general-purpose approach. In group studies,
+\cite{friedman2008} is in general a good approach for structure recovery. In group studies,
 the $\ell_{21}$ estimator \cite{varoquaux2010c,honorio2012} is useful to
@@
 
-% XXX: should we have a summary paragraph commenting on the structure of
-% the graphs and correlation matrices extracted.
-% And also commenting on the meaning of regressions and sign of
-% correlation coefficients (the whole global mean debate).
+% XXX: must comment on the estimator figure
+
+\paragraph{Network structure extracted}
+%
+The correlation matrices and inverse-covariance matrices that we extract
+contain a lot of information on the functional structure of the brain.
+First, the correlation matrix (Fig.\,\ref{fig:correlation_matrices})
+shows blocks of coactivating regions that can be interpreted as
+large-scale functional networks, such as the default mode network. Note
+the split in network is not straightforward. Different ordering of the
+nodes will reveal different networks. Indeed, because of the presence of
+hubs and interleaved networks the picture in terms of segregated networks
+is not sufficient to explain full-brain connectivity
+\cite{varoquaux2012}. The connectivity matrices, correlation matrix or
+inverse-covariance matrix, can be represented as graphs: nodes connected
+by weighted edges (inserts Fig.\,\ref{fig:correlation_matrices} and
+Fig.\,\ref{fig:icov_estimators}). The inverse-covariance matrix,
+capturing partial correlations, appears then as extracting a
+\emph{backbone} or \emph{core} of the graph. While such structure have
+been used as a way to summarize anatomical brain connectivity graphs
+\cite{hagmann2008}, here they have a clear-cut meaning with regards to
+the BOLD signal: they give the conditional independence structure between
+the regions \cite{varoquaux2012}. In other words, regions $a$ and $b$ are
+not connected if the signal that they have in common can be explained by
+a third region $c$. In this light, the choice of nuisance regressors to
+remove confounding common signal is less critical. Indeed, while with
+correlation matrices regressing out the global mean has a drastic
+(Fig.\,\ref{fig:correlation_matrices} upper right and lower right), on
+inverse covariance it only changes very slightly the resulting matrices
+(Fig.\,\ref{fig:icov_regressors}). There have been debates on whether to
+regress out certain signals, such as the global mean,  as it induces
+negative correlations \cite{murphy2009,chang2009}, and these may seem
+surprising: one network is doing the opposite of the other. However,
+correlation between two signals only takes its meaning with the
+definition of a baseline. A simple picture to explain anti-correlations
+between two regions is the presence of a third region, mediating the
+interactions. Using this third region as a baseline would amount to
+estimate partial correlations in the whole system. Using 
+inverse-covariance matrices or partial correlations to understand brain
+connectivity makes the interpretation in terms of interactions between
+brain regions easier and more robust to the choice of confounds.
+
+% XXX: where to insert this in the above paragraph: cite the
+% Fransson/Marrelec paper on the role of the PCC
+
 % \cite{chai2011} (note: chai2011 used compcor)
@@
 \section{Comparing connections}
+
+Note here that using a Ledoit-Wolf is probably a good choice for this
+application
 

### 2012-12-26 paper.tex
Iter on comparison part

@@
 inverse-covariance matrix, can be represented as graphs: nodes connected
-by weighted edges (inserts Fig.\,\ref{fig:correlation_matrices} and
+by weighted edges (inserts on Fig.\,\ref{fig:correlation_matrices} and
 Fig.\,\ref{fig:icov_estimators}). The inverse-covariance matrix,
@@
 regress out certain signals, such as the global mean,  as it induces
-negative correlations \cite{murphy2009,chang2009}, and these may seem
+negative correlations \cite{murphy2009,chang2009,fox2009}, and these may seem
 surprising: one network is doing the opposite of the other. However,
@@
 
-\section{Comparing connections}
+\section{Comparing connectivity}
 
-Note here that using a Ledoit-Wolf is probably a good choice for this
-application
+Here, we consider the problem of comparing functional connectivity across
+subjects or across conditions.
 
 %------------------------------------------------------------------------------
-\subsection{Mass-univariate approaches}
+\subsection{Detecting changing connections}
 
-Boils down to a standard linear model => t-tests and co.
-Stress that to have Gaussian-distributed correlations, a Fisher Z
-transform is required.
+First, we focus on detecting where the connectivity matrices estimated in
+the previous section differ.
+\paragraph{Mass-univariate approaches}
+%
+The most natural approach is to do a linear model on each coefficient of
+the connectivity matrices, as in \cite{lewis2009,grillon2012}.
+This approach is similar to the second-level
+analysis used in mass-univariate brain mapping, and will give rise to
+many of the well-known techniques used in such a context, such as the
+definition of second-level design, with possibly the inclusion of
+confounding effects, and statistical tests (T tests or F tests) on
+contrast vector. Importantly, in order to work with Gaussian-distributed
+correlations, it is necessary to apply a Fisher Z
+transform\footnote{See 
+\url{http://en.wikipedia.org/wiki/Fisher_transformation}
+or \cite{anderson1958}, section 4.2.3 for mathematical arguments}.
+Note that in these settings, the Ledoit-Wolf estimator \cite{ledoit2004}
+is probably a good choice to estimate the correlation matrix, as it is
+parameter-less and gives good estimation performance without imposing any
+restrictions on the data.
+%
+Correcting for multiple comparison can often severely limit statistical
+power, as the number of tests performed scales as the square of the
+number of regions used. Controlling for the false discovery rate (FDR)
+mitigates this problem. Alternatively, as the assumption underlying the
+Benjamini-Holchberg procedure for the FDR can easily be broken,
+non-parametric permutations-based approaches give reliable approaches. In
+particular, the max-T procedure
+% NEEDREF: FDR for neuroimaging data, check the spelling of BH
+is interesting to avoid the drastic Bonferroni correction when
+controlling for multiple comparison in family-wise error rate.
 
-Multiple comparison problem is quite an issue (scales a $p^2$) =>
-permutation and max-T approach XXX: cite Ge
-"resampling-based multiple testing for microarray data analysis", and
-Nichols multiple comparison paper.
+% XXX: cite Ge "resampling-based multiple testing for microarray data
+% analysis", and Nichols multiple comparison paper.
 
-Family (Cameron, is that the correct name?) FWE?
+%{{{------ Inter subject fluctuations ----------------------------------------
+\begin{figure}
+\hspace*{.5ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53.pdf}%
+\hspace*{.1ex}%
+\raisebox{.005\linewidth}{%
+    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
+    \llap{
+	\raisebox{.003\linewidth}{%
+	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
+    }%
+    \llap{
+	\raisebox{.17\linewidth}{%
+	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
+    }%
+}%
+\llap{\rlap{
+    \setlength\fboxsep{1pt}%
+    \raisebox{.16\linewidth}{%
+	\colorbox{black!10}{%
+	    \sffamily\small Covariance matrices}}%
+	}%
+    \hspace*{.993\linewidth}%
+}
 
-%------------------------------------------------------------------------------
-\subsection{Modeling between-connection dependences}
+\hspace*{.5ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53.pdf}%
+\hspace*{.1ex}%
+\raisebox{.005\linewidth}{%
+    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
+    \llap{
+	\raisebox{.003\linewidth}{%
+	    \bfseries\tiny -\!4\hspace*{-.2ex}}%
+    }%
+    \llap{
+	\raisebox{.168\linewidth}{%
+	    \bfseries\tiny 4\hspace*{.1ex}}%
+    }%
+}%
+\llap{\rlap{
+    \setlength\fboxsep{1pt}%
+    \raisebox{.16\linewidth}{%
+	\colorbox{black!10}{%
+	    \sffamily\small Z score on difference}}%
+	}%
+    \hspace*{.993\linewidth}%
+}
+
+\hspace*{.5ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub00.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub29.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub01.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub07.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub53.pdf}%
+\hspace*{.1ex}%
+\raisebox{.005\linewidth}{%
+    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
+    \llap{
+	\raisebox{.003\linewidth}{%
+	    \bfseries\tiny -\!4\hspace*{-.2ex}}%
+    }%
+    \llap{
+	\raisebox{.168\linewidth}{%
+	    \bfseries\tiny 4\hspace*{.1ex}}%
+    }%
+}%
+\llap{\rlap{
+    \setlength\fboxsep{1pt}%
+    \raisebox{.16\linewidth}{%
+	\colorbox{black!10}{%
+	    \sffamily\small Z score on residuals \scriptsize
+		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
+	}%
+    \hspace*{.993\linewidth}%
+}
+
+\caption{Inter subject fluctuations
+\label{fig:icov_regressors}
+}
+\end{figure}
+%---------------------------------------------------------------------------}}}
+
+\paragraph{Modeling between-connection dependences}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%------------------------------------------------------------------------------
 
-\section{Comparing Network Summary Statistics}
+\subsection{Comparing Network Summary Statistics}
 

### 2012-12-26 paper.tex
Iterate on paper

@@
 First, we focus on detecting where the connectivity matrices estimated in
-the previous section differ.
-\paragraph{Mass-univariate approaches}
+the previous section differ. \paragraph{Mass-univariate approaches}
 %
 The most natural approach is to do a linear model on each coefficient of
-the connectivity matrices, as in \cite{lewis2009,grillon2012}.
-This approach is similar to the second-level
-analysis used in mass-univariate brain mapping, and will give rise to
-many of the well-known techniques used in such a context, such as the
-definition of second-level design, with possibly the inclusion of
-confounding effects, and statistical tests (T tests or F tests) on
-contrast vector. Importantly, in order to work with Gaussian-distributed
-correlations, it is necessary to apply a Fisher Z
-transform\footnote{See 
-\url{http://en.wikipedia.org/wiki/Fisher_transformation}
-or \cite{anderson1958}, section 4.2.3 for mathematical arguments}.
-Note that in these settings, the Ledoit-Wolf estimator \cite{ledoit2004}
-is probably a good choice to estimate the correlation matrix, as it is
+the connectivity matrices, as in \cite{lewis2009,grillon2012}. This
+approach is similar to the second-level analysis used in mass-univariate
+brain mapping, and will give rise to many of the well-known techniques
+used in such a context, such as the definition of second-level design,
+with possibly the inclusion of confounding effects, and statistical tests
+(T tests or F tests) on contrast vector. Importantly, in order to work
+with Gaussian-distributed correlations, it is necessary to apply a Fisher
+Z transform\footnote{See
+\url{http://en.wikipedia.org/wiki/Fisher_transformation} or
+\cite{anderson1958}, section 4.2.3 for mathematical arguments}. Note that
+in these settings, the Ledoit-Wolf estimator \cite{ledoit2004} is
+probably a good choice to estimate the correlation matrix, as it is
 parameter-less and gives good estimation performance without imposing any
@@
 mitigates this problem. Alternatively, as the assumption underlying the
-Benjamini-Holchberg procedure for the FDR can easily be broken,
-non-parametric permutations-based approaches give reliable approaches. In
-particular, the max-T procedure
-% NEEDREF: FDR for neuroimaging data, check the spelling of BH
+Benjamini-Hochberg procedure \cite{benjamini1995} for the FDR can easily
+be broken, non-parametric permutations-based approaches give reliable
+approaches. In particular, the max-T procedure \cite{ge2003,nichols2001}
 is interesting to avoid the drastic Bonferroni correction when
 controlling for multiple comparison in family-wise error rate.
-
-% XXX: cite Ge "resampling-based multiple testing for microarray data
-% analysis", and Nichols multiple comparison paper.
 

### 2012-12-26 paper.tex
Iter on paper

@@
 	\colorbox{black!10}{%
-	    \sffamily\small Covariance matrices}}%
+	    \sffamily\small\textbf{a}. Correlation matrices}}%
 	}%
@@
 	\raisebox{.003\linewidth}{%
-	    \bfseries\tiny -\!4\hspace*{-.2ex}}%
+	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
     }%
@@
 	\colorbox{black!10}{%
-	    \sffamily\small Z score on difference}}%
+	    \sffamily\small\textbf{b}. Z score on difference}}%
+	}%
+    \hspace*{.993\linewidth}%
+}
+
+\hspace*{.5ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53.pdf}%
+\hspace*{.1ex}%
+\raisebox{.005\linewidth}{%
+    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
+    \llap{
+	\raisebox{.003\linewidth}{%
+	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
+    }%
+    \llap{
+	\raisebox{.17\linewidth}{%
+	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
+    }%
+}%
+\llap{\rlap{
+    \setlength\fboxsep{1pt}%
+    \raisebox{.16\linewidth}{%
+	\colorbox{black!10}{%
+	    \sffamily\small\textbf{c}. Inverse-covariance matrices}}%
+	}%
+    \hspace*{.993\linewidth}%
+}
+
+\hspace*{.5ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07.pdf}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53.pdf}%
+\hspace*{.1ex}%
+\raisebox{.005\linewidth}{%
+    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
+    \llap{
+	\raisebox{.003\linewidth}{%
+	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
+    }%
+    \llap{
+	\raisebox{.168\linewidth}{%
+	    \bfseries\tiny 4\hspace*{.1ex}}%
+    }%
+}%
+\llap{\rlap{
+    \setlength\fboxsep{1pt}%
+    \raisebox{.16\linewidth}{%
+	\colorbox{black!10}{%
+	    \sffamily\small\textbf{d}. Z score on inverse-covariance}}%
 	}%
@@
 	\colorbox{black!10}{%
-	    \sffamily\small Z score on residuals \scriptsize
+	    \sffamily\small\textbf{e}. Z score on residuals \scriptsize
 		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
@@
 
-\caption{Inter subject fluctuations
-\label{fig:icov_regressors}
-}
+\caption{Inter subject variability. Note that this is variability
+occurring in a healthy population at rest, in other words non specific
+variability -- \textbf{a}: single-subject
+correlation matrices for different subjects -- \textbf{b}:
+Corresponding Z-score (effect / standard deviation) of the difference
+between a subject and the remaining others -- \textbf{c}:
+single-subject precision matrices -- \textbf{d}: Corresponding Z-score
+for the precision matrices -- \textbf{e}:
+Corresponding Z-score for the subject residuals, as defined in 
+\cite{varoquaux2010b}.
+\label{fig:inter_subject}}
 \end{figure}
@@
 
-\paragraph{Modeling between-connection dependences}
+\paragraph{Accounting for distributed variability}
+%
+A specific challenge of connectivity analysis is that the connectivity
+between different regions tend to covary. For instance, with
+resting-state data, functional networks comprising many nodes can appear
+as more or less connected across subjects (see for instance
+Fig.\,\ref{fig:inter_subject}.a, showing variability in a control
+population at rest). In other words, non-specific variability is
+distributed accross the connectivity graph, and it is structured by the
+graph itself. This observation brings the natural question of whether
+second-level analysis should be performed on correlation matrices,
+inverse-covariance matrices, or another parametrisation that would
+disentangle effects and give unstructured (white) residuals. While
+inverse-covariance matrices show less distributed fluctuations than
+correlation matrices, they capture a lot of background noise, as partial
+correlations are intrinsically harder to estimate. Preliminary work
+\cite{varoquaux2010b} suggest to perform statistics on residuals of
+a parametrisation intermediate between correlation matrix and inverse
+covariance matrix.
 
-Show that correlations co-fluctuation with images, spatial correlations between correlations.
-
-Ad-hoc model: network-based statistics \cite{zalesky2010}
-
-Discuss the 'residual' strategy?
-\cite{varoquaux2010b}
+Taking a difference stance on distributed variability, the ``network-based
+statistics'' approach \cite{zalesky2010} draws from the hypothesis that
+if, in a second-level analysis, an effect is detected in a connection
+that lies in a network of strongly connected nodes, the whole network is
+likely to cary an effect. Thus, they adapt cluster-level inference to
+connectivity analysis, in order to mitigate the curse of multiple
+comparisons.
 
@@
 
+Mutual information? Entropy correlation? MI as measure of integration (Marralec)
+
 Small world networks, transport properties, resilient...
+\cite{achard2006,bullmore2009}
 
 Warning note that correlation matrices have long-tailed degree
-distribution by definition (cite recent Bullmore paper showing that).
-
-Mutual information? Entropy correlation? MI as measure of integration (Marralec)
+distribution by definition \cite{zalesky2012}.
 

### 2012-12-26 paper.tex
typo

@@
 
-Taking a difference stance on distributed variability, the ``network-based
+Taking a different stance on distributed variability, the ``network-based
 statistics'' approach \cite{zalesky2010} draws from the hypothesis that

### 2012-12-27 paper.tex
iter

@@
 
-Mutual information? Entropy correlation? MI as measure of integration (Marralec)
+\paragraph{Network integration}
+%
+To avoid the multiple comparison issue and to capture the network-level
+distributed variability, a possible strategy is to perform comparison and
+statistical testing at the level of the network, rather than the
+individual connection. In particular, Marrelec \emph{et al.}\
+\cite{marrelec2008} introduce the use of entropy and mutual information
+as a measure of network integration\footnote{See \cite{varoquaux2010c}
+for simplified formulas for network integration and mutual information.}.
+Gaussian entropy can be seen as a simple metric to generalize correlation
+or variance to multiple nodes (see \cite{anderson1958} \S2.5.2 and
+\S7.5). Indeed, let us considering 3 nodes: $a$, $b$ and $c$. Their
+correlation structure is captured by three correlation coefficients:
+$\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$.
 
+% Rmk average of correlations will measure the sphericity of the
+% distribution
+
+%{{{------ Integration measure -----------------------------------------------
+\begin{figure}
+\begin{minipage}{.19\linewidth}
+    \center\sffamily
+    {\small Integration:}
+
+    1.513
+\end{minipage}%
+\begin{minipage}{.25\linewidth}
+    \includegraphics[width=\linewidth]{correlation_ex1.pdf}
+\end{minipage}%
+\hfill%
+\begin{minipage}{.25\linewidth}
+    \includegraphics[width=\linewidth]{correlation_ex2.pdf}
+\end{minipage}%
+\begin{minipage}{.19\linewidth}
+    \center\sffamily
+    {\small Integration:}
+
+    0.492
+\end{minipage}%
+
+\caption{Two different correlation matrix with the same average
+correlation, but integration values that strongly differ.
+\label{fig:integration}}
+\end{figure}
+%---------------------------------------------------------------------------}}}
+
+\paragraph{Graph-topology metrics}
+%
 Small world networks, transport properties, resilient...

### 2012-12-27 paper.tex
Finish the mutual information paragraph

@@
 
-\subsection{Comparing Network Summary Statistics}
+\subsection{Comparing network summary statistics}
 
@@
 correlation structure is captured by three correlation coefficients:
-$\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$.
-
-% Rmk average of correlations will measure the sphericity of the
-% distribution
+$\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$. Summarizing these by their
+mean, as it might seem natural, discards the relationship between the
+signals, while using the integration tells us how much two signals can be
+combined to form the third (see Fig.\,\ref{fig:integration}). Similarly
+as Gaussian entropy can be used to measure the integration of a brain
+system or network, cross-entropy --or mutual information--
+\cite{marrelec2008} measures the amount of cross-talk between two
+systems. The functional-connectivity structure, or its representation in
+form of a correlation matrix, can thus be characterized via the
+integration and cross-talk of some of its subs-systems. This appraoch
+gives a simplified representation with a small number of metrics that can
+be compared across subjects.
 
@@
 \begin{figure}
+\hspace*{2ex}%
 \begin{minipage}{.19\linewidth}
@@
 
-    1.513
+    0.554
 \end{minipage}%
-\begin{minipage}{.25\linewidth}
+\begin{minipage}{.2\linewidth}
     \includegraphics[width=\linewidth]{correlation_ex1.pdf}
@@
 \hfill%
-\begin{minipage}{.25\linewidth}
+\begin{minipage}{.033\linewidth}
+    \includegraphics[width=\linewidth]{correlation_cmap.pdf}%
+    \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
+    \llap{\raisebox{10.1ex}{\scriptsize\sffamily\bfseries\color{white} 1}%
+	    \hspace*{.54ex}}
+\end{minipage}%
+\hfill%
+\begin{minipage}{.2\linewidth}
     \includegraphics[width=\linewidth]{correlation_ex2.pdf}
@@
 
-    0.492
+    2.422
 \end{minipage}%
+\hspace*{2ex}%
 
-\caption{Two different correlation matrix with the same average
-correlation, but integration values that strongly differ.
+\caption{Two different correlation matrices with the same average
+correlation, but with very different integration values. Indeed, the
+matrix on the left was chosen to have represent three signals $a$, $b$
+and $c$ as different from each other as possible, given $\rho_{ab} +
+\rho_{bc} + \rho{ac} = 1.35$; it thus as a small integration value. On
+the opposite, for the matrix on the right, signal $b$ can almost be fully
+recovered by combining signals $a$ and $c$; the matrix thus has a large
+integration value.
 \label{fig:integration}}
+% Rmq: in this example, in the second figure, the 3 signals are more
+% independent, and thus define a wider range of acceptable signal.
 \end{figure}

### 2012-12-28 paper.tex
Add missing files
iter of graph-topology appraoches

@@
 %
-Small world networks, transport properties, resilient...
-\cite{achard2006,bullmore2009}
+Functional connectivity graphs have been found to display specific
+topological properties\footnote{In the neuroscience world, these
+descriptions are group under the terms of ``graph theoretical
+approaches'', however graph theory is an entire division of mathematics
+and computer science that is concerned with much more than topology of
+random graphs.} that are characteristic of small-word networks
+\cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
+display excellent transport properties: although they display relatively
+small number of connections, any two regions of the brain are well
+connected. Another interesting consequence of their specific topology is
+the resilience it gives to the system to attacks such as resulting from
+brain lesions \cite{achard2006}. This overall structure of
+functional-connectivity graphs can be summarized by a few metrics, such
+as the average path length between any two nodes or the local clustering
+coefficients. Given that pathologies without a well-defined focus, such
+as schizophrenia, are thought to have a global impact on brain
+connectivity \cite{liu2008,bassett2008}, it is interesting to use the
+graph-topology metrics to perform inter-subject comparison. Such an
+approach is appealing as it is not subject to multiple comparison issues.
+However, it has been criticized as giving a fairly unspecific
+characterization of the brain and being fragile to noise 
+\cite{ioannides2007}.
 

### 2012-12-28 paper.tex
Finish small world part

@@
 as the average path length between any two nodes or the local clustering
-coefficients. Given that pathologies without a well-defined focus, such
+coefficients \cite{rubinov2010}. Given that pathologies without a well-defined focus, such
 as schizophrenia, are thought to have a global impact on brain
@@
 characterization of the brain and being fragile to noise
-\cite{ioannides2007}.
-
-Warning note that correlation matrices have long-tailed degree
-distribution by definition \cite{zalesky2012}.
+\cite{ioannides2007}. Another caveat is that correlation matrices display
+small-word properties such as local clustering by construction, as if two
+nodes are strongly correlated to a third, they are highly likely to be
+correlated to each other \cite{zalesky2012}. This observation highlight
+the need for well defined null-hypothesis \cite{zalesky2012,rubinov2011},
+but also for controlled recovery of brain functional connectivity going
+beyond empirical correlation.
 

### 2012-12-28 paper.tex
Iter on last part

@@
 but also for controlled recovery of brain functional connectivity going
-beyond empirical correlation.
+beyond empirical correlation matrices.
 
@@
 
-\section{Functional and effective connectivity}
+\section{Beyond correlation, effective connectivity?}
 
-Effective connectivity does not have to be causal => but a precise mathematical
-definition of the relationship => BCI workshop reports
+All the approaches that we have presented in this review are based on
+second-order statistics of the signal, in other words correlation
+analysis. Traditionally, these are defined as \emph{functional
+connectivity}, defined as ``temporal correlations between remote
+neurophysiological events'' \cite{friston1994}, and opposed to
+\emph{effective connectivity}, \emph{i.e.}\ ``the influence one neural
+system exerts over another'' \cite{friston1994}. To conclude this review,
+we would like to bridge the gap between these concepts, which in our eyes
+should be seen as a continuum rather than an opposition (this opinion is
+also expressed in \cite{mcintosh2010}).
 
-Fucntional connectivity is a statistical relationship, instead of precise mathematical
-relationship
+A first step to move from purely descriptive statistics to modeling with
+functional connectivity analysis is to consider a correlation matrix as a
+Gaussian graphical model, \emph{i.e.} a well-defined probabilistic model
+that describes observed correlations in terms of an independence
+structure and conditional relations \cite{lauritzen1996,varoquaux2011}.
+In such settings, the inverse covariance graph or the partial
+correlations are a measure of influence from one node to another, albeit
+undirected.
 
@@
 
-Cross validation???
+Cross validation
 

### 2012-12-28 paper.tex
Iter on last part

@@
 correlations are a measure of influence from one node to another, albeit
-undirected.
+undirected. Inferring direction in a Gaussian model is impossible. Linear
+structural equation models (SEMs) \cite{mcintosh1994} rely on similar
+model that consists in specifying a candidate directed graphical
+structure. This structure constraints the covariance matrix of the
+signals and can thus be tested on observed data. In fact some forms of
+SEMs are known as ``covariance structure models''. Their is thus a strong
+formal link between correlation analysis in the framework of graphical
+models and SEMs: the former is undirected but fully exploratory, as it
+does not require the specification of candidate structure, while the
+latter is directory but confirmatory. The link has been exploited to
+specify candidate structures for SEMs using partial correlations
+\cite{marrelec2007}. More complex models, such as dynamical causal models
+(DCMs) \cite{friston2003a} or Granger causality \cite{goebel2003} require
+additional hypotheses such as non-linear couplings or time lags.
 
-%------------------------------------------------------------------------------
-\subsection{From correlations to structural equation modeling}
-
-\cite{mcintosh1994}
-\cite{marrelec2007}
-\cite{marrelec2009}
-
-%------------------------------------------------------------------------------
-\subsection{Matching model complexity to data}
+Most importantly, more complex models can only be estimated to model
+interactions between a smaller number of nodes. This is not only due to a
+computational difficulty, but also to fundamental roadblocks in
+statistics: the complexity of the model must match the richness of the
+data. While injecting prior information can help model estimation, the
+more informative this prior, the fragile the inference becomes. The
+ongoing debate on the impact of hemodynamic lag on Granger-causality
+inference \cite{smith2012a} is an example of such fragility.
 
@@
 description, and simple phenomenological models such as correlation
-matrices.
+matrices. Cite \cite{ravikumar2011} to argue that sparse inverse
+covariance is reasonably robust to violations of the assumption of
+Gaussianity.
 
-\cite{mcintosh2010}
-
-Cross validation
+Cross validation \cite{friston2012} to destroy the argument on the
+Neyman-Pearson lemma (it is self-confirmatory).
 

### 2012-12-29 paper.tex
iter
Finish up last part

@@
 
-Most importantly, more complex models can only be estimated to model
+Most importantly, more complex models can only be used to model
 interactions between a smaller number of nodes. This is not only due to a
@@
 inference \cite{smith2012a} is an example of such fragility.
+While most of the theory underpinning correlation analysis (Gaussian
+graphical models) is based on a Gaussian assumption, the core results
+are robust to violations of this assumption \cite{ravikumar2011}.
 
-Diatribe: all model are wrong, but some are useful => a cat is a model of a cat
-
-Setting the cursor between complex models based on a bio-physical
-description, and simple phenomenological models such as correlation
-matrices. Cite \cite{ravikumar2011} to argue that sparse inverse
-covariance is reasonably robust to violations of the assumption of
-Gaussianity.
-
-Cross validation \cite{friston2012} to destroy the argument on the
-Neyman-Pearson lemma (it is self-confirmatory).
+It is tempting to favor more neurobiologically-inspired models that give
+descriptions close to our knowledge of the brain basic mechanisms,
+however, as George Box famously said, ``all models are wrong; some models
+are useful''. Depending on the question and the data at hand, the cursor
+should be set between complex models based on a bio-physical description,
+and simple phenomenological models such as correlation matrices. In
+particular to model interactions between a large number of regions, as in
+full-brain analysis, and learn a large \emph{connectome}, simple models
+are to be preferred. For more hypothesis-driven studies, such as the
+analysis of the mechanism underlying a specific task, more complex models
+can be preferred, if rich data is available. Automatic choice of model is
+a difficult problem, however, cross-validation (as used in
+\cite{varoquaux2010c,craddock2011,strother2006}) is a useful tool. The
+central principle of cross-validation is to learn (or fit) a model, and
+then test its test predictive power on unseen data. Models too complex
+for the data available while fit noise in the data, and thus generalize
+poorly. The main benefit of cross-validation is that it is a
+non-parametric method which does not rely strongly on modeling
+assumption\footnote{This is to be contrasted to Bayesian model
+comparison, which will give correct results only if the true generative
+model is in the list of models compared. \cite{friston2012} argues that,
+based on the Neyman-Pearson lemma, cross-validation is less powerful than
+likelihood ratio tests relying on the full dataset. However, it is
+important to keep in mind that these approaches only test for
+self-consistence, as they require that model likelihood to describe the
+data well.}.
 

### 2012-12-29 paper.tex
Iter on intro

@@
 \sloppy % Fed up with messed-up line breaks
+
 \section{Introduction}
+
+Brain functional connectivity captures the synchronization of distant
+neural systems via correlations in brain activity. Given that brain
+function emerges from the interaction of specialized units, functional
+connectivity is an essential part of the description of brain function,
+complementary to the localizationist picture emerging from the systematic
+mapping of regions recruited in tasks. However, while activation mapping
+has a well-defined standard analysis framework that enables
+statistically-controlled comparisons across subjects \cite{friston1995},
+group-level analysis of functional connectivity is still offers many
+challenges.
+
+\cite{kelly2012}
 
@@
 BOLD signal during rest is typically just 5-10\% lower than during task-based
-experiments (cite Raichle,  Mintun, Annu. Rev. Neurosci. 29, 449–476 (2006).)
+experiments \cite{raichle2006}.
 

### 2012-12-29 paper.tex
iter on intro

@@
 group-level analysis of functional connectivity is still offers many
-challenges.
+methodological challenges. Giving a picture of functional connectivity at
+the subject level is by itself not straightforward, as the brain
+comprises a myriad of interacting subsystems and must be decomposed in
+simplified and synthetic representations: distributed functional networks
+depicted by their spatial maps \cite{fox2005} or a connections linking
+localized functional modules depicted as a graph \cite{bullmore2009}.
+Here we focus on the latter: the functional connectome \cite{sporns2005}.
 

### 2012-12-30 paper.tex
Iter intro

@@
 
+% General introduction
 Brain functional connectivity captures the synchronization of distant
@@
 comprises a myriad of interacting subsystems and must be decomposed in
-simplified and synthetic representations: distributed functional networks
-depicted by their spatial maps \cite{fox2005} or a connections linking
-localized functional modules depicted as a graph \cite{bullmore2009}.
-Here we focus on the latter: the functional connectome \cite{sporns2005}.
+simplified and synthetic representations. An important view of brain
+connectivity is that of distributed functional networks depicted by their
+spatial maps \cite{fox2005}. Another no less important and complementary
+view is that of connections linking localized functional modules depicted
+as a graph \cite{bullmore2009}. This representation of brain connectivity
+is often called the functional connectome \cite{sporns2005} and is the
+focus of intense worldwide research efforts as it holds promises of new
+insights in cognition and pathologies
+\cite{greicius2008b,biswal2010,fox2010}.
 
-\cite{kelly2012}
+% Give the scope of the paper and narrow it
+The purpose of this paper is to review methodological progress in the
+estimation and comparison of functional connectomes. It does not attempt
+to be exhaustive, as the field is wide and moving rapidly, but details
+specific tools and guidelines that, in the experience of the authors,
+lead to controlled and powerful inter-subject comparisons. The paper is
+focused on functional connectomes, in contrast to structural connectomes,
+as the inference of functional connectivity from fluctuations in the
+signal induces important specificities. While the notion of functional
+connectome is often associated with the study of resting-state
+\cite{biswal2010}, the methods presented in this paper are also relevant
+for task-based studies. On the other hand, the paper has a focus on fMRI;
+although the core concepts presented can be applied to MEG or EEG
+\cite{stam2004}, additional specific problems such as source
+reconstruction must be considered \cite{schoffelen2009}.
 
-Review paper giving technical guidelines.
-
-BOLD signal during rest is typically just 5-10\% lower than during task-based
-experiments \cite{raichle2006}.
-
+% Define terms
 Define what we call a functional connectome, and the term \emph{graph},
@@
 Define on-going vs evoked activity
+
+% Give a layout of the paper
 

### 2012-12-30 paper.tex
Iter intro

@@
 % Define terms
-Define what we call a functional connectome, and the term \emph{graph},
-as well as its relation with an adjacency matrix.
-
-Define a functional network
-
-Define on-going vs evoked activity
+By ``functional connectome'', here we specifically denote a graph
+representing functional interactions in the brain, where the term
+``graph'' is taken in its mathematical sens: a set of \emph{nodes}
+connected together by \emph{edges}. A graph can be weighted or not, and
+is completely equivalent to its \emph{adjacency matrix}, a symmetric
+matrix tabulating the connection weights between each pair of nodes.
+Functional-connectivity graphs can be used to represent evoked activity,
+as in task-response studies \cite{mcintosh2000}, as well as
+task-independent ongoing activity that is present in the background
+during task and often studies in so-called \emph{resting-state}
+experiments \cite{raichle2010}. Another important notion that arises from
+the study of distributed modes of brain function is that of specialized
+functional networks\footnote{In neuroimaging, the term network is
+sometimes used to denote a graph of brain function. To disambiguate the
+notion of segregated spatial mode \cite{fox2005} from that of
+connectivity graphs, we will purposely restrict its usage in this
+paper.}. With our definition of the functional connection, functional
+networks are not directly building blocks of the connectome but appears
+as a consequence of the graphical structure
+\cite{varoquaux2010c,varoquaux2012}.
 

### 2012-12-30 paper.tex
typos

@@
 connectivity graphs, we will purposely restrict its usage in this
-paper.}. With our definition of the functional connection, functional
-networks are not directly building blocks of the connectome but appears
+paper.}. With our definition of the functional connectome, functional
+networks are not directly building blocks of the connectome but appear
 as a consequence of the graphical structure

### 2012-12-30 paper.tex
intro done!

@@
 % Give a layout of the paper
+The paper is organized has follows. First we discuss estimation of
+functional connectomes. This part, akin to a first-level analysis in
+standard activation mapping methodology, is not in itself a group-level
+operation, but it is a critical step for inter-subject comparison.
+In a following section, we discuss several strategies for comparing
+connectomes across subjects. Finally we discuss the links between the
+representation of brain connectivity as graphs of functional connectivity
+and more complex models, such as effective-connectivity models.
 

### 2012-12-30 paper.tex
added draft predictive modeling

@@
 4. setting parameters.
+\section{Predictive Modeling}
+craddock 2009, Dosenbach 2010, lord 2011, deshpande,
+
+1. importance of interpretation!
+2. the need for feature extraction
+3. the need for feature selection
+4. setting parameters.
 5. different methods have different interpretations
 
+Predictive modeling has been an active area of research in functional
+neuroimaging since the early 90s [] that has more recently been adapted to
+comparing connectomes [].  A predictive model defines a mathematical
+relationship between a set of data features and a categorical or continuous
+variable of interest (target) that is capable of decoding or \emph{predicting}
+the target variable from the data.  In the context of comparing connectomes,
+features correspond to bivariate measures of connectivity or other region
+specifc graph statistics and the target is a phenotypic variable (e.g. age, sex,
+disease state). The accuracy of a model for predicting the target variable
+provides a natural means for evaluating the utility of the model as a biomarker
+[] and for measuring the amount of information present in the connectome about
+the target variable [Kjems, Kriegeskorte]. Prediction accuracy when combined
+with a measure of model reproducibilty provides a means to evaluate experimental
+tradeoffs for data acquisition, preprocessing, and analysis [NPAIRS]. Predictive
+modeling techniques have been successfully applied to identify connectome-based
+biomarkers of Alzheimer's disease [92], major depression [93], schizophrenia
+[94], autism [47], ADHD [], and aging [].  Recent work has illustrated the
+utility of predictive modeling for deriving connectivity models at the
+individual level [97,].
+
+Nearly every analytical method can be appplied in a predictive modelling framework, but
+multivariate classification and regression have been the most commonly used
+(referred to as MVPA; multivariate prediction analysis).  Multivariate methods
+are attractive in connectomics because they are sensitive to dependencies
+between features and avoid the need to correct for multiple comparisions since
+the significance of an entire pattern is evaluated using a single statistical
+test. Predictive modeling is typically performed in a supervised learning
+framework where a target is available for each observation of the features,
+although unsupervised and semi-supervised methods can also be used.
+
+Predictive models are validated using one or more iterations of cross
+validation, which involves training and testing phases.  A cross validation
+cycle begins by seperating the available data into two independent subsets:
+training data and testing data.  Training involves learning a predictive model
+from the training data. During testing the model is applied to the testing data
+to predict corresponding values of the target variable.  Prediction accuracy is
+then assessed by comparing these predictions to the observed values of the
+target variable. In order to make
+
+A general application of predictive modeling can be broken down into feature
+extraction, model selection, feature selection, and model validation, each of
+which may contain one or more iteration of training and testing. Feature
+extraction
+
+Model training can be further broken down into feature extraction, model
+selection and feature selection and testing can be performed for model
+optimziation and
+
+The application of predictive modeling to functional neuroimaging data has been
+an active area of research since the early 90s[] and more recently for comparing
+connectomes[]. Nearly every analytical method can be appplied in a predictive
+modelling framework, but multivariate classification and regression have been
+the most commonly used (referred to as MVPA; multivariate prediction analysis).
+Multivariate methods are attractive in connectomics because they do not require
+any assumptions regarding independence between features and avoid the need to
+correct for multiple comparisions since the significance of an entire pattern is
+evaluated using a single statistical test. Support vector machines
+(classification and regression) are popular for MVPA applications owing to their
+proven track record for acheiving good prediction accuracy in high dimensional
+datasets (many features) with few observations.
+
+Cross validation
+
+MVPA algorithms typically require the specification of several parameters, the
+values of which will impact the quality of the results. These parameters may be
+prespecified based on domain specific knowledge, or requirements, determined
+using an analytical approach, or optimized using cross validation. In latter
+case a nest cross-validation scheme is required to avoid biasing resultant
+measures of prediction accuracy. it is necessary to perform a nested
+cross-validation These parameters may be set by hand in the case where
+
+Determining the subset of features most relevant to the model (feature
+selection) is essential for interpreting the models, and is the subject of
+ongoing research. In cases were model weights can be directly mapped to their
+corresponding feature, there is typically no statistical framework for
+thresholding these weights, and meaningless features are not always set to zero
+(this is particularly the case for L2 regularized algorithms such as SVM and
+ridge regression). One feature selection strategy is to filter out features
+based on their statistical relationship with the variable of interest using a
+univariate statistical criterion such as t-test, Pearson's correlation, or
+mutual information.  A drawback of this approach is that since the filters are
+typically insensitive to multivaratiate information, they may exclude features
+that would be important to the model.  Another approach is to treat feature
+selection as a model selection problem in which case the features are
+iteratively pruned and a subset is chosen based on prediction performance. A
+third approach is to use sparse modeling methods such as L1 SVM or LASSO that
+force meaningless weights to be zero.  Although ideal, these methods may have
+limits on the number of non-zero weights used in the model or the exclusion of
+highly correlated features from the model.  Contrary to previous reports [Guyon
+2002, Craddock 2009] no matter which feature selection strategy is employed, it
+must be performed withen cross-validation to avoid biasing estimates of
+prediction accuracy [later Guyon].
+
+The interpretation of classifier weights for selected features, when available,
+is complicated and requires insight into the mechanisms underlying the modeling
+approach. If features are appropriately standardized prior to training, the
+magnitude of weights can be interpreted to reflect the relative importance of
+the feature to the model, but interpreting how the feature differs between
+classes or relates to a continuous variable is more complicated, particularly
+given the multivariate nature of their involvement.  For classification methods
+such as Fisher's linear descriminate analysis (LDA),which maximally seperates
+class means given their standard deviation, feature weights are representative
+of the differences between class means. For support vector classification,
+classifier weights are derived from observations that are the most similar
+between classes, and hence represents the border between classes.  It is perhaps
+most reasonable to adapt a conservative interpretation in which MVPA is used to
+identify the most relevant features that are later tested in followon
+experiments better suited to elucidating their relationship to the variable of
+interest.
+
 \emph{ --- CC text from TICS paper, do not use without modification!}
-Multivariate Prediction Analysis. When applied to the study of intrinsic activity, the goal of discovery
-science is to identify models that relate measures of that activity (such as iFC) to phenotypic variables.
-Prediction analysis provides a means for measuring how well these models generalize to independent data.
-This is complementary to inferential statistics, which measure the likelihood of such relationships
-arising by chance. In the prediction analysis framework, a model relating iFC to a phenotype is learned 
-from a training dataset. This model is then applied to an independent test dataset to predict phenotypes.
-The resultant predictions are compared to the true phenotypes to estimate how well the model generalizes
-to the tese dataset. Thus, prediction analysis provides a natural framework for evaluating biomarkers [21],
-performing real-time fMRI [88], and evaluating experimental tradeoffs [89].
+Multivariate Prediction Analysis. When applied to the study of intrinsic
+activity, the goal of discovery science is to identify models that relate
+measures of that activity (such as iFC) to phenotypic variables.  Prediction
+analysis provides a means for measuring how well these models generalize to
+independent data.  This is complementary to inferential statistics, which
+measure the likelihood of such relationships arising by chance. In the
+prediction analysis framework, a model relating iFC to a phenotype is learned
+from a training dataset. This model is then applied to an independent test
+dataset to predict phenotypes.  The resultant predictions are compared to the
+true phenotypes to estimate how well the model generalizes to the tese dataset.
+Thus, prediction analysis provides a natural framework for evaluating biomarkers
+[21], performing real-time fMRI [88], and evaluating experimental tradeoffs
+[89].
 

### 2012-12-30 paper.tex
Minor edits

@@
 
-%\title{Comparing Connectomes Between Populations}
-\title{Learning and comparing functional connectomes between populations}
+\title{Learning and comparing functional connectomes across subjects}
 
@@
 % General introduction
-Brain functional connectivity captures the synchronization of distant
-neural systems via correlations in brain activity. Given that brain
+Functional connectivity captures the synchronization of distant
+neural systems via correlations in brain activity
+\cite{biswal1995,cordes2000}. Given that high-level
 function emerges from the interaction of specialized units, functional
@@
 complementary to the localizationist picture emerging from the systematic
-mapping of regions recruited in tasks. However, while activation mapping
-has a well-defined standard analysis framework that enables
+mapping of regions recruited in tasks. However, while there exists a
+well-defined standard analysis framework for activation mapping that enables
 statistically-controlled comparisons across subjects \cite{friston1995},
-group-level analysis of functional connectivity is still offers many
+group-level analysis of functional connectivity still faces many open
 methodological challenges. Giving a picture of functional connectivity at
@@
 
+Horwitz \emph{el al.}\ \cite{horwitz1995} mentioned almost 20 years ago
+that ``the crucial concept needed for network analysis is covariance''.
+
 {

### 2012-12-30 paper.tex
minor edits

@@
 group-level analysis of functional connectivity still faces many open
-methodological challenges. Giving a picture of functional connectivity at
-the subject level is by itself not straightforward, as the brain
-comprises a myriad of interacting subsystems and must be decomposed in
+methodological challenges. Giving a picture of a single subject's 
+functional connectivity is by itself not straightforward, as the brain
+comprises a myriad of interacting subsystems and its connectivity must 
+be decomposed in
 simplified and synthetic representations. An important view of brain
@@
 as the inference of functional connectivity from fluctuations in the
-signal induces important specificities. While the notion of functional
+signal implies important specificities in the statistical modeling. While 
+the notion of functional
 connectome is often associated with the study of resting-state
@@
 as in task-response studies \cite{mcintosh2000}, as well as
-task-independent ongoing activity that is present in the background
-during task and often studies in so-called \emph{resting-state}
+ongoing activity, present in the absence of specific tasks or in 
+the background during task and often studied in so-called \emph{resting-state}
 experiments \cite{raichle2010}. Another important notion that arises from
@@
 connectivity graphs, we will purposely restrict its usage in this
-paper.}. With our definition of the functional connectome, functional
+paper.} \cite{fox2005}. With our definition of the functional connectome, functional
 networks are not directly building blocks of the connectome but appear
@@
 % Give a layout of the paper
-The paper is organized has follows. First we discuss estimation of
+The paper is organized as follows. First we discuss estimation of
 functional connectomes. This part, akin to a first-level analysis in
@@
 
-Here we discuss strategies to infer connectomes from functional brain
+Here we discuss the inference of connectomes from functional brain
 imaging data. We start with the choice of nodes \emph{i.e.}\ regions,
@@
 shown that extracting signal from ROIs that did not match functional
-units would lead to incorrect graph extraction \cite{smith2011}.
-%
-Different strategies coexist. While dense parcellations approaches cover
+units would lead to incorrect graphs estimated \cite{smith2011}.
+%
+Different strategies to define suitable ROIs coexist. While dense parcellations approaches cover
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
@@
 differentiation across networks \cite{greicius2003, fair2009,
-varoquaux2010b, lewis2009, fransson2008, shirer2012}. In addition, while
-ROIs and most often defined as a hard selection of voxels, it is also
+varoquaux2010b}. In addition, while
+ROIs are most often defined as a hard selection of voxels, it is also
 possible to use a \emph{soft} definition, attributing weights as with

### 2012-12-30 paper.tex
minor edits

@@
 benefits from an SPM toolbox. However, it suffers from major
-shortcomings; namely that \emph{i)} it was defined on a single subject
+shortcomings; namely \emph{i)} that it was defined on a single subject
 and thus does does not reflect inter-subject variability and \emph{ii)}
-focuses on labeling large anatomical structures and does not match
+that it focuses on labeling large anatomical structures and does not match
 functional layout --for instance only two regions describe the medial
@@
 First, it can capture subject-specific functional information. Second, it
-also adapts to the signal at hand and it's limitations, such as
+adapts to the signal at hand and its limitations, such as
 EPI-specific warps or vascular and movement artifacts that are isolated

### 2012-12-30 paper.tex
minor edits

@@
 thirion2006}, and have been shown to extract well-known functional
-structures from rest data \cite{yeo2011}. Alternatively, decompositions
-methods, such as ICA \cite{beckmann2004}, can unmixing linear
-combinations of multiple effects and separate out multiple spatial maps
+structures from rest data. Alternatively, decompositions
+methods, such as ICA \cite{beckmann2004}, can unmix linear
+combinations of multiple effects and separate out overlapping spatial maps
 capturing functional networks or confounding effects. At high model
@@
 CSF average signals and movement parameters. The insert shows the
-connections restricted to the .
+connections restricted to a few major nodes.
 -- \textbf{Upper right}: regressing out only movement parameters. -- 
@@
 run a first-level analysis, enforcing specificity of the measure
-extracted to the task. With slow event-related design, task-specific
+extracted to the task. With slow event-related designs, task-specific
 functional connectivity can be captured in trial-to-trial fluctuations in
@@
 often recommended, based on the initial observation that neural-related
-signal are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
+signals are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
 high-pass and low-pass filtering decrease the impact of some confounds,
@@
 The insert shows the
-connections restricted to the default mode network. -- \textbf{Upper
+connections restricted to a few major nodes. -- \textbf{Upper
 right}: non-sparse estimate: inverse of the sample correlation matrix. --
@@
 number of measurements was infinite, the two would coincide, however if
-this number is not large compared to the number of connection (that
+this number is not large compared to the number of connections (that
 scales as the square of the number of ROIs), the sample correlation
@@
 standard correlation (marginal correlation) between two variables $a$ and
-$b$ also capture the effects of other variables -- strong correlation of
+$b$ also capture the effects of other variables: strong correlation of
 $a$ and $b$ with a third variable $c$ will induce a correlation between
@@
 regularization parameter which controls the sparsity of the estimate. A
-good rule of thumb to set this parameter is via cross-validation
+good rule of thumb to choose this parameter is via cross-validation
 \cite{varoquaux2010c}.
@@
 large-scale functional networks, such as the default mode network. Note
-the split in network is not straightforward. Different ordering of the
+that the split in networks is not straightforward. Different ordering of the
 nodes will reveal different networks. Indeed, because of the presence of
-hubs and interleaved networks the picture in terms of segregated networks
+hubs and interleaved networks, the picture in terms of segregated networks
 is not sufficient to explain full-brain connectivity
@@
 a third region $c$. In this light, the choice of nuisance regressors to
-remove confounding common signal is less critical. Indeed, while with
+remove confounding common signal is less critical with partial
+correlations than with correlations. Indeed, while with
 correlation matrices regressing out the global mean has a drastic

### 2012-12-31 paper.tex
minor edits

@@
 % Neuroimage-like layout
-\documentclass[5p]{elsarticle}
+%\documentclass[5p]{elsarticle}
+% For kindle
+\documentclass[1p,12pt]{elsarticle}
+\usepackage{geometry}
+\geometry{a6paper,hmargin={.2cm,.2cm},vmargin={1cm,1cm}}
+% End kindle
 \usepackage{amsmath,amsfonts,amssymb}
@@
 
-Here, we consider the problem of comparing functional connectivity across
-subjects or across conditions.
+In this section, we consider the problem of comparing functional
+connectivity across subjects or across conditions.
 
@@
 First, we focus on detecting where the connectivity matrices estimated in
-the previous section differ. \paragraph{Mass-univariate approaches}
-%
-The most natural approach is to do a linear model on each coefficient of
-the connectivity matrices, as in \cite{lewis2009,grillon2012}. This
+the previous section differ.
+
+\paragraph{Mass-univariate approaches}
+%
+The most natural approach is to apply a linear model to each coefficient of
+the connectivity matrices \cite{lewis2009,grillon2012}. This
 approach is similar to the second-level analysis used in mass-univariate
-brain mapping, and will give rise to many of the well-known techniques
-used in such a context, such as the definition of second-level design,
+brain mapping, and gives rise to many of the well-known techniques
+used in such a context, such as the definition of a second-level design,
 with possibly the inclusion of confounding effects, and statistical tests
 (T tests or F tests) on contrast vector. Importantly, in order to work
-with Gaussian-distributed correlations, it is necessary to apply a Fisher
+with Gaussian-distributed variables, it is necessary to apply a Fisher
 Z transform\footnote{See
 \url{http://en.wikipedia.org/wiki/Fisher_transformation} or
-\cite{anderson1958}, section 4.2.3 for mathematical arguments}. Note that
+\cite{anderson1958}, section 4.2.3 for mathematical arguments} to the
+correlations. Note that
 in these settings, the Ledoit-Wolf estimator \cite{ledoit2004} is
-probably a good choice to estimate the correlation matrix, as it is
-parameter-less and gives good estimation performance without imposing any
+often a good choice to estimate the correlation matrix, as it is
+parameter-free and gives good estimation performance without imposing any
 restrictions on the data.
 %
-Correcting for multiple comparison can often severely limit statistical
+For hypothesis testing,
+correcting for multiple comparison can severely limit statistical
 power, as the number of tests performed scales as the square of the
@@
 A specific challenge of connectivity analysis is that the connectivity
-between different regions tend to covary. For instance, with
+strength between different regions tend to covary. For instance, with
 resting-state data, functional networks comprising many nodes can appear
@@
 second-level analysis should be performed on correlation matrices,
-inverse-covariance matrices, or another parametrisation that would
+inverse-covariance matrices, or another parametrization that would
 disentangle effects and give unstructured (white) residuals. While
@@
 correlations are intrinsically harder to estimate. Preliminary work
-\cite{varoquaux2010b} suggest to perform statistics on residuals of
-a parametrisation intermediate between correlation matrix and inverse
-covariance matrix.
+\cite{varoquaux2010b} suggests to perform statistics on residuals of
+a parametrization intermediate between correlation matrix and inverse
+covariance matrix, that decouples effects and noise.
 
@@
 statistics'' approach \cite{zalesky2010} draws from the hypothesis that
-if, in a second-level analysis, an effect is detected in a connection
+if, in a second-level analysis, an effect is detected on a connection
 that lies in a network of strongly connected nodes, the whole network is
@@
 
+Both the multiple comparison issue and the network-level distributed
+variability are a plague to edge-level comparison of connectomes. A
+possible strategy to circumvent these difficulties is to perform
+comparison and statistical testing at the level of the network, rather
+than the individual connection.
+
 \paragraph{Network integration}
 %
-To avoid the multiple comparison issue and to capture the network-level
-distributed variability, a possible strategy is to perform comparison and
-statistical testing at the level of the network, rather than the
-individual connection. In particular, Marrelec \emph{et al.}\
+Marrelec \emph{et al.}\
 \cite{marrelec2008} introduce the use of entropy and mutual information
@@
 or variance to multiple nodes (see \cite{anderson1958} \S2.5.2 and
-\S7.5). Indeed, let us considering 3 nodes: $a$, $b$ and $c$. Their
+\S7.5). Indeed, let us consider 3 nodes: $a$, $b$ and $c$. Their
 correlation structure is captured by three correlation coefficients:
@@
 signals, while using the integration tells us how much two signals can be
-combined to form the third (see Fig.\,\ref{fig:integration}). Similarly
-as Gaussian entropy can be used to measure the integration of a brain
-system or network, cross-entropy --or mutual information--
+combined to form the third (see Fig.\,\ref{fig:integration}). 
+Cross-entropy --or mutual information--
 \cite{marrelec2008} measures the amount of cross-talk between two
-systems. The functional-connectivity structure, or its representation in
+systems in a similar way as Gaussian entropy to used to measure the
+integration of a brain
+system. The functional-connectivity structure, or its representation in
 form of a correlation matrix, can thus be characterized via the
-integration and cross-talk of some of its subs-systems. This appraoch
+integration and cross-talk of some of its subs-systems. This approach
 gives a simplified representation with a small number of metrics that can
@@
 correlation, but with very different integration values. Indeed, the
-matrix on the left was chosen to have represent three signals $a$, $b$
+matrix on the left was chosen to represent three signals $a$, $b$
 and $c$ as different from each other as possible, given $\rho_{ab} +
-\rho_{bc} + \rho{ac} = 1.35$; it thus as a small integration value. On
+\rho_{bc} + \rho{ac} = 1.35$; it thus has a small integration value. On
 the opposite, for the matrix on the right, signal $b$ can almost be fully
@@
 \cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
-display excellent transport properties: although they display relatively
+display excellent transport properties: although they have a relatively
 small number of connections, any two regions of the brain are well
 connected. Another interesting consequence of their specific topology is
-the resilience it gives to the system to attacks such as resulting from
+the resilience it gives the system to attacks such as resulting from
 brain lesions \cite{achard2006}. This overall structure of
@@
 as the average path length between any two nodes or the local clustering
-coefficients \cite{rubinov2010}. Given that pathologies without a well-defined focus, such
+coefficients \cite{rubinov2010}. Given that pathologies without a
+localized focus, such
 as schizophrenia, are thought to have a global impact on brain
-connectivity \cite{liu2008,bassett2008}, it is interesting to use the
-graph-topology metrics to perform inter-subject comparison. Such an
+connectivity \cite{liu2008,bassett2008}, the graph-topology metrics are
+promising markers to perform inter-subject comparison. Such an
 approach is appealing as it is not subject to multiple comparison issues.
@@
 characterization of the brain and being fragile to noise
-\cite{ioannides2007}. Another caveat is that correlation matrices display
-small-word properties such as local clustering by construction, as if two
+\cite{ioannides2007}. Another caveat is that these properties are not
+specific to brain function: correlation matrices display
+small-word properties such as local clustering by construction. Indeed, if two
 nodes are strongly correlated to a third, they are highly likely to be
@@
 but also for controlled recovery of brain functional connectivity going
-beyond empirical correlation matrices.
+beyond empirical correlation matrices, as discuss in the previous section.
 

### 2012-12-31 paper.tex
minor edits

@@
 % Neuroimage-like layout
-%\documentclass[5p]{elsarticle}
+\documentclass[5p]{elsarticle}
 % For kindle
-\documentclass[1p,12pt]{elsarticle}
-\usepackage{geometry}
-\geometry{a6paper,hmargin={.2cm,.2cm},vmargin={1cm,1cm}}
+%\documentclass[1p,12pt]{elsarticle}
+%\usepackage{geometry}
+%\geometry{a6paper,hmargin={.2cm,.2cm},vmargin={1cm,1cm}}
 % End kindle
@@
 functional connectivity analysis is to consider a correlation matrix as a
-Gaussian graphical model, \emph{i.e.} a well-defined probabilistic model
+Gaussian graphical model, \emph{i.e.}\ a well-defined probabilistic model
 that describes observed correlations in terms of an independence
@@
 undirected. Inferring direction in a Gaussian model is impossible. Linear
-structural equation models (SEMs) \cite{mcintosh1994} rely on similar
+structural equation models (SEMs) \cite{mcintosh1994} rely on a similar
 model that consists in specifying a candidate directed graphical
@@
 signals and can thus be tested on observed data. In fact some forms of
-SEMs are known as ``covariance structure models''. Their is thus a strong
+SEMs are known as ``covariance structure models''. There is thus a strong
 formal link between correlation analysis in the framework of graphical
@@
 does not require the specification of candidate structure, while the
-latter is directory but confirmatory. The link has been exploited to
+latter is directed but confirmatory. This link has been exploited to
 specify candidate structures for SEMs using partial correlations
@@
 Most importantly, more complex models can only be used to model
-interactions between a smaller number of nodes. This is not only due to a
+interactions between a small number of nodes. This is not only due to a
 computational difficulty, but also to fundamental roadblocks in
@@
 data. While injecting prior information can help model estimation, the
-more informative this prior, the fragile the inference becomes. The
+more informative this prior the more fragile the inference becomes. The
 ongoing debate on the impact of hemodynamic lag on Granger-causality
 inference \cite{smith2012a} is an example of such fragility.
-While most of the theory underpinning correlation analysis (Gaussian
-graphical models) is based on a Gaussian assumption, the core results
+Note that although most of the theory underpinning correlation analysis
+(Gaussian graphical models) is based on a Gaussian assumption, the core results
 are robust to violations of this assumption \cite{ravikumar2011}.
@@
 central principle of cross-validation is to learn (or fit) a model, and
-then test its test predictive power on unseen data. Models too complex
-for the data available while fit noise in the data, and thus generalize
+then test its predictive power on unseen data. Models too complex
+for the data available will fit noise in the data, and thus generalize
 poorly. The main benefit of cross-validation is that it is a
 non-parametric method which does not rely strongly on modeling
-assumption\footnote{This is to be contrasted to Bayesian model
+assumptions\footnote{This is to be contrasted to Bayesian model
 comparison, which will give correct results only if the true generative
@@
 important to keep in mind that these approaches only test for
-self-consistence, as they require that model likelihood to describe the
-data well.}.
+self-consistence, as the Neyman-Pearson lemma requires that 
+the model likelihood describes the data well which may not always be the
+case\cite{lohmann2012}.}.
 

### 2012-12-31 paper.tex
Start of clean up of predictive modelling section

@@
 
-\section{Predictive Modeling}
-craddock 2009, Dosenbach 2010, lord 2011, deshpande,
-
-1. importance of interpretation!
-2. the need for feature extraction
-3. the need for feature selection
-4. setting parameters.
-\section{Predictive Modeling}
+\subsection{Predictive Modeling}
+
+\cite{craddock2009}
 craddock 2009, Dosenbach 2010, lord 2011, deshpande,
@@
 5. different methods have different interpretations
+
+% Define predictive modeling and give examples
+
+% Feature extraction and parameter selection
+
+% Importance and caveats of interpretation
 
@@
 
-Nearly every analytical method can be appplied in a predictive modelling framework, but
+Nearly every analytical method can be applied in a predictive modeling framework, but
 multivariate classification and regression have been the most commonly used
@@
 selection and feature selection and testing can be performed for model
-optimziation and
+optimization and
 
@@
 2002, Craddock 2009] no matter which feature selection strategy is employed, it
-must be performed withen cross-validation to avoid biasing estimates of
+must be performed with cross-validation to avoid biasing estimates of
 prediction accuracy [later Guyon].
@@
 given the multivariate nature of their involvement.  For classification methods
-such as Fisher's linear descriminate analysis (LDA),which maximally seperates
+such as Fisher's linear discriminant analysis (LDA), which maximally seperates
 class means given their standard deviation, feature weights are representative
@@
 interest.
-
-\emph{ --- CC text from TICS paper, do not use without modification!}
-Multivariate Prediction Analysis. When applied to the study of intrinsic
-activity, the goal of discovery science is to identify models that relate
-measures of that activity (such as iFC) to phenotypic variables.  Prediction
-analysis provides a means for measuring how well these models generalize to
-independent data.  This is complementary to inferential statistics, which
-measure the likelihood of such relationships arising by chance. In the
-prediction analysis framework, a model relating iFC to a phenotype is learned
-from a training dataset. This model is then applied to an independent test
-dataset to predict phenotypes.  The resultant predictions are compared to the
-true phenotypes to estimate how well the model generalizes to the tese dataset.
-Thus, prediction analysis provides a natural framework for evaluating biomarkers
-[21], performing real-time fMRI [88], and evaluating experimental tradeoffs
-[89].
-
-Prediction analysis has been applied to functional neuroimaging data since the early 90’s [90], and more
-recently to IFC data [91]. Most, if not all, analysis methods can be applied in a predictive modeling
-framework but the majority of methods that have been applied to iFC are multivariate classification and
-regression methods (referred to as MVPA; multivariate prediction analysis). Multivariate methods are more
-sensitive to distributed patterns of iFC than their univariate counterparts. Additionally they provide a
-means for evaluating the significance of an entire pattern using a single statistic, obviating the need
-to correct for multiple comparisons.
-
-Although there are many circumstances in which high prediction accuracy is the ultimate goal of an
-analysis (e.g. predicting treatment outcome), in general it is desirable that the model also be
-interpretable. Identifying the iFC measures (features) that are most important to the model is
-problematic and an open issue for MVPA research. Several feature selection algorithms have been proposed
-to address this issue, but there is no consensus on which is best [21]. We note that feature selection
-methods that rely on feature-by-feature statistical tests require correction for multiple comparisons.
-
-MVPA classification has already been successfully used to identify potential iFC biomarkers of Alzheimer’s
-disease [92], major depression [93], schizophrenia [94], and autism [47], among others. MVPA
-classification and regression techniques have also been applied to identify biomarkers of age [95,96]
-and recent work has shown the utility of MVPA methods for deriving iFC models at the individual
-level [97]. An in-depth overview of the statistical pattern recognition methods underlying MVPA
-techniques can be found in [98].
-\emph{ --- END CC text from TICS paper, do not use without modification!}
 

### 2012-12-31 paper.tex
prediction modeling more

@@
 \cite{craddock2009}
-craddock 2009, Dosenbach 2010, lord 2011, deshpande,
-
-1. importance of interpretation!
-2. the need for feature extraction
-3. the need for feature selection
-4. setting parameters.
-5. different methods have different interpretations
-
 % Define predictive modeling and give examples
@@
 
+The quality of a predictive model is determined by its ability to make accurate predictions
+from never-before-seen data. This generalization ability is estimated by seperating the 
+available data into independet training and testing subsets. A predictive model is learned
+from the training data and applied to the testing data to predict corresponding values of the
+target variable. Prediction accuracy is then assessed by comparing these predictions to the 
+observed value of the target variable. This procedure can be iterated several times for different
+splits of the data and averaged to form a single measure of prediction accuracy, in a procedure termed 
+cross validation. One of the most important parameters for cross validation is the manner in which data 
+are subdivided. There are several strategies for constructing the training dataset ranging from using
+all but one observations (leave-one-out cross-validation), using a fraction of the observations
+(k-fold cross validation; kfcv), to resampling the observations with replacement (boostrap 
+cross-validation, bscv). Although loocv has been popular in neuroimaging applications of MVPA since
+it incorporates the largest amount of data into training performs the largest amount of data as it is
+easy to implement and results in the same error estimate, its estimates are more variable than 
+kfcv or bscv. Split-half cross validation (two-fold cross validation, 2fcv), minimizes the estimation
+variance, at the cost of using less training
+
+single observation (leave-one-out cross-validation; loocv), a fraction of the observations (k-fold cross-validation; kfcv),
+or resampling the observations with replacement (bootstrap cross-validation; bscv);
+
+, leaving a  A commmon practice is leave-on-out cross-validation (loocv) in which a single observation
+is used for testing at each iteration,
+
+is estimated through a one or
+more iterations of cross validation.
+
+A cross validation cycle begins by seperating the 
+available data into two independent subsets: training data and testing data. A predictive model 
+is learned from the training data and subsequently applied to the testing data to predict 
+corresponding values of the target variable. Prediction accuracy is then assessed by comparing
+these predictions to the observed value of the target variable. This procedure is typically repeated
+for several different splits of the data. The simplest is hold-out validation in which the data
+is split into testing and training
+
+	One of the most important parameters for cross validation
+is the manner in which data are subdivided, which sets the balance between maximally use of the
+data for training.
+
+	Cross-validation can be performed
+in a variaty of ways, and if performed correctly will result in an unbiased estimator of 
+generalization ability. A major choice
+
 Predictive models are validated using one or more iterations of cross
@@
 then assessed by comparing these predictions to the observed values of the
-target variable. In order to make
+target variable.
 

### 2013-01-01 paper.tex
Iterate on the predictive modeling part

--- 2012-12-31 paper.tex
@@
 
-\cite{craddock2009}
-craddock 2009, Dosenbach 2010, lord 2011, deshpande,
-
-1. importance of interpretation!
-2. the need for feature extraction
-3. the need for feature selection
-4. setting parameters.
-5. different methods have different interpretations
-
 % Define predictive modeling and give examples
 
-% Feature extraction and parameter selection
+Predictive modeling is concerned with learning (or fitting) a model to
+draw conclusion on new and unseen data \cite{pereira2009}. Typically on
+brain imaging data, it opens the door to learning diagnosis or prognosis
+markers \cite{stonnington2010}. However, beyond the practical use of
+prediction, these models can also be useful to uncover mechanism of brain
+function \cite{norman2006}. Both the fact that information \emph{can} be
+drawn to generalize predictions to new data and \emph{how} or
+\emph{where} informs us on brain function. Multivariate predictive models
+are attractive in connectomics because they are sensitive to dependencies
+between features and avoid the need to correct for multiple comparisons
+since the significance of an entire pattern is evaluated using a single
+statistical test. From the perspective of medical applications, using
+resting-state connectivity as a biomarker is particularly appealing as it
+can be applied to impaired patients \cite{greicius2008b}. Predictive
+modeling techniques have been successfully applied to identify
+connectome-based biomarkers of Alzheimer's disease
+\cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
+\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
+\cite{dosenbach2010}, as well as to classify mental operations
+\cite{richiardi2011,shirer2012}.
+
+% A bit of technical details
+
+Technically, predictive modeling is a supervised machine learning problem
+where a target to be predicted --\emph{e.g.}\ age, disease state,
+cognitive state-- is available for each observation of the data. In the
+context of comparing connectomes, features used in the predictive model
+usually correspond to bivariate measures of connectivity, or any other
+summary metrics discussed earlier.
+%
+The prediction accuracy of a model for predicting the target variable
+provides a natural means for evaluating the utility of the model as a
+biomarker, but also its explanatory power for the mechanism under study.
+%
+This prediction accuracy is measured using one or more iterations of
+cross validation, which involves training and testing phases
+\cite{pereira2009}.  A cross validation cycle begins by separating the
+available data into two independent subsets: training data and testing
+data.  Training involves learning a predictive model from the training
+data. During testing the model is applied to the testing data to predict
+corresponding values of the target variable.  Prediction accuracy is then
+assessed by comparing these predictions to the observed values of the
+target variable.
+
+% XXX: sentence below should probably be moved elsewhere
+Support vector machines (classification and regression) are popular
+algorithms for predictive modeling as they do not require fine parameter
+setting.
+% XXX: need better explanation, in particular of nested cross-val
+However, learning algorithms require in general the specification of
+parameters, the values of which will impact the quality of the results.
+These parameters may be specified based on domain specific knowledge, or
+requirements, determined using an analytical approach, or optimized using
+cross validation. In latter case a nest cross-validation scheme is
+required to avoid biasing resultant measures of prediction accuracy.
+
+Determining the subset of features most relevant to the model (feature
+selection) is essential for interpreting the models. In cases were model
+weights can be directly mapped to their corresponding feature, there is
+typically no statistical framework for thresholding these weights, and
+meaningless features are not always set to zero (this is particularly the
+case for $\ell_2$ regularized algorithms such as SVM and ridge
+regression). One feature selection strategy is to filter out features
+based on their statistical relationship with the variable of interest
+using a univariate statistical criterion such as t-test, Pearson's
+correlation, or mutual information.  A drawback of this approach is that
+since the filters are typically insensitive to multivariate
+information, they may exclude features that would be important to the
+model.
+
+% XXX: mention nested cross-val for feature selection above
 
@@
 
-Predictive modeling has been an active area of research in functional
-neuroimaging since the early 90s [] that has more recently been adapted to
-comparing connectomes [].  A predictive model defines a mathematical
-relationship between a set of data features and a categorical or continuous
-variable of interest (target) that is capable of decoding or \emph{predicting}
-the target variable from the data.  In the context of comparing connectomes,
-features correspond to bivariate measures of connectivity or other region
-specifc graph statistics and the target is a phenotypic variable (e.g. age, sex,
-disease state). The accuracy of a model for predicting the target variable
-provides a natural means for evaluating the utility of the model as a biomarker
-[] and for measuring the amount of information present in the connectome about
-the target variable [Kjems, Kriegeskorte]. Prediction accuracy when combined
-with a measure of model reproducibilty provides a means to evaluate experimental
-tradeoffs for data acquisition, preprocessing, and analysis [NPAIRS]. Predictive
-modeling techniques have been successfully applied to identify connectome-based
-biomarkers of Alzheimer's disease [92], major depression [93], schizophrenia
-[94], autism [47], ADHD [], and aging [].  Recent work has illustrated the
-utility of predictive modeling for deriving connectivity models at the
-individual level [97,].
-
-Nearly every analytical method can be applied in a predictive modeling framework, but
-multivariate classification and regression have been the most commonly used
-(referred to as MVPA; multivariate prediction analysis).  Multivariate methods
-are attractive in connectomics because they are sensitive to dependencies
-between features and avoid the need to correct for multiple comparisions since
-the significance of an entire pattern is evaluated using a single statistical
-test. Predictive modeling is typically performed in a supervised learning
-framework where a target is available for each observation of the features,
-although unsupervised and semi-supervised methods can also be used.
-
-Predictive models are validated using one or more iterations of cross
-validation, which involves training and testing phases.  A cross validation
-cycle begins by seperating the available data into two independent subsets:
-training data and testing data.  Training involves learning a predictive model
-from the training data. During testing the model is applied to the testing data
-to predict corresponding values of the target variable.  Prediction accuracy is
-then assessed by comparing these predictions to the observed values of the
-target variable. In order to make
-
-A general application of predictive modeling can be broken down into feature
-extraction, model selection, feature selection, and model validation, each of
-which may contain one or more iteration of training and testing. Feature
-extraction
-
-Model training can be further broken down into feature extraction, model
-selection and feature selection and testing can be performed for model
-optimization and
-
-The application of predictive modeling to functional neuroimaging data has been
-an active area of research since the early 90s[] and more recently for comparing
-connectomes[]. Nearly every analytical method can be appplied in a predictive
-modelling framework, but multivariate classification and regression have been
-the most commonly used (referred to as MVPA; multivariate prediction analysis).
-Multivariate methods are attractive in connectomics because they do not require
-any assumptions regarding independence between features and avoid the need to
-correct for multiple comparisions since the significance of an entire pattern is
-evaluated using a single statistical test. Support vector machines
-(classification and regression) are popular for MVPA applications owing to their
-proven track record for acheiving good prediction accuracy in high dimensional
-datasets (many features) with few observations.
-
-Cross validation
-
-MVPA algorithms typically require the specification of several parameters, the
-values of which will impact the quality of the results. These parameters may be
-prespecified based on domain specific knowledge, or requirements, determined
-using an analytical approach, or optimized using cross validation. In latter
-case a nest cross-validation scheme is required to avoid biasing resultant
-measures of prediction accuracy. it is necessary to perform a nested
-cross-validation These parameters may be set by hand in the case where
-
-Determining the subset of features most relevant to the model (feature
-selection) is essential for interpreting the models, and is the subject of
-ongoing research. In cases were model weights can be directly mapped to their
-corresponding feature, there is typically no statistical framework for
-thresholding these weights, and meaningless features are not always set to zero
-(this is particularly the case for L2 regularized algorithms such as SVM and
-ridge regression). One feature selection strategy is to filter out features
-based on their statistical relationship with the variable of interest using a
-univariate statistical criterion such as t-test, Pearson's correlation, or
-mutual information.  A drawback of this approach is that since the filters are
-typically insensitive to multivaratiate information, they may exclude features
-that would be important to the model.  Another approach is to treat feature
-selection as a model selection problem in which case the features are
-iteratively pruned and a subset is chosen based on prediction performance. A
-third approach is to use sparse modeling methods such as L1 SVM or LASSO that
-force meaningless weights to be zero.  Although ideal, these methods may have
-limits on the number of non-zero weights used in the model or the exclusion of
-highly correlated features from the model.  Contrary to previous reports [Guyon
-2002, Craddock 2009] no matter which feature selection strategy is employed, it
-must be performed with cross-validation to avoid biasing estimates of
-prediction accuracy [later Guyon].
-
-The interpretation of classifier weights for selected features, when available,
-is complicated and requires insight into the mechanisms underlying the modeling
-approach. If features are appropriately standardized prior to training, the
-magnitude of weights can be interpreted to reflect the relative importance of
-the feature to the model, but interpreting how the feature differs between
-classes or relates to a continuous variable is more complicated, particularly
-given the multivariate nature of their involvement.  For classification methods
-such as Fisher's linear discriminant analysis (LDA), which maximally seperates
-class means given their standard deviation, feature weights are representative
-of the differences between class means. For support vector classification,
-classifier weights are derived from observations that are the most similar
-between classes, and hence represents the border between classes.  It is perhaps
-most reasonable to adapt a conservative interpretation in which MVPA is used to
-identify the most relevant features that are later tested in followon
-experiments better suited to elucidating their relationship to the variable of
-interest.
+% XXX: distinguish linear from non-linear classifiers. Explain that a
+% linear classifier is nothing more than a fancy linear regression
+
+The interpretation of classifier weights for selected features, when
+available, is complicated and requires insight into the mechanisms
+underlying the modeling approach. If features are appropriately
+standardized prior to training, the magnitude of weights can be
+interpreted to reflect the relative importance of the feature to the
+model, but interpreting how the feature differs between classes or
+relates to a continuous variable is more complicated, particularly given
+the multivariate nature of their involvement.  For classification methods
+such as Fisher's linear discriminant analysis (LDA), which maximally
+separates class means given their standard deviation, feature weights are
+representative of the differences between class means. For support vector
+classification, classifier weights are derived from observations that are
+the most similar between classes, and hence represents the border between
+classes. To draw conclusions on the features used for prediction, it is
+perhaps most reasonable to adapt a conservative interpretation in which
+predictive models is used to identify the most relevant features that are
+later tested in followon experiments better suited to elucidating their
+relationship to the variable of interest.
 
@@
 the model likelihood describes the data well which may not always be the
-case\cite{lohmann2012}.}.
+case \cite{lohmann2012}.}.
 

### 2013-01-01 paper.tex
prediction modeling more

--- 2012-12-31 paper.tex
@@
 
-Predictive models are validated using one or more iterations of cross
-validation, which involves training and testing phases.  A cross validation
-cycle begins by seperating the available data into two independent subsets:
-training data and testing data.  Training involves learning a predictive model
-from the training data. During testing the model is applied to the testing data
-to predict corresponding values of the target variable.  Prediction accuracy is
-then assessed by comparing these predictions to the observed values of the
-target variable. In order to make
-
-A general application of predictive modeling can be broken down into feature
-extraction, model selection, feature selection, and model validation, each of
-which may contain one or more iteration of training and testing. Feature
-extraction
-
-Model training can be further broken down into feature extraction, model
-selection and feature selection and testing can be performed for model
-optimization and
-
-The application of predictive modeling to functional neuroimaging data has been
-an active area of research since the early 90s[] and more recently for comparing
-connectomes[]. Nearly every analytical method can be appplied in a predictive
-modelling framework, but multivariate classification and regression have been
-the most commonly used (referred to as MVPA; multivariate prediction analysis).
-Multivariate methods are attractive in connectomics because they do not require
-any assumptions regarding independence between features and avoid the need to
-correct for multiple comparisions since the significance of an entire pattern is
-evaluated using a single statistical test. Support vector machines
-(classification and regression) are popular for MVPA applications owing to their
-proven track record for acheiving good prediction accuracy in high dimensional
-datasets (many features) with few observations.
-
-Cross validation
+The quality of a predictive model is determined by its ability to make accurate predictions
+from never-before-seen data. This generalization ability is estimated by seperating the 
+available data into independet training and testing subsets. A predictive model is learned
+from the training data and applied to the testing data to predict corresponding values of the
+target variable. Prediction accuracy is then assessed by comparing these predictions to the 
+observed value of the target variable. This procedure can be iterated several times for different
+splits of the data and averaged to form a single measure of prediction accuracy, in a procedure termed 
+cross validation. One of the most important parameters for cross validation is the manner in which data 
+are subdivided. There are several strategies for constructing the training dataset ranging from using
+all but one observations (leave-one-out cross-validation), using a fraction of the observations
+(k-fold cross validation; kfcv), to resampling the observations with replacement (boostrap 
+cross-validation, bscv). Although loocv has been popular in neuroimaging applications of MVPA since
+it results in the largest amount of training data, its estimates are more variable than 
+kfcv or bscv. Split-half cross validation (two-fold cross validation, 2fcv), minimizes the estimation
+variance, at the cost of using less training data, and also permits the simultaneous estimation
+of model reproducibility using the NPAIRs framework []. Bootstrap cross-validation minimizes estimation
+variance while maximising the amount of data available for training at the cost of introducing bias. This
+bias is due to the fact that on average 63.2\percent of the testing data overlaps with the training data,
+the .632\plus bootstrap corrects for this bias.
+No matter which cross validation scheme is used, the accurate estimation of generalization ability
+requires that the testing data and training data are independent and identically distributied (iid). The
+meaning of indenpdence here depends on the context in which the predictive model will be applied. For 
+example, if observations correspond to subjects, then testing with scans acquired from the same subject, 
+even acquired at different points in time, will introduce bias. If observations are different time points 
+for the same subject, with the goal of testing whether the model can predict a later time point for that 
+subject, then scans acquired from a later time point for that subject may be used for testing as long as
+enough time has passed to account for temporal autocorrelation.
+
+Another important parameter for estimating generalization ability is the error term employed. For
+classification problems error can be simply measured as a '1' if the prediction is correct and a '0' if it
+is incorrect, alternatively misclassifications for some groups may be weighted higher then others.
+Log-loss or the negative log-likelihood can be used if class probabilities are outputed rather than
+simply class membership. For
+regression problems, common loss functions are the correlation or mean squared error between predicted and
+true target values. The former is preferred in cases when differences in scale and shift are less 
+important then the relative ordering of the output balues.  Mean-squared error is preferred when the 
+target variable has units and penalizing a model for shift or scale differences is important.
+
+After generalization ability (or error) has been estimated it is compared to what would be acheived by 
+``chance'' in order to estimate its significance. In the case of classification problems, the likelihood
+of obtaining a generalization accuracy by change can be estimated from a multinomial distribution []. 
+Alternatively, a permutation test can be performed in which the target labels are randomly permuted 
+several times and the cross-validation error is estimated using each of the permutations. Significance
+is the assessed from the fraction of permutations that obtained higher prediction accuracy then was 
+obtained from the unpermuted model. This method has the advantage of being available for both 
+classification and regression models with the caveat that, any correlationl 
+structure between observations to avoid biased results. Null distributions can be constructed for
+non-independent data using block permutation or wavelet resampling. When that statistical significance
+of the entire model is measured in this manner, the entire pattern is test with a single statistical
+test and there is no need to correct for multiple comparisons (unless multiple patterns are tested in 
+this manner).
 
@@
 prespecified based on domain specific knowledge, or requirements, determined
-using an analytical approach, or optimized using cross validation. In latter
+using an analytical approach, or optimized using cross validation. In the latter
 case a nest cross-validation scheme is required to avoid biasing resultant
-measures of prediction accuracy. it is necessary to perform a nested
-cross-validation These parameters may be set by hand in the case where
-
-Determining the subset of features most relevant to the model (feature
+measures of prediction accuracy.  Determining the subset of features most relevant 
+to the model (feature
 selection) is essential for interpreting the models, and is the subject of
@@
 thresholding these weights, and meaningless features are not always set to zero
-(this is particularly the case for L2 regularized algorithms such as SVM and
+(this is particularly the case for L2 regularized algorithms such as support vector machines and
 ridge regression). One feature selection strategy is to filter out features
@@
 that would be important to the model. Another approach is to treat feature
-selection as a model selection problem in which case the features are
-iteratively pruned and a subset is chosen based on prediction performance. A
-third approach is to use sparse modeling methods such as L1 SVM or LASSO that
+selection as a model selection problem in which case the optimal festure subset 
+is chosen based on cross validation based measures of prediction performance [] or 
+a measure of their stability[].  A third approach is to use sparse modeling methods 
+such as L1 SVM or LASSO that
 force meaningless weights to be zero.  Although ideal, these methods may have

### 2013-01-01 paper.tex
typo

--- 2013-01-01 paper.tex
@@
 nodes are strongly correlated to a third, they are highly likely to be
-correlated to each other \cite{zalesky2012}. This observation highlight
+correlated to each other \cite{zalesky2012}. This observation highlights
 the need for well defined null-hypothesis \cite{zalesky2012,rubinov2011},

### 2013-01-01 paper.tex
minor edits

@@
 
-The interpretation of classifier weights for selected features, when
-available, is complicated and requires insight into the mechanisms
-underlying the modeling approach. If features are appropriately
+The interpretation of the predictive model can be complicated and
+requires insight into the mechanisms
+underlying the modeling approach. For linear classifiers, 
+classifier weights are similar to the weight of a ordinary regression.
+If features are appropriately
 standardized prior to training, the magnitude of weights can be

### 2013-01-01 paper.tex
typo

@@
 Predictive modeling is concerned with learning (or fitting) a model to
-draw conclusion on new and unseen data \cite{pereira2009}. Typically on
+draw conclusions on new and unseen data \cite{pereira2009}. Typically on
 brain imaging data, it opens the door to learning diagnosis or prognosis
@@
 underlying the modeling approach. For linear classifiers, 
-classifier weights are similar to the weight of a ordinary regression.
+classifier weights are similar to the weights of a ordinary regression.
 If features are appropriately

### 2013-01-01 paper.tex
iter

@@
 drawn to generalize predictions to new data and \emph{how} or
-\emph{where} informs us on brain function. Multivariate predictive models
+\emph{where} it lies informs us on brain function. Multivariate
+predictive models
 are attractive in connectomics because they are sensitive to dependencies
@@
 cross validation, which involves training and testing phases
-\cite{pereira2009}.  A cross validation cycle begins by separating the
+\cite{pereira2009}. Cross validation cycles separate the
 available data into two independent subsets: training data and testing
@@
 
-% XXX: sentence below should probably be moved elsewhere
-Support vector machines (classification and regression) are popular
-algorithms for predictive modeling as they do not require fine parameter
-setting.
-% XXX: need better explanation, in particular of nested cross-val
-However, learning algorithms require in general the specification of
+Support vector machines\footnote{See \cite{kloppel2008}
+for a gentle introduction to support vector machines.} (classification and regression) are popular
+algorithms for predictive modeling as they work on a large class of problems 
+and do not require fine parameter setting.
+However, in general learning algorithms do require the specification of
 parameters, the values of which will impact the quality of the results.
-These parameters may be specified based on domain specific knowledge, or
-requirements, determined using an analytical approach, or optimized using
-cross validation. In latter case a nest cross-validation scheme is
-required to avoid biasing resultant measures of prediction accuracy.
-
-Determining the subset of features most relevant to the model (feature
-selection) is essential for interpreting the models. In cases were model
-weights can be directly mapped to their corresponding feature, there is
-typically no statistical framework for thresholding these weights, and
-meaningless features are not always set to zero (this is particularly the
-case for $\ell_2$ regularized algorithms such as SVM and ridge
-regression). One feature selection strategy is to filter out features
+These parameters may be specified based on domain specific knowledge,
+determined using an analytical approach, or set using
+cross validation to optimize the prediction accuracy. In latter case 
+to avoid biasing measures of prediction accuracy, a
+nested cross-validation scheme \cite{pereira2009} is required, assessing 
+prediction on left-out data not used to set the parameters.
+%
+Selecting features most relevant to the model can help prediction
+accuracy and model interpretation \cite{pereira2009}. One feature selection strategy is 
+to filter out features
 based on their statistical relationship with the variable of interest
@@
 information, they may exclude features that would be important to the
-model.
-
-% XXX: mention nested cross-val for feature selection above
+model. Note that feature selection must be performed inside the
+cross-validation loop, \emph{i.e.}\ on the train data, excluding the test
+data.
 
 % Importance and caveats of interpretation
-
-% XXX: distinguish linear from non-linear classifiers. Explain that a
-% linear classifier is nothing more than a fancy linear regression
 
@@
 relates to a continuous variable is more complicated, particularly given
-the multivariate nature of their involvement.  For classification methods
+the multivariate nature of their involvement\footnote{Note that there is
+typically no statistical framework for thresholding these weights, and
+meaningless features are not always set to zero (this is particularly the
+case for $\ell_2$ regularized algorithms such as SVM and ridge
+regression)}. For classification methods
 such as Fisher's linear discriminant analysis (LDA), which maximally

### 2013-01-01 paper.tex
iter

@@
 Selecting features most relevant to the model can help prediction
-accuracy and model interpretation \cite{pereira2009}. One feature selection strategy is 
+accuracy and model interpretation \cite{pereira2009}; for instance with a
+functional connectome by highlighting the connections that underpin the
+prediction. One feature selection strategy is 
 to filter out features
@@
 predictive models is used to identify the most relevant features that are
-later tested in followon experiments better suited to elucidating their
+later tested in follow-up experiments better suited to elucidating their
 relationship to the variable of interest.

### 2013-01-01 paper.tex
iter

@@
 underlying the modeling approach. For linear classifiers, 
-classifier weights are similar to the weights of a ordinary regression.
+classifier weights are similar to the weights of a ordinary linear regression.
 If features are appropriately
@@
 interpreted to reflect the relative importance of the feature to the
-model, but interpreting how the feature differs between classes or
-relates to a continuous variable is more complicated, particularly given
+model. However, interpreting how the feature differs between classes or
+relates to a continuous variable can be more complicated given
 the multivariate nature of their involvement\footnote{Note that there is
@@
 relationship to the variable of interest.
+
+To conclude on predictive modeling with a practical note for connectome
+comparison, we would like to stress that, while machine learning
+algorithms are powerful tools, they work best if they are provided with
+discriminant and noiseless features. In other words, as with all other
+connectome comparison methods, optimizing first-level analysis
+--subject-level connectome extraction-- is paramount.
 

### 2013-01-01 paper.tex
iter

@@
 % Neuroimage-like layout
-\documentclass[5p]{elsarticle}
+%\documentclass[5p]{elsarticle}
 % For kindle
-%\documentclass[1p,12pt]{elsarticle}
-%\usepackage{geometry}
-%\geometry{a6paper,hmargin={.2cm,.2cm},vmargin={1cm,1cm}}
+\documentclass[1p,12pt]{elsarticle}
+\usepackage{geometry}
+\geometry{a6paper,hmargin={.2cm,.2cm},vmargin={1cm,1cm}}
 % End kindle
@@
 connectivity is an essential part of the description of brain function,
-complementary to the localizationist picture emerging from the systematic
+that complements the localizationist picture emerging from the systematic
 mapping of regions recruited in tasks. However, while there exists a
@@
 lead to controlled and powerful inter-subject comparisons. The paper is
-focused on functional connectomes, in contrast to structural connectomes,
+focused on functional connectomes in contrast to structural connectomes,
 as the inference of functional connectivity from fluctuations in the
@@
 matrix tabulating the connection weights between each pair of nodes.
-Functional-connectivity graphs can be used to represent evoked activity,
+Functional-connectivity graphs are used to represent evoked activity,
 as in task-response studies \cite{mcintosh2000}, as well as
@@
 
-The choice of regions of interests (ROIs) that defines the nodes of the
+The choice of regions of interests (ROIs) that define the nodes of the
 graphs can be very important both in the estimation of connectomes and
@@
 full-brain parcellations \cite{craddock2011, bellec2010, yeo2011,
-thirion2006}, and have been shown to extract well-known functional
+thirion2006}, and have been shown to segment well-known functional
 structures from rest data. Alternatively, decompositions
@@
 essence they all strive to extract simple statistics from functional
-imaging to characterize synchrony and communication between large
+imaging in order to characterize synchrony and communication between large
 ensembles of neurons. Here we choose to focus on second order statistics
@@
 \emph{evoked} activity with task-driven studies it can be beneficial to
-run a first-level analysis, enforcing specificity of the measure
+run a GLM-based first-level analysis, enforcing specificity of the measure
 extracted to the task. With slow event-related designs, task-specific
@@
 Different inverse-covariance matrices estimates corresponding to
-Fig.\,\ref{fig:correlation_matrices} -- \textbf{Left}: group-sparse estimate
+fig.\,\ref{fig:correlation_matrices} -- \textbf{Left}: group-sparse estimate
 using the $\ell_{21}$ estimator \cite{varoquaux2010c}.
@@
 \cite{marrelec2006a}. In the small sample limit, this removal is
-challenging from the statistical standpoint, and assumption of sparsity,
+challenging from the statistical standpoint, and an assumption of sparsity,
 \emph{i.e.}\ that only few variables need to be considered at a time, is
@@
 are necessary because estimation noise creates a background structure
-(see Fig.\,\ref{fig:icov_estimators}); however, unlike in a univariate situation, the
+(see fig.\,\ref{fig:icov_estimators}); however, unlike in a univariate situation, the
 parameters are not independent, and the spurious background connections
@@
 contain a lot of information on the functional structure of the brain.
-First, the correlation matrix (Fig.\,\ref{fig:correlation_matrices})
+First, the correlation matrix (fig.\,\ref{fig:correlation_matrices})
 shows blocks of coactivating regions that can be interpreted as
@@
 inverse-covariance matrix, can be represented as graphs: nodes connected
-by weighted edges (inserts on Fig.\,\ref{fig:correlation_matrices} and
-Fig.\,\ref{fig:icov_estimators}). The inverse-covariance matrix,
+by weighted edges (inserts on fig.\,\ref{fig:correlation_matrices} and
+fig.\,\ref{fig:icov_estimators}). The inverse-covariance matrix,
 capturing partial correlations, appears then as extracting a
-\emph{backbone} or \emph{core} of the graph. While such structure have
+\emph{backbone} or \emph{core} of the graph. While such structure has
 been used as a way to summarize anatomical brain connectivity graphs
-\cite{hagmann2008}, here they have a clear-cut meaning with regards to
-the BOLD signal: they give the conditional independence structure between
+\cite{hagmann2008}, here it has a clear-cut meaning with regards to
+the BOLD signal: it gives the conditional independence structure between
 the regions \cite{varoquaux2012}. In other words, regions $a$ and $b$ are
@@
 correlations than with correlations. Indeed, while with
-correlation matrices regressing out the global mean has a drastic
-(Fig.\,\ref{fig:correlation_matrices} upper right and lower right), on
+correlation matrices regressing out the global mean has a drastic effect
+(fig.\,\ref{fig:correlation_matrices} upper right and lower right), on
 inverse covariance it only changes very slightly the resulting matrices
-(Fig.\,\ref{fig:icov_regressors}). There have been debates on whether to
+(fig.\,\ref{fig:icov_regressors}). There have been debates on whether to
 regress out certain signals, such as the global mean,  as it induces
@@
 
-In this section, we consider the problem of comparing functional
+We now turn to the problem of comparing functional
 connectivity across subjects or across conditions.
@@
 \url{http://en.wikipedia.org/wiki/Fisher_transformation} or
-\cite{anderson1958}, section 4.2.3 for mathematical arguments} to the
+\cite{anderson1958} section 4.2.3 for mathematical arguments.} to the
 correlations. Note that
@@
 number of regions used. Controlling for the false discovery rate (FDR)
-mitigates this problem. Alternatively, as the assumption underlying the
+mitigates this problem. Alternatively, as the assumptions underlying the
 Benjamini-Hochberg procedure \cite{benjamini1995} for the FDR can easily
-be broken, non-parametric permutations-based approaches give reliable
+be broken, non-parametric permutations-based tests give reliable
 approaches. In particular, the max-T procedure \cite{ge2003,nichols2001}
@@
 \caption{Inter subject variability. Note that this is variability
-occurring in a healthy population at rest, in other words non specific
+occurring in a healthy population at rest, in other words it is non specific
 variability -- \textbf{a}: single-subject
@@
 as more or less connected across subjects (see for instance
-Fig.\,\ref{fig:inter_subject}.a, showing variability in a control
+fig.\,\ref{fig:inter_subject}.a, showing variability in a control
 population at rest). In other words, non-specific variability is
@@
 signals, while using the integration tells us how much two signals can be
-combined to form the third (see Fig.\,\ref{fig:integration}). 
+combined to form the third (see fig.\,\ref{fig:integration}). 
 Cross-entropy --or mutual information--
 \cite{marrelec2008} measures the amount of cross-talk between two
-systems in a similar way as Gaussian entropy to used to measure the
+systems in a similar way as Gaussian entropy is used to measure the
 integration of a brain
@@
 topological properties\footnote{In the neuroscience world, these
-descriptions are group under the terms of ``graph theoretical
+descriptions are grouped under the terms of ``graph theoretical
 approaches'', however graph theory is an entire division of mathematics
@@
 Predictive modeling is concerned with learning (or fitting) a model to
-draw conclusions on new and unseen data \cite{pereira2009}. Typically on
+draw conclusions on new and unseen data \cite{pereira2009}. Typically, on
 brain imaging data, it opens the door to learning diagnosis or prognosis
 markers \cite{stonnington2010}. However, beyond the practical use of
-prediction, these models can also be useful to uncover mechanism of brain
+prediction, these models can also be useful to uncover mechanisms of brain
 function \cite{norman2006}. Both the fact that information \emph{can} be
-drawn to generalize predictions to new data and \emph{how} or
+used to make predictions on new data, and \emph{how} it is used or
 \emph{where} it lies informs us on brain function. Multivariate
@@
 are attractive in connectomics because they are sensitive to dependencies
-between features and avoid the need to correct for multiple comparisons
+between features and avoid the curse of multiple comparisons
 since the significance of an entire pattern is evaluated using a single
@@
 Support vector machines\footnote{See \cite{kloppel2008}
-for a gentle introduction to support vector machines.} (classification and regression) are popular
+for a gentle introduction to support vector machines.} are popular
 algorithms for predictive modeling as they work on a large class of problems 
@@
 determined using an analytical approach, or set using
-cross validation to optimize the prediction accuracy. In latter case 
+cross validation to optimize the prediction accuracy. In latter case, 
 to avoid biasing measures of prediction accuracy, a
@@
 To conclude on predictive modeling with a practical note for connectome
-comparison, we would like to stress that, while machine learning
+comparison, we would like to stress that while machine learning
 algorithms are powerful tools, they work best if they are provided with
@@
 
-A first step to move from purely descriptive statistics to modeling with
+A first step to move from purely descriptive statistics to interaction
+models with
 functional connectivity analysis is to consider a correlation matrix as a
@@
 correlations are a measure of influence from one node to another, albeit
-undirected. Inferring direction in a Gaussian model is impossible. Linear
+undirected. Inferring directionality in a Gaussian model is impossible. Linear
 structural equation models (SEMs) \cite{mcintosh1994} rely on a similar
@@
 data. While injecting prior information can help model estimation, the
-more informative this prior the more fragile the inference becomes. The
+more informative this prior is, the more fragile the inference becomes. The
 ongoing debate on the impact of hemodynamic lag on Granger-causality
@@
 are to be preferred. For more hypothesis-driven studies, such as the
-analysis of the mechanism underlying a specific task, more complex models
+analysis of the mechanisms underlying a specific task, more complex models
 can be preferred, if rich data is available. Automatic choice of model is
@@
 \cite{varoquaux2010c,craddock2011,strother2006}) is a useful tool. The
-central principle of cross-validation is to learn (or fit) a model, and
-then test its predictive power on unseen data. Models too complex
+central principle of cross-validation is to test a model on different
+data than the data used to fit the model. Models too complex
 for the data available will fit noise in the data, and thus generalize

### 2013-01-01 paper.tex
remove kindle formatting
Progress on abstract

@@
 \begin{abstract}
-    We are the champion... of the world
+    Functional connectomes capture brain interactions via 
+    fluctuations in brain imaging signal. On rest data they map
+    the intrinsic functional architecture of the brain and with
+    task-driven experiments they represent the integration mechanisms
+    between specialized brain areas. Analysis of their variability 
+    across subjects and conditions can reveal markers of brain
+    pathologies and cognitive mechanisms. However, connectomes are
+    complex multivariate objects. The methodology to estimate them from
+    the functional signal, and to compare them is still...
 

### 2013-01-01 paper.tex
iter
Abstract somewhat done

@@
     pathologies and cognitive mechanisms. However, connectomes are
-    complex multivariate objects. The methodology to estimate them from
-    the functional signal, and to compare them is still...
-
-    Scope: rest and task-based studies. But focusing on fMRI.
+    complex multivariate objects. Methods to estimate them 
+    from the functional signal have undergone rapid developments.
+    The literature is full of diverse strategies to compare them.
+    This paper aims to clarify some links across functional-connectivity
+    methods and expose different steps to perform a group study on
+    functional connectomes.
 \end{abstract}

### 2013-01-01 paper.tex
start intro

@@
 
-Horwitz \emph{el al.}\ \cite{horwitz1995} mentioned almost 20 years ago
+Horwitz \emph{el al.}\ \cite{horwitz1995} claimed almost 20 years ago
 that ``the crucial concept needed for network analysis is covariance''.
+In our eyes, this still holds today. Estimation of noiseless functional
+connectomes relies largely on fitting covariance models.
 

### 2013-01-01 paper.tex
Progress on conclusion

@@
 that ``the crucial concept needed for network analysis is covariance''.
-In our eyes, this still holds today. Estimation of noiseless functional
-connectomes relies largely on fitting covariance models.
+In our eyes, this still holds today. Estimation functional connectomes
+relies largely on fitting covariance models. Their comparison requires
+understanding how these covariances vary and finding metrics to capture
+this variability. Additionally, a secret ingredient to all statistical
+steps is a good choice of confounds.
+
+% XXX add here a bit more of connectome stuff. Be optimistic!
+% Look to the future: note that estimation of connectomes with many nodes
+% is more challenging than small connectomes, but that better apriori and
+% better algorithms will push these limits further.
+
+Reviewing methodological options to learn and compare connectomes
+highlights that there is currently no unique solution, but a spectrum of
+related methods and analysis strategies. More empirical results are
+required to guide the choices, however this diversity is probably
+unavoidable: a diffuse disease like schizophrenia will not lead to the
+same connectome modifications as a focal lesion. In statistical learning,
+``no free lunch'' theorems \cite{wolpert1996} tell us that no strategy
+can perform uniformly better in all situations. In practice, the key to a
+successful analysis is to understand well the assumptions and
+interpretation of each option, in order to match the method to the
+research question.
 

### 2013-01-01 paper.tex
Progress on conclusion

@@
 steps is a good choice of confounds.
-
-% XXX add here a bit more of connectome stuff. Be optimistic!
-% Look to the future: note that estimation of connectomes with many nodes
-% is more challenging than small connectomes, but that better apriori and
-% better algorithms will push these limits further.
+% XXX: more practical advice?
+
+Methodological challenges to functional-connectome-based group studies
+arise from the dimensionality and the of variability the connectome. With
+the current tools, inter-subject comparison of connectomes comprising
+many nodes is limited by the difficulty of estimating high-dimensional
+covariance matrices and the loss of statistical power due to multiple
+comparisons. Better algorithms integrating powerful a priori is required
+to push the limits of covariance estimation. Better characterization of
+inter-subject variability of connectomes \cite{kelly2012} will help
+choosing parameterizations and invariants to avoid testing each edge for
+a difference, as it inevitably leads to a needle in a haystack problem.
 
@@
 interpretation of each option, in order to match the method to the
-research question.
+question.
 

### 2013-01-01 paper.tex
iter

@@
     fluctuations in brain imaging signal. On rest data they map
-    the intrinsic functional architecture of the brain and with
+    the intrinsic functional architecture of the brain. With
     task-driven experiments they represent the integration mechanisms

### 2013-01-01 paper.tex
iter

@@
 understanding how these covariances vary and finding metrics to capture
-this variability. Additionally, a secret ingredient to all statistical
-steps is a good choice of confounds.
-% XXX: more practical advice?
+this variability. The additional secret ingredient may be a good choice
+of confounds in all statistical steps. A good choice of a small number of
+relevant regions facilitates connectome comparison. However, such a
+choice cannot yet be fully factored out via methods and must rely on
+neuroscientific expertise.
 
@@
 covariance matrices and the loss of statistical power due to multiple
-comparisons. Better algorithms integrating powerful a priori is required
+comparisons. Better algorithms integrating powerful a priori are required
 to push the limits of covariance estimation. Better characterization of
@@
 choosing parameterizations and invariants to avoid testing each edge for
-a difference, as it inevitably leads to a needle in a haystack problem.
+a difference, as this strategy inevitably leads to a needle in a haystack
+problem.
 
@@
 related methods and analysis strategies. More empirical results are
-required to guide the choices, however this diversity is probably
+required to guide the choices. However this diversity is probably
 unavoidable: a diffuse disease like schizophrenia will not lead to the

### 2013-01-02 paper.tex
iter

@@
 % General introduction
-Functional connectivity captures the synchronization of distant
+Functional connectivity reveals the synchronization of distant
 neural systems via correlations in brain activity
@@
 understanding how these covariances vary and finding metrics to capture
-this variability. The additional secret ingredient may be a good choice
-of confounds in all statistical steps. A good choice of a small number of
+this variability. The additional secret ingredient may be using  
+confounds regressors in all statistical steps. A good choice of a small number of
 relevant regions facilitates connectome comparison. However, such a

### 2013-01-03 paper.tex
comments and changes on latest from varoquaux branch

@@
 neural systems via correlations in brain activity
-\cite{biswal1995,cordes2000}. Given that high-level
+% CAMERON change cordes 2000 to Friston 1993
+\cite{biswal1995,cordes2000}.
+% CAMERON would probably include citation to connectome in next sentence.
+Given that high-level
 function emerges from the interaction of specialized units, functional
@@
 group-level analysis of functional connectivity still faces many open
-methodological challenges. Giving a picture of a single subject's 
+methodological challenges. Deriving a picture of a single subject's 
 functional connectivity is by itself not straightforward, as the brain
 comprises a myriad of interacting subsystems and its connectivity must 
-be decomposed in
+be decomposed into
 simplified and synthetic representations. An important view of brain
@@
 focused on functional connectomes in contrast to structural connectomes,
-as the inference of functional connectivity from fluctuations in the
-signal implies important specificities in the statistical modeling. While 
+as the inference of functional connectivity from (hemodynamic?, BOLD?) fluctuations 
+% CAMERON the sentence "implies important specificities in the statical modeling"
+% is a little odd
+implies important specificities in the statistical modeling. While 
 the notion of functional
@@
 representing functional interactions in the brain, where the term
-``graph'' is taken in its mathematical sens: a set of \emph{nodes}
-connected together by \emph{edges}. A graph can be weighted or not, and
+``graph'' is taken in its mathematical sense: a set of \emph{nodes}
+connected together by \emph{edges}. 
+% CAMERON I would define nodes and edges here, I like the Varela definitions
+% where a node represents a local network of cells, typically < 1 cm^3
+% in volume in which synchronization is achieved via biochemical processes
+% and edges represent long range interactions synchronized via fibers
+A graph can be weighted or not, and
 is completely equivalent to its \emph{adjacency matrix}, a symmetric
@@
 shown that extracting signal from ROIs that did not match functional
-units would lead to incorrect graphs estimated \cite{smith2011}.
+units would lead to erronous graph estimation \cite{smith2011}.
 %
 Different strategies to define suitable ROIs coexist. While dense parcellations approaches cover
+% CAMERON what about all the other clustering people Flandin, Poline, Bellec, ...
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
@@
 regions, in favor of increased functional specificity and thus better
+% CAMERON I think that this reference to Fair should be Dosenbach
 differentiation across networks \cite{greicius2003, fair2009,
@@
 probabilistic atlases, or spatial maps of functional networks extracted
+% CAMERON: cite Smith, Kivinimi, maybe Yeo
 from techniques such as independent component analysis (ICA).
@@
 % XXX: discuss tradeoffs in the number of regions
+% CAMERON TODO
 
@@
 Atlases can be used to define full-brain parcellations. The most popular
+% CAMERON I would avoid using such statements, in my readings HO is much
+% more popular, also the Talaraich Atlas is commonly used, I would include
+% all of these
 choice is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
@@
 fig.\,\ref{fig:parcellations}).
+% CAMERON my paper directly shows the inadequacy of AAL, TT, HO and EZ for
+% representing functional connectivity
 
@@
 useful to study connectivity in task-specific networks
+% CAMERON include citation to Dosenbach, and some others
 \cite{grillon2012}. The common practice is to place balls of a given
@@
 adapts to the signal at hand and its limitations, such as
+% CAMERON I don't think that EPI was ever defined or even need be
 EPI-specific warps or vascular and movement artifacts that are isolated
@@
 techniques leads to contrasted maps that outline many different
-structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
+structures \cite{craddock2011, varoquaux2012} (see fig.\,\ref{fig:parcellations}).
 
@@
 different choices of confound regressors -- 
+% CAMERON = using CompCor in addition to WM and CSF is redundant as 
+% CompCor involves a PCA decomposition of WM and CSF
 \textbf{Left}: regressing out CompCor signals, as well as white matter and
@@
 \paragraph{Signal extraction}
-%
+% CAMERON = I think we should differentiate between signal extraction and
+% signal cleaning, actually the cleaning is a seperate issue, that is independent
+% of the regions or nodes.
+Given graph nodes, the next step 
 Given ROIs, the next step is to extract from them a summary measure. To
@@
 multiple GLMs to optimize deconvolution of each trial \cite{mumford2012}.
+% CAMERON it is important to regress movement and other stuff from 
+% REST and TASK, just not done in task
 With rest datasets, it is important to regress out time series capturing
@@
 parameters estimated during preprocessing, removing linear trends, signal
+% CAMERON WM and CSF are "negative controls" and represent thermal noise, 
+% systematic variation due to multichannel head coils, cardiac and resp.
+% smaller motions, physiological noise correction, spatial varying WM noise
+% GLOBAL MEAN IS A HUGE CONTROVERSY
 extracted from the white matter and the CSF \cite{chang2009}, as well as
@@
 
+% CAMERON, this is just as important for task btw ...
 Finally, it is important to keep in mind that using resting-state to
@@
 weighted by the subject-specific gray matter probabilistic segmentation,
+% CAMERON why only SPM's tool?
 as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
 
+% CAMERON TODO: two sentences max
 % Regressing out task?? Skipping for lack of space
@@
 %
+% CAMERON might want to pull this back to graph edges
 Functional connectivity between the ROIs can be measured by computing the
@@
 \emph{i.e.}\ the correlation matrix of the data-generating process. If the
+% CAMERON THIS IS ALSO DETERMINED BY TEMPORAL AUTOCORRELATIONS! band-limited
+% by hemodynamic response, low sampling frequency
 number of measurements was infinite, the two would coincide, however if
@@
 which, sparse inverse covariance estimators have been found to be
+% CAMERON Isn't there a paper from Stanford about this as well??
 efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
@@
 matrix captures the amplitude of a signal, via its variance, while a
-correlation matrix is computed on normalized signals.}
+correlation matrix is computed on standardized (zero mean, unit variance) signals.}
 matrix captures
@@
 make a compromise between imposing simpler models, \emph{i.e.}\ with less
+% CAMERON "fitting well the data" needs to be fixed
 connections, and fitting well the data. This compromise is set via a
@@
 \cite{varoquaux2010c}.
+
+% CAMERON should you discuss limitations to the L1 norm, such as bounding
+% the number of non-zero weights by the number of observations: does this
+% only apply to regressions?
 
@@
 large-scale functional networks, such as the default mode network. Note
+% CAMERON How about spectral reordering?
 that the split in networks is not straightforward. Different ordering of the
-nodes will reveal different networks. Indeed, because of the presence of
+nodes will reveal different networks. 
+% CAMERON I don't get this sentence
+Indeed, because of the presence of
 hubs and interleaved networks, the picture in terms of segregated networks
 is not sufficient to explain full-brain connectivity
-\cite{varoquaux2012}. The connectivity matrices, correlation matrix or
-inverse-covariance matrix, can be represented as graphs: nodes connected
+\cite{varoquaux2012}. Connectivity matrices, correlation matrices and
+inverse-covariance matrices, can be represented as graphs: nodes connected
 by weighted edges (inserts on fig.\,\ref{fig:correlation_matrices} and
-fig.\,\ref{fig:icov_estimators}). The inverse-covariance matrix,
-capturing partial correlations, appears then as extracting a
-\emph{backbone} or \emph{core} of the graph. While such structure has
+fig.\,\ref{fig:icov_estimators}). The inverse-covariance matrix, which
+captures partial correlations, appears then as extracting a
+\emph{backbone} or \emph{core} of the graph.
+% CAMERON This is a really long sentence
+While such structure has
 been used as a way to summarize anatomical brain connectivity graphs
 \cite{hagmann2008}, here it has a clear-cut meaning with regards to
+% CAMERON BOLD not explicitly defined
 the BOLD signal: it gives the conditional independence structure between
-the regions \cite{varoquaux2012}. In other words, regions $a$ and $b$ are
+regions \cite{varoquaux2012}. In other words, regions $a$ and $b$ are
 not connected if the signal that they have in common can be explained by
@@
 inverse covariance it only changes very slightly the resulting matrices
-(fig.\,\ref{fig:icov_regressors}). There have been debates on whether to
+(fig.\,\ref{fig:icov_regressors}). 
+% CAMERON I would move this to preprocessing section
+There have been debates on whether to
 regress out certain signals, such as the global mean,  as it induces
 negative correlations \cite{murphy2009,chang2009,fox2009}, and these may seem
+% CAMERON "doing the opposite of the other" is a bit odd
 surprising: one network is doing the opposite of the other. However,
@@
 %
+% CAMERON there has to be other references ...
 The most natural approach is to apply a linear model to each coefficient of
@@
 
+% CAMERON what about CWAS or Bellec??
+
 %{{{------ Inter subject fluctuations ----------------------------------------
@@
 correlations are intrinsically harder to estimate. Preliminary work
-\cite{varoquaux2010b} suggests to perform statistics on residuals of
+\cite{varoquaux2010b} suggests performing statistical tests on residuals of
 a parametrization intermediate between correlation matrix and inverse
@@
 that lies in a network of strongly connected nodes, the whole network is
-likely to cary an effect. Thus, they adapt cluster-level inference to
+likely to carry an effect. Thus, they adapt cluster-level inference to
 connectivity analysis, in order to mitigate the curse of multiple
@@
 possible strategy to circumvent these difficulties is to perform
-comparison and statistical testing at the level of the network, rather
+comparisons and statistical testing at the level of the network, rather
 than the individual connection.
@@
 random graphs.} that are characteristic of small-word networks
+% CAMERON should cite dani basset
 \cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
@@
 small number of connections, any two regions of the brain are well
-connected. Another interesting consequence of their specific topology is
+connected. 
+% CAMERON cite first small world network science paper
+Another interesting consequence of their specific topology is
 the resilience it gives the system to attacks such as resulting from
@@
 beyond empirical correlation matrices, as discuss in the previous section.
+% CAMERON What about regional summary measures such as centrality??? Xinian's work
+% maybe a paragraph on these ReHo, degree centrality, eigenvector centrality, pagerank etc...
 
@@
 
-Predictive modeling is concerned with learning (or fitting) a model to
-draw conclusions on new and unseen data \cite{pereira2009}. Typically, on
-brain imaging data, it opens the door to learning diagnosis or prognosis
-markers \cite{stonnington2010}. However, beyond the practical use of
-prediction, these models can also be useful to uncover mechanisms of brain
-function \cite{norman2006}. Both the fact that information \emph{can} be
-used to make predictions on new data, and \emph{how} it is used or
-\emph{where} it lies informs us on brain function. Multivariate
-predictive models
-are attractive in connectomics because they are sensitive to dependencies
-between features and avoid the curse of multiple comparisons
-since the significance of an entire pattern is evaluated using a single
-statistical test. From the perspective of medical applications, using
+% Importance and caveats of interpretation
+
+Predictive modeling is concerned with learning (or fitting) a model that is
+capable of decoding or \emph{predicting} information from new unseen data \cite{pereira2009}.
+In the context of connectomes, predictive modeling provides a means for
+delineating connectivity based biomarkers of disease diagnosis, 
+prognosis, or other phenotypic outcomes \cite{craddock2009, dosenbach2010}. The accuracy
+of a predictive model provides a measure of the amount of information present
+in the connectome about the phenotypic measure being evaluated [kriegeskorte, Kjems]. 
+When combined with reproducibility, prediction accuracy provides a metric for
+evaluating experimental tradeoffs for data acquisition, preprocessing, and analysis 
+[Strother, LaConte].  Multivariate predictive models are attractive in connectomics 
+because they are sensitive to dependencies between features and avoid the need to correct
+for  multiple comparisons since the significance of an entire pattern is evaluated 
+using a single statistical test. From the perspective of medical applications, using
 resting-state connectivity as a biomarker is particularly appealing as it
@@
 \cite{richiardi2011,shirer2012}.
+% CAMERON something about the ADHD200 Global Competition highlights the
+% interest/need for predictive modeling in connectomics as well
+% as the number of approaches applicable 
+Recent work has illustrated the
+utility of predictive modeling for deriving connectivity models at the
+individual level [Chu 2010, Craddock in press or HBM].
+
+Both the fact that information \emph{can} be
+used to make predictions on new data, and \emph{how} it is used or
+\emph{where} it lies informs us on brain function.
 
 % A bit of technical details
-
+% technical details
 Technically, predictive modeling is a supervised machine learning problem
@@
 %
-The prediction accuracy of a model for predicting the target variable
-provides a natural means for evaluating the utility of the model as a
-biomarker, but also its explanatory power for the mechanism under study.
-%
-This prediction accuracy is measured using one or more iterations of
-cross validation, which involves training and testing phases
-\cite{pereira2009}. Cross validation cycles separate the
-available data into two independent subsets: training data and testing
-data.  Training involves learning a predictive model from the training
-data. During testing the model is applied to the testing data to predict
-corresponding values of the target variable.  Prediction accuracy is then
-assessed by comparing these predictions to the observed values of the
-target variable.
-
-Support vector machines\footnote{See \cite{kloppel2008}
-for a gentle introduction to support vector machines.} are popular
-algorithms for predictive modeling as they work on a large class of problems 
-and do not require fine parameter setting.
-However, in general learning algorithms do require the specification of
-parameters, the values of which will impact the quality of the results.
-These parameters may be specified based on domain specific knowledge,
-determined using an analytical approach, or set using
-cross validation to optimize the prediction accuracy. In latter case, 
-to avoid biasing measures of prediction accuracy, a
-nested cross-validation scheme \cite{pereira2009} is required, assessing 
-prediction on left-out data not used to set the parameters.
-%
-Selecting features most relevant to the model can help prediction
-accuracy and model interpretation \cite{pereira2009}; for instance with a
-functional connectome by highlighting the connections that underpin the
-prediction. One feature selection strategy is 
-to filter out features
-based on their statistical relationship with the variable of interest
-using a univariate statistical criterion such as t-test, Pearson's
-correlation, or mutual information.  A drawback of this approach is that
-since the filters are typically insensitive to multivariate
-information, they may exclude features that would be important to the
-model. Note that feature selection must be performed inside the
-cross-validation loop, \emph{i.e.}\ on the train data, excluding the test
-data.
-
-% Importance and caveats of interpretation
-
-The interpretation of the predictive model can be complicated and
-requires insight into the mechanisms
-underlying the modeling approach. For linear classifiers, 
-classifier weights are similar to the weights of a ordinary linear regression.
-If features are appropriately
-standardized prior to training, the magnitude of weights can be
-interpreted to reflect the relative importance of the feature to the
-model. However, interpreting how the feature differs between classes or
-relates to a continuous variable can be more complicated given
-the multivariate nature of their involvement\footnote{Note that there is
-typically no statistical framework for thresholding these weights, and
-meaningless features are not always set to zero (this is particularly the
-case for $\ell_2$ regularized algorithms such as SVM and ridge
-regression)}. For classification methods
-such as Fisher's linear discriminant analysis (LDA), which maximally
-separates class means given their standard deviation, feature weights are
-representative of the differences between class means. For support vector
-classification, classifier weights are derived from observations that are
-the most similar between classes, and hence represents the border between
-classes. To draw conclusions on the features used for prediction, it is
-perhaps most reasonable to adapt a conservative interpretation in which
-predictive models is used to identify the most relevant features that are
-later tested in follow-up experiments better suited to elucidating their
-relationship to the variable of interest.
+The quality of a predictive model is determined by its prediction accuracy (or
+generalization ability) which is measured using one or more iterations of
+cross-validation. Cross-validation begins by seperating the available data into
+independent training and testing subsets.  A predictive model is learned from
+the training data and applied to the testing data to predict corresponding
+values of the target variable. Prediction accuracy is then assessed by comparing
+these predictions to the observed value of the target variable. This procedure
+can be iterated several times for different splits of the data and averaged to
+form a single measure of prediction accuracy.  One of the most important
+parameters for cross validation is the manner in which data are subdivided.
+There are several strategies for constructing the training dataset ranging from
+using all but one observations (leave-one-out cross-validation), using a
+fraction of the observations (k-fold cross validation; kfcv), to resampling the
+observations with replacement (boostrap cross-validation, bscv). Although loocv
+has been popular in neuroimaging applications of MVPA since it makes the largest
+amount of data available for training, its estimates are more variable than kfcv
+or bscv [tibs, book]. Split-half cross validation (two-fold cross validation,
+2fcv), minimizes the estimation variance, at the cost of using less training
+data, and also permits the simultaneous estimation of model reproducibility
+using the NPAIRs framework []. Bootstrap cross-validation minimizes estimation
+variance while maximising the amount of data available for training at the cost
+of introducing bias. This bias is due to the fact that on average 63.2\percent
+of the testing data overlaps with the training data, the .632\plus bootstrap
+corrects for this bias.  No matter which cross validation scheme is used, the
+accurate estimation of generalization ability requires that the testing data and
+training data are independent and identically distributied (iid). The meaning of
+independence here depends on the context in which the predictive model will be
+applied. For example, if observations correspond to subjects, then testing with
+scans acquired from the same subject, even acquired at different points in time,
+will introduce bias. If observations are different time points for the same
+subject, with the goal of testing whether the model can predict a later time
+point for that subject, then scans acquired from a later time point for that
+subject may be used for testing as long as enough time has passed to account for
+temporal autocorrelation.
+
+Another important parameter for estimating generalization ability is the error
+term employed. For classification problems error can be simply measured as a '1'
+if the prediction is correct and a '0' if it is incorrect, alternatively
+misclassifications for some groups may be weighted higher then others.  Log-loss
+or the negative log-likelihood can be used if class probabilities are outputed
+rather than simply class membership. For regression problems, common loss
+functions are the correlation or mean squared error between predicted and true
+target values. The former is preferred in cases when differences in scale and
+shift are less important then the relative ordering of the output values.
+Mean-squared error is preferred when the target variable has units and
+penalizing a model for shift or scale differences is important.
+
+After generalization ability (or error) has been estimated it is compared to
+what would be acheived by ``chance'' in order to estimate its significance. In
+the case of classification problems, the likelihood of obtaining a
+generalization accuracy by change can be estimated from a multinomial
+distribution [].  Alternatively, a permutation test can be performed in which
+the target labels are randomly permuted several times and the cross-validation
+error is estimated using each of the permutations. Significance is the assessed
+from the fraction of permutations that obtained higher prediction accuracy then
+was obtained from the unpermuted model. This method has the advantage of being
+available for both classification and regression models with the caveat that any
+correlationl structure between observations must be preserved to avoid biased
+results. Null distributions can be constructed for non-independent data using
+block permutation or wavelet resampling. When statistical significance is
+measured in this manner, the entire pattern is test with a single statistical
+test and there is no need to correct for multiple comparisons (unless multiple
+patterns are evaluated).
+
+MVPA algorithms typically require the specification of several parameters, the
+values of which will impact the quality of the results. These parameters may be
+prespecified based on domain specific knowledge or requirements [cherkassky
+book], determined using an analytical approach [cherkassky], or optimized using
+cross validation [cherrkasky book, tibs book].  In the latter case a nested
+cross-validation scheme is required to avoid biasing resultant measures of
+prediction accuracy [cherkassky].  
+%
+Determining the subset of features most relevant to the model (feature
+selection) can improve prediction accuracy \footnote{This is not necessarily
+	true, it has been shown in very high dimensional datasets that feature
+	selection does not improve prediction accuracy[cite high dimensional
+	gene paper], whereas in other cases it does\cite{craddock2009}.} and is
+essential for interpreting the models. For connectivity analyses, feature
+selection involves highlighting the connections that underlie the obtained
+prediction.  In cases were model weights can be directly mapped to their
+corresponding feature, there is typically no statistical framework for
+thresholding these weights, and meaningless features are not always set to zero
+\footnote{This is particularly the case for $\ell_2$ regularized algorithms such
+	as support vector machines and ridge regression}. One strategy is to
+filter out features based on their statistical relationship with the variable of
+interest using a univariate statistical criterion such as t-test, Pearson's
+correlation, or mutual information [guyon].  A drawback of this approach is that
+since the filters are typically insensitive to multivaratiate information, they
+may exclude features that would be important to the model [guyon]. Another
+approach is to treat feature selection as a model selection problem in which
+case the optimal feature subset is chosen based on cross validation based
+measures of prediction performance [] or a measure of their stability[].  A
+third approach are to use sparse modeling methods such as L1 SVM or LASSO that
+force weights for non-essential features to be zero [tibs,??]. Although ideal,
+these methods may have limits on the number of non-zero weights used in the
+model or the exclusion of highly correlated features from the model [elastic net
+paper].  Contrary to previous reports [Guyon 2002, Craddock 2009] no matter
+which feature selection strategy is employed, it must be performed with
+cross-validation to avoid biasing estimates of prediction accuracy [later
+Guyon].
+
+The interpretation of classifier weights for selected features, when available,
+is complicated and requires insight into the mechanisms underlying the modeling
+approach. If features are appropriately standardized prior to training, the
+magnitude of weights can be interpreted to reflect the relative importance of
+the feature to the model, but interpreting how the feature differs between
+classes or relates to a continuous variable is more complicated, particularly
+given the multivariate nature of their involvement.  For classification methods
+such as Fisher's linear discriminant analysis (LDA), which maximally seperates
+class means given their standard deviation, feature weights are representative
+of the differences between class means. For support vector classification,
+classifier weights are derived from observations that are the most similar
+between classes, and hence represents the border between classes.  It is perhaps
+most reasonable to adapt a conservative interpretation in which predictive
+modeling is used to identify candidate connections that are later tested in
+followon experiments better suited to elucidating their relationship to the
+variable of interest.
 
@@
 also expressed in \cite{mcintosh2010}).
+% CAMERON should we mention follow on discussion from the first brain 
+% connectivity meeting
 
@@
 covariance matrices and the loss of statistical power due to multiple
+% CAMERON = integrating powerfulr a priori information?
 comparisons. Better algorithms integrating powerful a priori are required
@@
 highlights that there is currently no unique solution, but a spectrum of
-related methods and analysis strategies. More empirical results are
+related methods and analytical strategies. More empirical results are
 required to guide the choices. However this diversity is probably

### 2013-01-03 paper.tex
Integrating part of cameron's changes

@@
 neural systems via correlations in brain activity
-% CAMERON change cordes 2000 to Friston 1993
-\cite{biswal1995,cordes2000}.
-% CAMERON would probably include citation to connectome in next sentence.
-Given that high-level
-function emerges from the interaction of specialized units, functional
+\cite{biswal1995,friston1993}. Given that high-level
+function emerges from the interaction of specialized units
+\cite{tononi1992}, functional
 connectivity is an essential part of the description of brain function,
 that complements the localizationist picture emerging from the systematic
-mapping of regions recruited in tasks. However, while there exists a
+mapping of regions recruited in tasks \cite{sporns2005,biswal2010}. However, while there exists a
 well-defined standard analysis framework for activation mapping that enables
@@
 focused on functional connectomes in contrast to structural connectomes,
-as the inference of functional connectivity from (hemodynamic?, BOLD?) fluctuations 
-% CAMERON the sentence "implies important specificities in the statical modeling"
-% is a little odd
-implies important specificities in the statistical modeling. While 
+as the inference of functional connectivity from observed brain activity
+fluctuations brings important specificities in the statistical modeling. While 
 the notion of functional
@@
 ``graph'' is taken in its mathematical sense: a set of \emph{nodes}
-connected together by \emph{edges}. 
-% CAMERON I would define nodes and edges here, I like the Varela definitions
-% where a node represents a local network of cells, typically < 1 cm^3
-% in volume in which synchronization is achieved via biochemical processes
-% and edges represent long range interactions synchronized via fibers
+connected together by \emph{edges}. Nodes are localized functional units
+and edges represent long range interactions synchronized via fibers.
 A graph can be weighted or not, and
@@
 Different strategies to define suitable ROIs coexist. While dense parcellations approaches cover
-% CAMERON what about all the other clustering people Flandin, Poline, Bellec, ...
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
-wang2009}, this coverage can be traded off to focus on some specific
+wang2009,bellec2006}, this coverage can be traded off to focus on some specific
 regions, in favor of increased functional specificity and thus better
-% CAMERON I think that this reference to Fair should be Dosenbach
-differentiation across networks \cite{greicius2003, fair2009,
+differentiation across networks \cite{greicius2003, dosenbach2010,
 varoquaux2010b}. In addition, while
@@
 probabilistic atlases, or spatial maps of functional networks extracted
-% CAMERON: cite Smith, Kivinimi, maybe Yeo
-from techniques such as independent component analysis (ICA).
-
-% XXX: discuss tradeoffs in the number of regions
-% CAMERON TODO
+from techniques such as independent component analysis (ICA)
+\cite{kiviniemi2009,smith2009}.
 
@@
 %
-Atlases can be used to define full-brain parcellations. The most popular
-% CAMERON I would avoid using such statements, in my readings HO is much
-% more popular, also the Talaraich Atlas is commonly used, I would include
-% all of these
-choice is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
+Atlases can be used to define full-brain parcellations. A popular
+is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
 benefits from an SPM toolbox. However, it suffers from major
@@
 that it focuses on labeling large anatomical structures and does not match
-functional layout --for instance only two regions describe the medial
+functional layout \cite{craddock2011} --for instance only two regions describe the medial
 part of the frontal lobe. Multi-subject probabilistic altases such as the
@@
 fig.\,\ref{fig:parcellations}).
-% CAMERON my paper directly shows the inadequacy of AAL, TT, HO and EZ for
-% representing functional connectivity
 
@@
 useful to study connectivity in task-specific networks
-% CAMERON include citation to Dosenbach, and some others
-\cite{grillon2012}. The common practice is to place balls of a given
+\cite{biswal1995,rissman2004,grillon2012}. The common practice is to place balls of a given
 radius, 5 or 10\,mm, centered at the coordinates of interest. Given that
@@
 adapts to the signal at hand and its limitations, such as
-% CAMERON I don't think that EPI was ever defined or even need be
 EPI-specific warps or vascular and movement artifacts that are isolated
@@
 different choices of confound regressors -- 
-% CAMERON = using CompCor in addition to WM and CSF is redundant as 
-% CompCor involves a PCA decomposition of WM and CSF
 \textbf{Left}: regressing out CompCor signals, as well as white matter and
@@
 
-\paragraph{Signal extraction}
-% CAMERON = I think we should differentiate between signal extraction and
-% signal cleaning, actually the cleaning is a seperate issue, that is independent
-% of the regions or nodes.
+\paragraph{Signal extraction and cleaning}
 Given graph nodes, the next step 
@@
 multiple GLMs to optimize deconvolution of each trial \cite{mumford2012}.
-% CAMERON it is important to regress movement and other stuff from 
-% REST and TASK, just not done in task
 With rest datasets, it is important to regress out time series capturing
@@
 parameters estimated during preprocessing, removing linear trends, signal
-% CAMERON WM and CSF are "negative controls" and represent thermal noise, 
-% systematic variation due to multichannel head coils, cardiac and resp.
-% smaller motions, physiological noise correction, spatial varying WM noise
-% GLOBAL MEAN IS A HUGE CONTROVERSY
 extracted from the white matter and the CSF \cite{chang2009}, as well as
@@
 correlation matrices that outline functional structures better
-(fig.\,\ref{fig:correlation_matrices}). Filtering high frequencies is
+(fig.\,\ref{fig:correlation_matrices}). 
+Indeed, white matter and CSF signals capture thermal noise, 
+systematic variation due to multichannel head coils, cardiac and resp.
+smaller motions, physiological noise correction.
+Filtering high frequencies is
 often recommended, based on the initial observation that neural-related
@@
 
-% CAMERON, this is just as important for task btw ...
 Finally, it is important to keep in mind that using resting-state to
@@
 % CAMERON why only SPM's tool?
+% GAEL: afaik, it only gives hard segmentation, and not probabilistic
+% segmentation
 as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
@@
 %
-% CAMERON might want to pull this back to graph edges
+Given ROIs defining nodes the nodes of the functional-connectome graph,
+one need to estimate the corresponding edges connecting them.
 Functional connectivity between the ROIs can be measured by computing the

### 2013-01-03 paper.tex
more changes

@@
 % General introduction
-Functional connectivity reveals the synchronization of distant
-neural systems via correlations in brain activity
-\cite{biswal1995,friston1993}. Given that high-level
-function emerges from the interaction of specialized units
-\cite{tononi1992}, functional
-connectivity is an essential part of the description of brain function,
-that complements the localizationist picture emerging from the systematic
-mapping of regions recruited in tasks \cite{sporns2005,biswal2010}. However, while there exists a
-well-defined standard analysis framework for activation mapping that enables
-statistically-controlled comparisons across subjects \cite{friston1995},
-group-level analysis of functional connectivity still faces many open
-methodological challenges. Deriving a picture of a single subject's 
-functional connectivity is by itself not straightforward, as the brain
-comprises a myriad of interacting subsystems and its connectivity must 
-be decomposed into
+Functional connectivity reveals the synchronization of distant neural systems
+via correlations in neurophysiological measures of brain activity 
+\cite{friston1994, biswal1995}.  Given that
+high-level function emerges from the interaction of specialized units,
+functional connectivity is an essential part of the description of brain
+function, that complements the localizationist picture emerging from the
+systematic mapping of regions recruited in tasks\cite{sporns2004}. However,
+while there exists a well-defined standard analysis framework for activation
+mapping that enables statistically-controlled comparisons across subjects
+\cite{friston1995}, group-level analysis of functional connectivity still faces
+many open methodological challenges. Deriving a picture of a single subject's
+functional connectivity is by itself not straightforward, as the brain comprises
+a myriad of interacting subsystems and its connectivity must be decomposed into
 simplified and synthetic representations. An important view of brain
 connectivity is that of distributed functional networks depicted by their
-spatial maps \cite{fox2005}. Another no less important and complementary
-view is that of connections linking localized functional modules depicted
-as a graph \cite{bullmore2009}. This representation of brain connectivity
-is often called the functional connectome \cite{sporns2005} and is the
-focus of intense worldwide research efforts as it holds promises of new
-insights in cognition and pathologies
-\cite{greicius2008b,biswal2010,fox2010}.
+spatial maps \cite{fox2005}. Another no less important and complementary view is
+that of connections linking localized functional modules depicted as a graph
+\cite{bullmore2009}. This representation of brain connectivity is often called
+the functional connectome \cite{sporns2005} and is the focus of intense
+worldwide research efforts as it holds promises of new insights in cognition and
+pathologies \cite{greicius2008b,biswal2010,fox2010}.
 
@@
 The purpose of this paper is to review methodological progress in the
-estimation and comparison of functional connectomes. It does not attempt
+estimation of functional connectomes from blood oxygenation level dependent
+(BOLD) based functional magnetic resonance imaging (fMRI) data and their
+comparisons across individuals.  It does not attempt
 to be exhaustive, as the field is wide and moving rapidly, but details
@@
 focused on functional connectomes in contrast to structural connectomes,
-as the inference of functional connectivity from observed brain activity
-fluctuations brings important specificities in the statistical modeling. While 
-the notion of functional
-connectome is often associated with the study of resting-state
+as the inference of functional connectivity requires important statistical
+modeling considerations that are vastly different from the complications involved
+with estimating structural connectivity.
+While the notion of functional
+connectomics is often associated with the study of resting-state
 \cite{biswal2010}, the methods presented in this paper are also relevant
 for task-based studies. On the other hand, the paper has a focus on fMRI;
-although the core concepts presented can be applied to MEG or EEG
+although the core concepts presented can be applied to 
+magnetoencephalography (MEG) or electroencephalography (EEG)
 \cite{stam2004}, additional specific problems such as source
@@
 % Define terms
-By ``functional connectome'', here we specifically denote a graph
-representing functional interactions in the brain, where the term
-``graph'' is taken in its mathematical sense: a set of \emph{nodes}
-connected together by \emph{edges}. Nodes are localized functional units
-and edges represent long range interactions synchronized via fibers.
-A graph can be weighted or not, and
-is completely equivalent to its \emph{adjacency matrix}, a symmetric
-matrix tabulating the connection weights between each pair of nodes.
-Functional-connectivity graphs are used to represent evoked activity,
-as in task-response studies \cite{mcintosh2000}, as well as
-ongoing activity, present in the absence of specific tasks or in 
-the background during task and often studied in so-called \emph{resting-state}
-experiments \cite{raichle2010}. Another important notion that arises from
-the study of distributed modes of brain function is that of specialized
-functional networks\footnote{In neuroimaging, the term network is
-sometimes used to denote a graph of brain function. To disambiguate the
-notion of segregated spatial mode \cite{fox2005} from that of
-connectivity graphs, we will purposely restrict its usage in this
-paper.} \cite{fox2005}. With our definition of the functional connectome, functional
-networks are not directly building blocks of the connectome but appear
-as a consequence of the graphical structure
-\cite{varoquaux2010c,varoquaux2012}.
+By ``functional connectome'', here we specifically denote a graph representing
+functional interactions in the brain, where the term ``graph'' is taken in its
+mathematical sense: a set of \emph{nodes} connected together by \emph{edges}.
+Graph nodes (brain region) correspond to a spatially contiguous and functionally
+coherent patchs of cortex whose activity is synchronized through
+cytoarchitecture and edges describe large range synchronizations between nodes
+that are putatively subtended by large fiber pathways \cite{marrelec2006}.  A
+graph can be weighted or not, and is completely equivalent to its
+\emph{adjacency matrix}, a symmetric matrix tabulating the connection weights
+between each pair of nodes.  Functional-connectivity graphs are used to
+represent evoked activity, as in task-response studies \cite{mcintosh2000}, as
+well as ongoing activity, present in the absence of specific tasks or in the
+background during task and often studied in so-called \emph{resting-state}
+experiments \cite{raichle2010}. Another important notion that arises from the
+study of distributed modes of brain function is that of specialized functional
+networks\footnote{In neuroimaging, the term network is sometimes used to denote
+	a graph of brain function. To disambiguate the notion of segregated
+	spatial mode \cite{fox2005} from that of connectivity graphs, we will
+	purposely restrict its usage in this paper.} \cite{fox2005}. With our
+definition of the functional connectome, functional networks are not directly
+building blocks of the connectome but appear as a consequence of the graphical
+structure \cite{varoquaux2010c,varoquaux2012}.
 
 % Give a layout of the paper
-The paper is organized as follows. First we discuss estimation of
-functional connectomes. This part, akin to a first-level analysis in
-standard activation mapping methodology, is not in itself a group-level
-operation, but it is a critical step for inter-subject comparison.
-In a following section, we discuss several strategies for comparing
-connectomes across subjects. Finally we discuss the links between the
-representation of brain connectivity as graphs of functional connectivity
-and more complex models, such as effective-connectivity models.
+The paper is organized as follows. First we discuss estimation of functional
+connectomes. This part, akin to a first-level analysis in standard activation
+mapping methodology, is not in itself a group-level operation, but it is a
+critical step for inter-subject comparison.  In a following section, we discuss
+several strategies for comparing connectomes across subjects. Finally we discuss
+the links between the representation of brain connectivity as graphs of
+functional connectivity and more complex models, such as effective-connectivity
+models.
 
@@
 Here we discuss the inference of connectomes from functional brain
-imaging data. We start with the choice of nodes \emph{i.e.}\ regions,
-followed by signal extraction, and the estimation of graphs.
+imaging data. We start with preprocessing considerations, followed by
+the choice of nodes \emph{i.e.}\ regions,
+signal extraction, and the estimation of graphs.
 
 %------------------------------------------------------------------------------
+\subsection{Preprocessing Considerations}
+
+% CAMERON make sure these citations are accounted for
+In addition to standard preprocessing performed for task based analyses
+(slice-timing correction, realignment, spatial normalization, and possibly
+smooting), connectivity based analyses require additional denoising 
+to separate intrinsic activity from confounding signals. This process involves
+regressing time series capturing sources of structured noise from the fMRI data.
+Physiological noise due to cardiac and respiration are two important
+noise signals \cite{Hu1993, lund2006, birn2006, birn2008} that are
+difficult to control for and as a result are not commonly regressed out. Instead
+the mean signal from white matter (WM) and cerbrospinal fluid (CSF) are used as
+surrogates to measure these sources of noise as well as other scanner induced
+signal fluctuations \cite{fox2005, lund2006}. More complex models account for
+spatial variation in noise by incorporating voxel specific regressors of
+neighboring WM (ANATICOR \cite{jo2010}) or the top components from a principle
+components analysis of WM signal (CompCor \cite{behzadi2007}). Head motion
+induced signal fluctuations are accounted for by incorporating movement
+parameters \cite{friston1996, fox2005, lund2006}. The global mean time series
+has been proposed as an additional noise regressor that appears to improve the
+spatial specifity of connectivity results \cite{fox2005, fox2009}. This practice
+has become controversial since the global mean has been shown to primarily reflect neuronal
+signal and the fact that global signal regression introduces negative correlations
+\cite{murphy2009,chang2009,saad2012}. 
+Removing these sources of
+nuisance in addition to linear trends results in more contrasted
+correlation matrices that improve the delineation of functional structures
+(fig.\,\ref{fig:correlation_matrices}).
+
+Filtering to remove high frequencies is often performed, based on the initial
+observation that fluctuations implicated in resting state functional
+connectivity are predominately slower than 0.1\,Hz \cite{cordes2001,biswal1995}.
+While high-pass and low-pass filtering decrease the impact of some confounds,
+recent studies have shown that connectivity is present across the
+full spectrum of observed frequencies \cite{smith2012,vanoort2012}. Regressing
+out a good choice of confound signals is more specific than frequency filter,
+and in our experience gives more contrasted correlation matrices\footnote{Note
+	that naive use of filtering can induce spurious correlations
+	\cite{davey2012}.}.
+
+It is important to keep in mind that the proposed correction strategies
+are approximate and not definitive techniques. This has become particularly
+apparent for head motion with reports that micromovements on the scale
+of $\le 0.2$mm can induce artefactual group-level findings even when motion is
+accounted for in preprocessing
+\cite{vandijk2012,power2011,satterthwaite2012}. Special care must be taken to
+adequately control for residual impact of head motion in the group model
+\cite{satterthwaite2012, saad2012}.
+
+%
+
 \subsection{Defining regions}
@@
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
-wang2009,bellec2006}, this coverage can be traded off to focus on some specific
+wang2009}, this coverage can be traded off to focus on some specific
 regions, in favor of increased functional specificity and thus better
-differentiation across networks \cite{greicius2003, dosenbach2010,
+% CAMERON I think that this reference to Fair should be Dosenbach 2006 neuron
+differentiation across networks \cite{greicius2003, dosenbach2006,
 varoquaux2010b}. In addition, while
@@
 probabilistic atlases, or spatial maps of functional networks extracted
-from techniques such as independent component analysis (ICA)
-\cite{kiviniemi2009,smith2009}.
+from techniques such as independent component analysis (ICA) \cite{kiviniemi2009,smith2012}.
 
@@
 %
-Atlases can be used to define full-brain parcellations. A popular
-is probably the AAL atlas \cite{tzourio-mazoyer2002a}, that
-benefits from an SPM toolbox. However, it suffers from major
-shortcomings; namely \emph{i)} that it was defined on a single subject
-and thus does does not reflect inter-subject variability and \emph{ii)}
-that it focuses on labeling large anatomical structures and does not match
-functional layout \cite{craddock2011} --for instance only two regions describe the medial
-part of the frontal lobe. Multi-subject probabilistic altases such as the
+Atlases can be used to define full-brain parcellations. Popular
+choices are the the Automatic Anatomic Labeling (AAL) atlas \cite{tzourio-mazoyer2002a}, 
+which benefits from an SPM toolbox or the ubiquitous Talaraich-Tournoux
+atlas \cite{talaraich}. 
+However, these atlases suffer from major
+shortcomings; namely \emph{i)} they were defined on a single subject
+and thus does does not reflect inter-subject variability, \emph{ii)}
+they focus on labeling large anatomical structures and does not match
+functional layout --for instance only two regions describe the medial
+part of the frontal lobe, and \emph{iii} they are defined based on
+cytoarchitectonic or anatomical boundaries and do not incorporate functional
+information. Multi-subject probabilistic altases such as the
 Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
@@
 first problem, and the high number of regions defined using sulci also
-somewhat circumvent the second problem (see
-fig.\,\ref{fig:parcellations}).
+somewhat circumvent the second problem (see fig.\,\ref{fig:parcellations}).
 
@@
 useful to study connectivity in task-specific networks
-\cite{biswal1995,rissman2004,grillon2012}. The common practice is to place balls of a given
+% CAMERON include citation to Dosenbach, and some others
+\cite{dosenbach2006,grillon2012}. The common practice is to place balls of a given
 radius, 5 or 10\,mm, centered at the coordinates of interest. Given that
@@
 adapts to the signal at hand and its limitations, such as
-EPI-specific warps or vascular and movement artifacts that are isolated
-in ICA-like approaches. The simplest approach to define task-specific
+image distortions or vascular and movement artifacts that are isolated
+in ICA-like approaches. Lastly, incorporating functional information into
+regional definition will result in more homogenous regions that better represent
+connectivity present at the voxel level then anatomically defined atlases such
+as AAL or Harvard-Oxford \cite{craddock2011}. The simplest approach to define task-specific
 regions is to use activation maps derived from standard GLM-based
@@
 
+%% XX number of regions
+% CAMERON added this since it was left to do, I don't know if it really says
+% anything 
+\paragraph{Optimal number of regions}
+%
+Defining an optimal number of regions to use for whole brain connectivity analysis bears
+careful consideration. On one hand we desire a sufficiently large number of
+regions to guarentee that they are functionally homogenous regions and adequately 
+represent the connectivity information present in the data. On the other hand
+too many regions will result in an explosion in computational complexity 
+and interfere with the interpretability of observed connections. For functional
+parcellation, cross validation methods can be employed to estimate an optimal 
+number of regions based on homogeniety, the ability to reproduce 
+connectivity information present at the voxel scale, and the ability to
+obtain the same parcellations from independent data 
+\cite{craddock2011, germanguy}. In general these metrics do not result in an
+obvious peak at a ``best'' number of regions, but instead offer a range over
+which the number of regions can be chosen based on the needs of the analysis at
+hand.
+
 %{{{------ Parcellation figure -----------------------------------------------
@@
 
-The concept of functional connectivity has be called elusive
+The concept of functional connectivity has been called elusive
 \cite{horwitz2003}: it has many mathematical instantiations although in
@@
 
-\paragraph{Signal extraction and cleaning}
-Given graph nodes, the next step 
-Given ROIs, the next step is to extract from them a summary measure. To
-study \emph{on-going} activity, \emph{e.g.}\ with rest data, signal
-extraction is performed from the EPI time series; however, to study
-\emph{evoked} activity with task-driven studies it can be beneficial to
-run a GLM-based first-level analysis, enforcing specificity of the measure
-extracted to the task. With slow event-related designs, task-specific
-functional connectivity can be captured in trial-to-trial fluctuations in
-the BOLD response, estimated using a GLM analysis with one regressor per
-trial \cite{grillon2012,rissman2004}. This approach, known as beta-series
-regression, has been adapted for rapid event-related designs, using
-multiple GLMs to optimize deconvolution of each trial \cite{mumford2012}.
-With rest datasets, it is important to regress out time series capturing
-movement and other sources of structured noise, to separate on-going
-activity from confounding signals. In addition to removing movement
-parameters estimated during preprocessing, removing linear trends, signal
-extracted from the white matter and the CSF \cite{chang2009}, as well as
-using the CompCor \cite{behzadi2007} procedure gives more contrasted
-correlation matrices that outline functional structures better
-(fig.\,\ref{fig:correlation_matrices}). 
-Indeed, white matter and CSF signals capture thermal noise, 
-systematic variation due to multichannel head coils, cardiac and resp.
-smaller motions, physiological noise correction.
-Filtering high frequencies is
-often recommended, based on the initial observation that neural-related
-signals are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
-high-pass and low-pass filtering decrease the impact of some confounds,
-recent studies have shown that information on neural processes is present
-in the full spectrum of frequencies observed
-\cite{smith2012,vanoort2012}. Regressing out a good choice of confound
-signals is more specific than frequency filter, and in our experience
-gives more contrasted correlation matrices\footnote{Note that naive use
-of filtering can induce spurious correlations \cite{davey2012}.}.
-
-Finally, it is important to keep in mind that using resting-state to
-study on-going activity is fragile to confounds such as movement
-\cite{vandijk2012,power2011} or scanner noise, and probably more so than
-activation studies as it is harder to control the specificity of the
-signal extracted. Special care must be taken in preprocessing strategies
-\cite{vandijk2010,satterthwaite2012}.
-%
-In addition, improved specificity to BOLD signal can be enforced by
-using only signal in voxels near gray-matter tissues. For this purpose,
-we suggest summarizing the signal in an ROI by a mean of the different voxels
-weighted by the subject-specific gray matter probabilistic segmentation,
-% CAMERON why only SPM's tool?
-% GAEL: afaik, it only gives hard segmentation, and not probabilistic
-% segmentation
-as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
-
-% CAMERON TODO: two sentences max
+\paragraph{Signal extraction}
+% CAMERON = I think we should differentiate between signal extraction and signal
+% cleaning, actually the cleaning is a seperate issue, that is independent of
+% the regions or nodes.
+Given a set of graph nodes, the next step is to extract a representative time
+series for each node.  To study \emph{intrinsic} activity, \emph{e.g.}\ with
+rest data, signal extraction can be acheived by either averaging the fmri time
+series across the voxels in a region, or by taking the first eigenvariate from a
+principle components analysis of the time series \cite{Friston functional
+	localizers}.  The latter approach provides an additional level of
+denoising by selecting a time series that explains the greatest variance across
+the voxels, and excludes ``deviant'' time series from noise or dissimilar
+voxels. Comparisons of these methods has shown that the eigenvariate method is
+more sensitive to function inhomogeniety \cite{craddock 2011} and exhibits worse
+test-retest reliablity than averaging time series \cite{zuo thingy}. A hybrid
+approach would be to average the top few eigenvariates from the PCA
+decomposition.  In addition, improved specificity to BOLD signal can be enforced
+by using only signal in voxels near gray-matter tissues. For this purpose, we
+suggest summarizing the signal in an ROI by a mean of the different voxels
+weighted by the subject-specific gray matter probabilistic segmentation, as
+output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
+
+To study connectivity from \emph{evoked} activity with task-driven studies it
+can be beneficial to run a GLM-based first-level analysis, enforcing specificity
+of the measure extracted to the task. With slow event-related designs,
+task-specific functional connectivity can be captured in trial-to-trial
+fluctuations in the BOLD response, estimated using a GLM analysis with one
+regressor per trial \cite{grillon2012,rissman2004,mennes2010}. This approach,
+known as beta-series regression, has been adapted for rapid event-related
+designs, using multiple GLMs to optimize deconvolution of each trial
+\cite{mumford2012}.
+
 % Regressing out task?? Skipping for lack of space
+% CAMERON make this better
+Estimating intrinsic activity from task based data can be obtained by either
+temporally concatenating rest blocks from the task, or by regressing the task
+from the fMRI data. The latter approach is justified by the observation that
+spontaneous activity is present during and additive to task BOLD responses 
+\cite{fox finger tapping}. Evaluations of these methods have shown variable
+results, where the resulting connectivity is similar too, but not the same as
+results obtained from resting state data \cite{fair, lohman}. The differences 
+are likely due to the
+large carry over effects seen from task to rest blocks.
 
@@
 %
-Given ROIs defining nodes the nodes of the functional-connectome graph,
-one need to estimate the corresponding edges connecting them.
+% CAMERON might want to pull this back to graph edges
 Functional connectivity between the ROIs can be measured by computing the
@@
 (fig.\,\ref{fig:icov_regressors}).
-% CAMERON I would move this to preprocessing section
+
+% CAMERON I really like this section, but would change it slightly to reflect
+% that preprocessing has been moved to its own sectoin.
 There have been debates on whether to
@@
 \paragraph{Mass-univariate approaches}
-%
-% CAMERON there has to be other references ...
 The most natural approach is to apply a linear model to each coefficient of
@@
 % CAMERON What about regional summary measures such as centrality??? Xinian's work
-% maybe a paragraph on these ReHo, degree centrality, eigenvector centrality, pagerank etc...
+% maybe a paragraph that covers ReHo, degree centrality, eigenvector centrality, pagerank etc...
 
@@
 Predictive modeling is concerned with learning (or fitting) a model that is
-capable of decoding or \emph{predicting} information from new unseen data \cite{pereira2009}.
-In the context of connectomes, predictive modeling provides a means for
-delineating connectivity based biomarkers of disease diagnosis, 
-prognosis, or other phenotypic outcomes \cite{craddock2009, dosenbach2010}. The accuracy
-of a predictive model provides a measure of the amount of information present
-in the connectome about the phenotypic measure being evaluated [kriegeskorte, Kjems]. 
-When combined with reproducibility, prediction accuracy provides a metric for
-evaluating experimental tradeoffs for data acquisition, preprocessing, and analysis 
-[Strother, LaConte].  Multivariate predictive models are attractive in connectomics 
-because they are sensitive to dependencies between features and avoid the need to correct
-for  multiple comparisons since the significance of an entire pattern is evaluated 
-using a single statistical test. From the perspective of medical applications, using
-resting-state connectivity as a biomarker is particularly appealing as it
-can be applied to impaired patients \cite{greicius2008b}. Predictive
-modeling techniques have been successfully applied to identify
-connectome-based biomarkers of Alzheimer's disease
-\cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
+capable of decoding or \emph{predicting} information from new unseen data
+\cite{pereira2009}.  In the context of connectomes, predictive modeling provides
+a means for delineating connectivity based biomarkers of disease diagnosis,
+prognosis, or other phenotypic outcomes \cite{craddock2009, dosenbach2010}. The
+accuracy of a predictive model provides a measure of the amount of information
+present in the connectome about the phenotypic measure being evaluated
+[kriegeskorte, Kjems].  When combined with reproducibility, prediction accuracy
+provides a metric for evaluating experimental tradeoffs for data acquisition,
+preprocessing, and analysis [Strother, LaConte].  Multivariate predictive models
+are attractive in connectomics because they are sensitive to dependencies
+between features and avoid the need to correct for  multiple comparisons since
+the significance of an entire pattern is evaluated using a single statistical
+test. From the perspective of medical applications, using resting-state
+connectivity as a biomarker is particularly appealing as it can be applied to
+impaired patients \cite{greicius2008b}. Predictive modeling techniques have been
+successfully applied to identify connectome-based biomarkers of Alzheimer's
+disease \cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
 \cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
@@
 % CAMERON something about the ADHD200 Global Competition highlights the
-% interest/need for predictive modeling in connectomics as well
-% as the number of approaches applicable 
-Recent work has illustrated the
-utility of predictive modeling for deriving connectivity models at the
-individual level [Chu 2010, Craddock in press or HBM].
+% interest/need for predictive modeling in connectomics as well as the number of
+% approaches applicable 
+Recent work has illustrated the utility of predictive modeling for deriving
+connectivity models at the individual level [Chu 2010, Craddock in press or
+HBM].
 
@@
 \emph{where} it lies informs us on brain function.
+
+% CAMERON condense below ALOT, focus on "where" the i information is
+% and how it is used ...
 
@@
 variance while maximising the amount of data available for training at the cost
-of introducing bias. This bias is due to the fact that on average 63.2\percent
-of the testing data overlaps with the training data, the .632\plus bootstrap
+of introducing bias. This bias is due to the fact that on average 63.2 percent
+of the testing data overlaps with the training data, the .632 plus bootstrap
 corrects for this bias.  No matter which cross validation scheme is used, the

### 2013-01-03 paper.tex
iter

--- 2013-01-03 paper.tex
@@
 % CAMERON Isn't there a paper from Stanford about this as well??
+% GAEL: I cannot find it with a quick Google. Do you have a name?
 efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
@@
 variance while maximising the amount of data available for training at the cost
-of introducing bias. This bias is due to the fact that on average 63.2\percent
-of the testing data overlaps with the training data, the .632\plus bootstrap
+of introducing bias. This bias is due to the fact that on average 63.2\%
+of the testing data overlaps with the training data, the .632+ bootstrap
 corrects for this bias.  No matter which cross validation scheme is used, the

### 2013-01-04 paper.tex
Remove merge mess

--- 2013-01-03 paper.tex
@@
 via correlations in neurophysiological measures of brain activity 
-\cite{friston1994, biswal1995}.  Given that
-high-level function emerges from the interaction of specialized units,
+\cite{friston1993, biswal1995}.  Given that
+high-level function emerges from the interaction of specialized units
+\cite{tononi1992},
 functional connectivity is an essential part of the description of brain
@@
 Graph nodes (brain region) correspond to a spatially contiguous and functionally
-coherent patchs of cortex whose activity is synchronized through
-cytoarchitecture and edges describe large range synchronizations between nodes
+coherent patchs of cortex and edges describe large range synchronizations between nodes
 that are putatively subtended by large fiber pathways \cite{marrelec2006}.  A
@@
 adequately control for residual impact of head motion in the group model
-\cite{satterthwaite2012, saad2012}.
+\cite{satterthwaite2012, vandijk2012}.
 
@@
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
-wang2009}, this coverage can be traded off to focus on some specific
+wang2009,bellec2006}, this coverage can be traded off to focus on some specific
 regions, in favor of increased functional specificity and thus better
-% CAMERON I think that this reference to Fair should be Dosenbach 2006 neuron
 differentiation across networks \cite{greicius2003, dosenbach2006,
@@
 Atlases can be used to define full-brain parcellations. Popular
-choices are the the Automatic Anatomic Labeling (AAL) atlas \cite{tzourio-mazoyer2002a}, 
+choices are the Automatic Anatomic Labeling (AAL) atlas \cite{tzourio-mazoyer2002a}, 
 which benefits from an SPM toolbox or the ubiquitous Talaraich-Tournoux
-atlas \cite{talaraich}. 
+atlas \cite{talaraich1988}. 
 However, these atlases suffer from major
@@
 and thus does does not reflect inter-subject variability, \emph{ii)}
-they focus on labeling large anatomical structures and does not match
+they focus on labeling large anatomical structures and do not match
 functional layout --for instance only two regions describe the medial
@@
 useful to study connectivity in task-specific networks
-% CAMERON include citation to Dosenbach, and some others
-\cite{dosenbach2006,grillon2012}. The common practice is to place balls of a given
+\cite{biswal1995,rissman2004,dosenbach2006,grillon2012}. The common practice is to place balls of a given
 radius, 5 or 10\,mm, centered at the coordinates of interest. Given that
@@
 connectivity present at the voxel level then anatomically defined atlases such
-as AAL or Harvard-Oxford \cite{craddock2011}. The simplest approach to define task-specific
+as AAL or Harvard-Oxford \cite{craddock2012}. The simplest approach to define task-specific
 regions is to use activation maps derived from standard GLM-based
@@
 analysis techniques are necessary. Clustering approaches extract
-full-brain parcellations \cite{craddock2011, bellec2010, yeo2011,
-thirion2006}, and have been shown to segment well-known functional
+full-brain parcellations \cite{craddock2012,bellec2010,yeo2011,thirion2006}, and have been shown to segment well-known functional
 structures from rest data. Alternatively, decompositions
@@
 techniques leads to contrasted maps that outline many different
-structures \cite{craddock2011, varoquaux2012} (see fig.\,\ref{fig:parcellations}).
-
-%% XX number of regions
+structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
+
+%% XXX number of regions
 % CAMERON added this since it was left to do, I don't know if it really says
@@
 obtain the same parcellations from independent data 
-\cite{craddock2011, germanguy}. In general these metrics do not result in an
+\cite{craddock2012, blumensath2012}. In general these metrics do not result in an
 obvious peak at a ``best'' number of regions, but instead offer a range over
@@
 \cite{varoquaux2010c}, regions extracted by Ncuts
-\cite{craddock2011}, the resting-state networks extracted in
+\cite{craddock2012}, the resting-state networks extracted in
 \cite{smith2009} by ICA, and in \cite{varoquaux2011} by sparse dictionary
@@
 
-% The following paragraph is convoluted: we start to say that rest is
-% from time-series, and task from beta, we go on discussing about beta
-% maps, and then we move back to rest. It might need restructuring
-
-% Horrible sentence below
-
-\paragraph{Signal extraction}
-% CAMERON = I think we should differentiate between signal extraction and signal
-% cleaning, actually the cleaning is a seperate issue, that is independent of
-% the regions or nodes.
+\paragraph{Signal extraction and cleaning}
 Given a set of graph nodes, the next step is to extract a representative time
 series for each node.  To study \emph{intrinsic} activity, \emph{e.g.}\ with
-rest data, signal extraction can be acheived by either averaging the fmri time
+rest data, signal extraction can be achieved by either averaging the fMRI time
 series across the voxels in a region, or by taking the first eigenvariate from a
 principle components analysis of the time series \cite{Friston functional
-	localizers}.  The latter approach provides an additional level of
-denoising by selecting a time series that explains the greatest variance across
-the voxels, and excludes ``deviant'' time series from noise or dissimilar
-voxels. Comparisons of these methods has shown that the eigenvariate method is
-more sensitive to function inhomogeniety \cite{craddock 2011} and exhibits worse
-test-retest reliablity than averaging time series \cite{zuo thingy}. A hybrid
-approach would be to average the top few eigenvariates from the PCA
-decomposition.  In addition, improved specificity to BOLD signal can be enforced
+	localizers}.
+Comparisons of these methods has shown that the eigenvariate method is
+more sensitive to function inhomogeneity \cite{craddock2012} and exhibits worse
+test-retest reliablity than averaging time series \cite{zuo2010}. 
+In addition, improved specificity to BOLD signal can be enforced
 by using only signal in voxels near gray-matter tissues. For this purpose, we
 suggest summarizing the signal in an ROI by a mean of the different voxels
-weighted by the subject-specific gray matter probabilistic segmentation, as
-output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
+weighted by the subject-specific gray matter probabilistic segmentation, 
+as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005} or
+FSL's FAST program \cite{zhang2001}.
+
+With rest dataset, it is important to regress out time series capturing
+movement and other sources of structured noise, to separate on-going
+activity from confounding signals. In addition to removing movement
+parameters estimated during preprocessing, removing linear trends, signal
+extracted from the white matter and the CSF \cite{chang2009}, as well as
+using the CompCor \cite{behzadi2007} procedure gives more contrasted
+correlation matrices that outline functional structures better
+(fig.\,\ref{fig:correlation_matrices}). 
+Indeed, white matter and CSF signals capture thermal noise, 
+systematic variation due to multichannel head coils, cardiac and resp.
+smaller motions, physiological noise correction.
+Filtering high frequencies is
+often recommended, based on the initial observation that neural-related
+signals are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
+high-pass and low-pass filtering decrease the impact of some confounds,
+recent studies have shown that information on neural processes is present
+in the full spectrum of frequencies observed
+\cite{smith2012,vanoort2012}. Regressing out a good choice of confound
+signals is more specific than frequency filter, and in our experience
+gives more contrasted correlation matrices\footnote{Note that naive use
+of filtering can induce spurious correlations \cite{davey2012}.}.
+Finally, it is important to keep in mind that using resting-state to
+study on-going activity is fragile to confounds such as movement
+\cite{vandijk2012,power2011} or scanner noise, and probably more so than
+activation studies as it is harder to control the specificity of the
+signal extracted. Special care must be taken in preprocessing strategies
+\cite{vandijk2010,satterthwaite2012}.
 
@@
 % Regressing out task?? Skipping for lack of space
-% CAMERON make this better
-Estimating intrinsic activity from task based data can be obtained by either
-temporally concatenating rest blocks from the task, or by regressing the task
-from the fMRI data. The latter approach is justified by the observation that
-spontaneous activity is present during and additive to task BOLD responses 
-\cite{fox finger tapping}. Evaluations of these methods have shown variable
-results, where the resulting connectivity is similar too, but not the same as
-results obtained from resting state data \cite{fair, lohman}. The differences 
-are likely due to the
-large carry over effects seen from task to rest blocks.
+% I'd rather skip it, as I really do not believe it actually works, and
+% would like to stay out of a controversy
 
@@
 % CAMERON Isn't there a paper from Stanford about this as well??
-efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
+% GAEL: I cannot find it with a quick Google. Do you have a name?
+% CAMERON: I think that it is ryali 2011, added
+efficient \cite{varoquaux2010c, ryali2011, smith2011}. The intuition for relying on
 inverse covariance rather than correlation stems from that fact that
@@
 functional-connectivity graphs can be summarized by a few metrics, such
-as the average path length between any two nodes or the local clustering
-coefficients \cite{rubinov2010}. Given that pathologies without a
+as the average path length between any two nodes, the local clustering
+coefficients, or the node degree centrality \cite{rubinov2010}. Given that pathologies without a
 localized focus, such
@@
 present in the connectome about the phenotypic measure being evaluated
-[kriegeskorte, Kjems].  When combined with reproducibility, prediction accuracy
+\cite{kjems2002, kriegeskorte2006}.  When combined with reproducibility, prediction accuracy
 provides a metric for evaluating experimental tradeoffs for data acquisition,
-preprocessing, and analysis [Strother, LaConte].  Multivariate predictive models
+preprocessing, and analysis \cite{strother2002, laconte2003}.  Multivariate
+predictive modeling (MPM)
 are attractive in connectomics because they are sensitive to dependencies
@@
 the significance of an entire pattern is evaluated using a single statistical
-test. From the perspective of medical applications, using resting-state
-connectivity as a biomarker is particularly appealing as it can be applied to
-impaired patients \cite{greicius2008b}. Predictive modeling techniques have been
+test. 
+Additionally many modern MPM techniques exist which are specifically
+formulated to deal with high dimensional datasets with few observations.
+Predictive modeling techniques have been
 successfully applied to identify connectome-based biomarkers of Alzheimer's
-disease \cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
-\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
+disease \cite{stonnington2010}, depression \cite{craddock2009, zeng2012}, schizophrenia
+\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008,}, aging
 \cite{dosenbach2010}, as well as to classify mental operations
-\cite{richiardi2011,shirer2012}.
-% CAMERON something about the ADHD200 Global Competition highlights the
-% interest/need for predictive modeling in connectomics as well as the number of
-% approaches applicable 
-Recent work has illustrated the utility of predictive modeling for deriving
-connectivity models at the individual level [Chu 2010, Craddock in press or
-HBM].
-
-Both the fact that information \emph{can} be
-used to make predictions on new data, and \emph{how} it is used or
-\emph{where} it lies informs us on brain function.
+\cite{richiardi2011,shirer2012}. The growing interest for applying MPM 
+to connectivity analysis was highlighted by the ADHD200
+Global Competition, in which the object was to identify a connectivity based
+biomarker of ADHD \cite{adhd2002012}. Recent work has illustrated the utility
+of predictive modeling for deriving connectivity models at the individual level
+\cite{chu2011}.
 
@@
 context of comparing connectomes, features used in the predictive model
-usually correspond to bivariate measures of connectivity, or any other
-summary metrics discussed earlier.  
+correspond to bivariate measures of connectivity, or any of the previously
+discussed summary metrics.  
 %
@@
 generalization ability) which is measured using one or more iterations of
-cross-validation. Cross-validation begins by seperating the available data into
-independent training and testing subsets.  A predictive model is learned from
-the training data and applied to the testing data to predict corresponding
-values of the target variable. Prediction accuracy is then assessed by comparing
-these predictions to the observed value of the target variable. This procedure
-can be iterated several times for different splits of the data and averaged to
-form a single measure of prediction accuracy.  One of the most important
-parameters for cross validation is the manner in which data are subdivided.
-There are several strategies for constructing the training dataset ranging from
-using all but one observations (leave-one-out cross-validation), using a
-fraction of the observations (k-fold cross validation; kfcv), to resampling the
-observations with replacement (boostrap cross-validation, bscv). Although loocv
-has been popular in neuroimaging applications of MVPA since it makes the largest
-amount of data available for training, its estimates are more variable than kfcv
-or bscv [tibs, book]. Split-half cross validation (two-fold cross validation,
-2fcv), minimizes the estimation variance, at the cost of using less training
-data, and also permits the simultaneous estimation of model reproducibility
-using the NPAIRs framework []. Bootstrap cross-validation minimizes estimation
-variance while maximising the amount of data available for training at the cost
-of introducing bias. This bias is due to the fact that on average 63.2 percent
-of the testing data overlaps with the training data, the .632 plus bootstrap
-corrects for this bias.  No matter which cross validation scheme is used, the
-accurate estimation of generalization ability requires that the testing data and
-training data are independent and identically distributied (iid). The meaning of
-independence here depends on the context in which the predictive model will be
-applied. For example, if observations correspond to subjects, then testing with
-scans acquired from the same subject, even acquired at different points in time,
-will introduce bias. If observations are different time points for the same
-subject, with the goal of testing whether the model can predict a later time
-point for that subject, then scans acquired from a later time point for that
-subject may be used for testing as long as enough time has passed to account for
-temporal autocorrelation.
-
-Another important parameter for estimating generalization ability is the error
-term employed. For classification problems error can be simply measured as a '1'
-if the prediction is correct and a '0' if it is incorrect, alternatively
-misclassifications for some groups may be weighted higher then others.  Log-loss
-or the negative log-likelihood can be used if class probabilities are outputed
-rather than simply class membership. For regression problems, common loss
-functions are the correlation or mean squared error between predicted and true
-target values. The former is preferred in cases when differences in scale and
-shift are less important then the relative ordering of the output values.
-Mean-squared error is preferred when the target variable has units and
-penalizing a model for shift or scale differences is important.
-
-After generalization ability (or error) has been estimated it is compared to
-what would be acheived by ``chance'' in order to estimate its significance. In
-the case of classification problems, the likelihood of obtaining a
-generalization accuracy by change can be estimated from a multinomial
-distribution [].  Alternatively, a permutation test can be performed in which
-the target labels are randomly permuted several times and the cross-validation
-error is estimated using each of the permutations. Significance is the assessed
-from the fraction of permutations that obtained higher prediction accuracy then
-was obtained from the unpermuted model. This method has the advantage of being
-available for both classification and regression models with the caveat that any
-correlationl structure between observations must be preserved to avoid biased
-results. Null distributions can be constructed for non-independent data using
-block permutation or wavelet resampling. When statistical significance is
-measured in this manner, the entire pattern is test with a single statistical
-test and there is no need to correct for multiple comparisons (unless multiple
-patterns are evaluated).
-
-MVPA algorithms typically require the specification of several parameters, the
-values of which will impact the quality of the results. These parameters may be
-prespecified based on domain specific knowledge or requirements [cherkassky
-book], determined using an analytical approach [cherkassky], or optimized using
-cross validation [cherrkasky book, tibs book].  In the latter case a nested
-cross-validation scheme is required to avoid biasing resultant measures of
-prediction accuracy [cherkassky].  
-%
-Determining the subset of features most relevant to the model (feature
-selection) can improve prediction accuracy \footnote{This is not necessarily
-	true, it has been shown in very high dimensional datasets that feature
-	selection does not improve prediction accuracy[cite high dimensional
-	gene paper], whereas in other cases it does\cite{craddock2009}.} and is
-essential for interpreting the models. For connectivity analyses, feature
-selection involves highlighting the connections that underlie the obtained
-prediction.  In cases were model weights can be directly mapped to their
-corresponding feature, there is typically no statistical framework for
-thresholding these weights, and meaningless features are not always set to zero
-\footnote{This is particularly the case for $\ell_2$ regularized algorithms such
-	as support vector machines and ridge regression}. One strategy is to
-filter out features based on their statistical relationship with the variable of
-interest using a univariate statistical criterion such as t-test, Pearson's
-correlation, or mutual information [guyon].  A drawback of this approach is that
+cross-validation. Cross-validation iteratively seperates available data into
+a subset used for training the classifier and a dataset for evaluating
+classifier performance. Several strategies exist for subdividing the data and
+the commonly used approach of using only a single observation for testing
+(leave-one-out cross-validation) results in highly variable estimates of
+prediction accuracy[]. Alternative approaches such as (5 or 10)-fold
+cross-validation, split half resampling, or $0.632+$ bootstrap should be
+preferred[]. The significance of acheived prediction accuracy can be assessed
+using permutation tests[]. Predictive modeling approaches typically require the
+specification of several parameters, which may be chosen based on domain
+specific knowledge or requirements [cherkassky book], determined using an
+analytical approach [cherkassky], or optimized using a second level cross
+validation procedure [cherrkasky book, tibs book].
+
+Although MPM techniques are extremely well suited at measuring whether
+information exists in the connectome about a phenotypic variable, indentifying the
+connections most relevant to the variable and interpreting their relationship
+with the variable is less straight forward. These problems can be somewhat mitigated by
+carefully selecting the number of
+% CAMERON: Need advice on how to say "previously described sparse inverse
+% covariance estimation techniques"
+nodes in the connectome and employing the previously described sparse inverse covariance estimation
+techniques to minimize the number of connections.
+
+Although MPM techniques are extremely well suited at measuring whether
+information exists in the connectome about a phenotypic variable, indentifying the
+connections most relevant to the predictive model (feature selection) is less straight forward. 
+These problems can be somewhat mitigated by carefully previously described
+sparse inverse covariance estimation techniques to minimize the number of
+connections. Additionally connections can be filtered out based on their statistical relationship with the variable of
+interest using a statistical criterion such as t-test, Pearson's
+correlation, or mutual information [guyon].  
+A drawback of this approach is that
 since the filters are typically insensitive to multivaratiate information, they
@@
 case the optimal feature subset is chosen based on cross validation based
-measures of prediction performance [] or a measure of their stability[].  A
+measures of prediction performance \cite{craddock2009, deshpande} or a measure
+of their stability \cite{craddock2009}.  A
 third approach are to use sparse modeling methods such as L1 SVM or LASSO that
-force weights for non-essential features to be zero [tibs,??]. Although ideal,
-these methods may have limits on the number of non-zero weights used in the
-model or the exclusion of highly correlated features from the model [elastic net
-paper].  Contrary to previous reports [Guyon 2002, Craddock 2009] no matter
-which feature selection strategy is employed, it must be performed with
+force weights for non-essential features to be zero [tibs,??]. 
+No matter
+which feature selection strategy is employed, it must be performed within
 cross-validation to avoid biasing estimates of prediction accuracy [later
@@
 
-The interpretation of classifier weights for selected features, when available,
-is complicated and requires insight into the mechanisms underlying the modeling
-approach. If features are appropriately standardized prior to training, the
-magnitude of weights can be interpreted to reflect the relative importance of
-the feature to the model, but interpreting how the feature differs between
-classes or relates to a continuous variable is more complicated, particularly
-given the multivariate nature of their involvement.  For classification methods
-such as Fisher's linear discriminant analysis (LDA), which maximally seperates
-class means given their standard deviation, feature weights are representative
-of the differences between class means. For support vector classification,
-classifier weights are derived from observations that are the most similar
-between classes, and hence represents the border between classes.  It is perhaps
+The interpretation of connections implicated by MPM and their relationship
+with a phenotypic outcome is complicated and requires insight into the
+mechanisms underlying the modeling approach. If features are appropriately
+standardized prior to training, the magnitude of model weights can be
+interpreted to reflect the relative importance of the corresponding feature to the model,
+similar to beta values from a standard regression model. But due to the
+multivariate nature of the MPMs, the sign of the weight cannot necessarily be
+interpreted to indicate the relationship between a connection and a phenotypic
+variable. Indeed, it is possible for the sign of a model weight to change based
+on the inclusion or exclusion of another feature in the model
+\cite{craddock2009}.  It is perhaps
 most reasonable to adapt a conservative interpretation in which predictive
@@
 a difficult problem, however, cross-validation (as used in
-\cite{varoquaux2010c,craddock2011,strother2006}) is a useful tool. The
+\cite{varoquaux2010c,craddock2012,strother2006}) is a useful tool. The
 central principle of cross-validation is to test a model on different

### 2013-01-04 paper.tex

@@
 coherent patchs of cortex and edges describe large range synchronizations between nodes
-that are putatively subtended by large fiber pathways \cite{marrelec2006}.  A
+that are putatively subtended by large fiber pathways \cite{marrelec2006b}.  A
 graph can be weighted or not, and is completely equivalent to its
@@
 Physiological noise due to cardiac and respiration are two important
-noise signals \cite{Hu1993, lund2006, birn2006, birn2008} that are
+noise signals \cite{hu1995, lund2006, birn2006, birn2008} that are
 difficult to control for and as a result are not commonly regressed out. Instead
@@
 which benefits from an SPM toolbox or the ubiquitous Talaraich-Tournoux
-atlas \cite{talaraich1988}. 
+atlas \cite{talairach1988}. 
 However, these atlases suffer from major
@@
 structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
+structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
 
@@
 series across the voxels in a region, or by taking the first eigenvariate from a
-principle components analysis of the time series \cite{Friston functional
-	localizers}.
+principle components analysis of the time series \cite{friston2006}.
 Comparisons of these methods has shown that the eigenvariate method is
@@
 disease \cite{stonnington2010}, depression \cite{craddock2009, zeng2012}, schizophrenia
-\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008,}, aging
+\cite{cecchi2009, shen2010}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
 \cite{dosenbach2010}, as well as to classify mental operations
@@
 % technical details
-Technically, predictive modeling is a supervised machine learning problem
-where a target to be predicted --\emph{e.g.}\ age, disease state,
-cognitive state-- is available for each observation of the data. In the
-context of comparing connectomes, features used in the predictive model
-correspond to bivariate measures of connectivity, or any of the previously
-discussed summary metrics.  
+Technically, predictive modeling is a supervised machine learning problem where
+a target to be predicted --\emph{e.g.}\ age, disease state, cognitive state-- is
+available for each observation of the data. In the context of comparing
+connectomes, features used in the predictive model correspond to bivariate
+measures of connectivity, or any of the previously discussed summary metrics.  
 %
@@
 generalization ability) which is measured using one or more iterations of
-cross-validation. Cross-validation iteratively seperates available data into
-a subset used for training the classifier and a dataset for evaluating
-classifier performance. Several strategies exist for subdividing the data and
-the commonly used approach of using only a single observation for testing
-(leave-one-out cross-validation) results in highly variable estimates of
-prediction accuracy[]. Alternative approaches such as (5 or 10)-fold
-cross-validation, split half resampling, or $0.632+$ bootstrap should be
-preferred[]. The significance of acheived prediction accuracy can be assessed
-using permutation tests[]. Predictive modeling approaches typically require the
-specification of several parameters, which may be chosen based on domain
-specific knowledge or requirements [cherkassky book], determined using an
-analytical approach [cherkassky], or optimized using a second level cross
-validation procedure [cherrkasky book, tibs book].
+cross-validation. Cross-validation iteratively seperates available data into a
+subset used for training the classifier and a dataset for evaluating classifier
+performance. Several strategies exist for performing cross-valdiaiton and the commonly
+used approach of using only a single observation for testing (leave-one-out
+cross-validation) results in highly variable estimates of prediction accuracy
+\cite{hastie2003}.
+Alternative approaches such as (5 or 10)-fold cross-validation, split half
+resampling, or $0.632+$ bootstrap should be preferred \cite{hastie2003}. The significance of
+achieved prediction accuracy can be assessed using permutation tests
+\cite{golland2003}.
+Predictive modeling approaches typically require the specification of several
+parameters, which may be chosen based on domain specific knowledge or
+requirements \cite{cherkassky1998}, determined using an analytical approach
+\cite{cherkassky2004}, or optimized using a second level cross validation procedure
+\cite{cherkassky1998}.
 
 Although MPM techniques are extremely well suited at measuring whether
-information exists in the connectome about a phenotypic variable, indentifying the
-connections most relevant to the variable and interpreting their relationship
-with the variable is less straight forward. These problems can be somewhat mitigated by
-carefully selecting the number of
-% CAMERON: Need advice on how to say "previously described sparse inverse
-% covariance estimation techniques"
-nodes in the connectome and employing the previously described sparse inverse covariance estimation
-techniques to minimize the number of connections.
-
-Although MPM techniques are extremely well suited at measuring whether
-information exists in the connectome about a phenotypic variable, indentifying the
-connections most relevant to the predictive model (feature selection) is less straight forward. 
-These problems can be somewhat mitigated by carefully previously described
-sparse inverse covariance estimation techniques to minimize the number of
-connections. Additionally connections can be filtered out based on their statistical relationship with the variable of
-interest using a statistical criterion such as t-test, Pearson's
-correlation, or mutual information [guyon].  
-A drawback of this approach is that
-since the filters are typically insensitive to multivaratiate information, they
-may exclude features that would be important to the model [guyon]. Another
-approach is to treat feature selection as a model selection problem in which
-case the optimal feature subset is chosen based on cross validation based
-measures of prediction performance \cite{craddock2009, deshpande} or a measure
-of their stability \cite{craddock2009}.  A
-third approach are to use sparse modeling methods such as L1 SVM or LASSO that
-force weights for non-essential features to be zero [tibs,??]. 
-No matter
-which feature selection strategy is employed, it must be performed within
-cross-validation to avoid biasing estimates of prediction accuracy [later
-Guyon].
-
-The interpretation of connections implicated by MPM and their relationship
-with a phenotypic outcome is complicated and requires insight into the
-mechanisms underlying the modeling approach. If features are appropriately
-standardized prior to training, the magnitude of model weights can be
-interpreted to reflect the relative importance of the corresponding feature to the model,
-similar to beta values from a standard regression model. But due to the
-multivariate nature of the MPMs, the sign of the weight cannot necessarily be
-interpreted to indicate the relationship between a connection and a phenotypic
-variable. Indeed, it is possible for the sign of a model weight to change based
-on the inclusion or exclusion of another feature in the model
-\cite{craddock2009}.  It is perhaps
-most reasonable to adapt a conservative interpretation in which predictive
-modeling is used to identify candidate connections that are later tested in
-followon experiments better suited to elucidating their relationship to the
-variable of interest.
+information exists in the connectome about a phenotypic variable, indentifying
+the connections most relevant to the predictive model (feature selection) is
+less straight forward.  These problems can be somewhat mitigated by carefully
+previously described sparse inverse covariance estimation techniques to minimize
+the number of connections. Feature selection \cite{guyon2003} can be performed by filtering out
+features based on their statistical relationship with the variable of interest
+\cite{craddock2009, shen2010},
+selecting features based on cross-validation \cite{craddock2009, deshpande2010}, or by employing sparse modeling
+methods that force weights for non-essential features to be zero
+\cite{tibshirani1994, michel2009, ryali2010}.
+Filtering features based on a univariate criterion such as t-test should be
+avoided, since they are insensitive to multivariate information and may exclude
+features that could be important to a multivariate model \cite{guyon2003,
+	craddock2009}. No matter which
+feature selection strategy is employed, it must be performed within
+cross-validation to avoid biasing estimates of prediction accuracy.
+
+The interpretation of connections implicated by MPM and their relationship with
+a phenotypic outcome is complicated and requires insight into the mechanisms
+underlying the modeling approach. If features are appropriately standardized
+prior to training, the magnitude of model weights can be interpreted to reflect
+the relative importance of the corresponding feature to the model, similar to
+beta values from a standard regression model. But due to the multivariate nature
+of the MPMs, the sign of the weight cannot necessarily be interpreted to
+indicate the relationship between a connection and a phenotypic variable.
+Indeed, it is possible for the sign of a model weight to change based on the
+inclusion or exclusion of another feature in the model \cite{craddock2009}.  It
+is perhaps most reasonable to adapt a conservative interpretation in which
+predictive modeling is used to identify candidate connections that are later
+tested in followon experiments better suited to elucidating their relationship
+to the variable of interest.
 
 To conclude on predictive modeling with a practical note for connectome
-comparison, we would like to stress that while machine learning
-algorithms are powerful tools, they work best if they are provided with
-discriminant and noiseless features. In other words, as with all other
-connectome comparison methods, optimizing first-level analysis
---subject-level connectome extraction-- is paramount.
+comparison, we would like to stress that while machine learning algorithms are
+powerful tools, they work best if they are provided with discriminant and
+noiseless features. In other words, as with all other connectome comparison
+methods, optimizing first-level analysis --subject-level connectome extraction--
+is paramount.
 

### 2013-01-04 paper.tex
fixed abstract, merge problem, typos, grammer

@@
 \begin{abstract}
-    Functional connectomes capture brain interactions via 
-    fluctuations in brain imaging signal. On rest data they map
-    the intrinsic functional architecture of the brain. With
-    task-driven experiments they represent the integration mechanisms
-    between specialized brain areas. Analysis of their variability 
-    across subjects and conditions can reveal markers of brain
-    pathologies and cognitive mechanisms. However, connectomes are
-    complex multivariate objects. Methods to estimate them 
-    from the functional signal have undergone rapid developments.
-    The literature is full of diverse strategies to compare them.
-    This paper aims to clarify some links across functional-connectivity
-    methods and expose different steps to perform a group study on
-    functional connectomes.
+	Functional connectomes capture brain interactions via synchronized
+	fluctuations in the functional magnetic resonance imaging signal. If
+	measured during rest, they map the intrinsic functional architecture of
+	the brain. With task-drive experiments they represent integration
+	mechanisms between specialized brain areas. Analyzing the variability in
+	the functional connectome across subjects and conditions can reveal
+	markers of brain pathologies and mechanisms underlying cognition.
+	Methods of estimating functional connectomes from the imaging signal
+	have undergone rapid developments and the literature is full of diverse
+	strategies for comparing them. This review aims to clarify links across
+	functional-connectivity methods and expose different steps in performing
+	a group study of functional connectomes.
 \end{abstract}
@@
 mapping that enables statistically-controlled comparisons across subjects
-\cite{friston1995}, group-level analysis of functional connectivity still faces
+\cite{friston1995}, group-level analyses of functional connectivity still face
 many open methodological challenges. Deriving a picture of a single subject's
@@
 
-% CAMERON make sure these citations are accounted for
 In addition to standard preprocessing performed for task based analyses
 (slice-timing correction, realignment, spatial normalization, and possibly
-smooting), connectivity based analyses require additional denoising 
+smoothing), connectivity based analyses require additional denoising 
 to separate intrinsic activity from confounding signals. This process involves
@@
 difficult to control for and as a result are not commonly regressed out. Instead
-the mean signal from white matter (WM) and cerbrospinal fluid (CSF) are used as
+the mean signal from white matter (WM) and cerebrospinal fluid (CSF) are used as
 surrogates to measure these sources of noise as well as other scanner induced
@@
 has been proposed as an additional noise regressor that appears to improve the
-spatial specifity of connectivity results \cite{fox2005, fox2009}. This practice
+spatial specificity of connectivity results \cite{fox2005, fox2009}. This practice
 has become controversial since the global mean has been shown to primarily reflect neuronal
@@
 apparent for head motion with reports that micromovements on the scale
-of $\le 0.2$mm can induce artefactual group-level findings even when motion is
+of $\le 0.2$\,mm can induce artefactual group-level findings even when motion is
 accounted for in preprocessing
@@
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
-wang2009,bellec2006}, this coverage can be traded off to focus on some specific
+wang2009,bellec2006,craddock2012}, this coverage can be traded off to focus on some specific
 regions, in favor of increased functional specificity and thus better
@@
 shortcomings; namely \emph{i)} they were defined on a single subject
-and thus does does not reflect inter-subject variability, \emph{ii)}
+and thus does does not reflect inter-subject variability, and \emph{ii)}
 they focus on labeling large anatomical structures and do not match
 functional layout --for instance only two regions describe the medial
-part of the frontal lobe, and \emph{iii} they are defined based on
-cytoarchitectonic or anatomical boundaries and do not incorporate functional
-information. Multi-subject probabilistic altases such as the
+part of the frontal lobe. Multi-subject probabilistic altases such as the
 Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
@@
 analysis techniques are necessary. Clustering approaches extract
-full-brain parcellations \cite{craddock2012,bellec2010,yeo2011,thirion2006}, and have been shown to segment well-known functional
+full-brain parcellations \cite{craddock2012, bellec2010, yeo2011,
+thirion2006}, and have been shown to segment well-known functional
 structures from rest data. Alternatively, decompositions
@@
 techniques leads to contrasted maps that outline many different
-structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
-structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
+structures \cite{craddock2012, varoquaux2012} (see fig.\,\ref{fig:parcellations}).
 
@@
 careful consideration. On one hand we desire a sufficiently large number of
-regions to guarentee that they are functionally homogenous regions and adequately 
+regions to guarantee that they are functionally homogeneous regions and adequately 
 represent the connectivity information present in the data. On the other hand
@@
 parcellation, cross validation methods can be employed to estimate an optimal 
-number of regions based on homogeniety, the ability to reproduce 
+number of regions based on homogeneity, the ability to reproduce 
 connectivity information present at the voxel scale, and the ability to
@@
 Different full-brain parcellations: the AAL atlas
-\cite{tzourio-mazoyer2002a}, the Harvard-Oxford atlas, the sucli atlas used in
+\cite{tzourio-mazoyer2002a}, the Harvard-Oxford atlas, the sulci atlas used in
 \cite{varoquaux2010c}, regions extracted by Ncuts
@@
 
-\paragraph{Signal extraction and cleaning}
+\paragraph{Signal extraction}
+%
 Given a set of graph nodes, the next step is to extract a representative time
@@
 more sensitive to function inhomogeneity \cite{craddock2012} and exhibits worse
-test-retest reliablity than averaging time series \cite{zuo2010}. 
+test-retest reliability than averaging time series \cite{zuo2010}. 
 In addition, improved specificity to BOLD signal can be enforced
@@
 suggest summarizing the signal in an ROI by a mean of the different voxels
-weighted by the subject-specific gray matter probabilistic segmentation, 
-as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005} or
-FSL's FAST program \cite{zhang2001}.
-
-With rest dataset, it is important to regress out time series capturing
-movement and other sources of structured noise, to separate on-going
-activity from confounding signals. In addition to removing movement
-parameters estimated during preprocessing, removing linear trends, signal
-extracted from the white matter and the CSF \cite{chang2009}, as well as
-using the CompCor \cite{behzadi2007} procedure gives more contrasted
-correlation matrices that outline functional structures better
-(fig.\,\ref{fig:correlation_matrices}). 
-Indeed, white matter and CSF signals capture thermal noise, 
-systematic variation due to multichannel head coils, cardiac and resp.
-smaller motions, physiological noise correction.
-Filtering high frequencies is
-often recommended, based on the initial observation that neural-related
-signals are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
-high-pass and low-pass filtering decrease the impact of some confounds,
-recent studies have shown that information on neural processes is present
-in the full spectrum of frequencies observed
-\cite{smith2012,vanoort2012}. Regressing out a good choice of confound
-signals is more specific than frequency filter, and in our experience
-gives more contrasted correlation matrices\footnote{Note that naive use
-of filtering can induce spurious correlations \cite{davey2012}.}.
-Finally, it is important to keep in mind that using resting-state to
-study on-going activity is fragile to confounds such as movement
-\cite{vandijk2012,power2011} or scanner noise, and probably more so than
-activation studies as it is harder to control the specificity of the
-signal extracted. Special care must be taken in preprocessing strategies
-\cite{vandijk2010,satterthwaite2012}.
+weighted by the subject-specific gray matter probabilistic segmentation, as
+output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
 
@@
 \cite{mumford2012}.
-
-% Regressing out task?? Skipping for lack of space
-% I'd rather skip it, as I really do not believe it actually works, and
-% would like to stay out of a controversy
 
@@
 \emph{i.e.}\ the correlation matrix of the data-generating process. If the
-% CAMERON THIS IS ALSO DETERMINED BY TEMPORAL AUTOCORRELATIONS! band-limited
-% by hemodynamic response, low sampling frequency
 number of measurements was infinite, the two would coincide, however if
@@
 which, sparse inverse covariance estimators have been found to be
-% CAMERON Isn't there a paper from Stanford about this as well??
-% GAEL: I cannot find it with a quick Google. Do you have a name?
-% CAMERON: I think that it is ryali 2011, added
 efficient \cite{varoquaux2010c, ryali2011, smith2011}. The intuition for relying on
@@
 make a compromise between imposing simpler models, \emph{i.e.}\ with less
-% CAMERON "fitting well the data" needs to be fixed
-connections, and fitting well the data. This compromise is set via a
+connections, and providing a good fit to the data. This compromise is set via a
 regularization parameter which controls the sparsity of the estimate. A
@@
 First, the correlation matrix (fig.\,\ref{fig:correlation_matrices})
-shows blocks of coactivating regions that can be interpreted as
+shows blocks of synchronized regions that can be interpreted as
 large-scale functional networks, such as the default mode network. Note
-% CAMERON How about spectral reordering?
 that the split in networks is not straightforward. Different ordering of the
 nodes will reveal different networks. 
-% CAMERON I don't get this sentence
 Indeed, because of the presence of
@@
 \emph{backbone} or \emph{core} of the graph.
-% CAMERON This is a really long sentence
 While such structure has
@@
 \cite{hagmann2008}, here it has a clear-cut meaning with regards to
-% CAMERON BOLD not explicitly defined
 the BOLD signal: it gives the conditional independence structure between
@@
 
-% CAMERON what about CWAS or Bellec??
-
 %{{{------ Inter subject fluctuations ----------------------------------------
@@
 population at rest). In other words, non-specific variability is
-distributed accross the connectivity graph, and it is structured by the
+distributed across the connectivity graph, and it is structured by the
 graph itself. This observation brings the natural question of whether
@@
 random graphs.} that are characteristic of small-word networks
-% CAMERON should cite dani basset
 \cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
@@
 connected. 
-% CAMERON cite first small world network science paper
 Another interesting consequence of their specific topology is
@@
 functional-connectivity graphs can be summarized by a few metrics, such
-as the average path length between any two nodes, the local clustering
-coefficients, or the node degree centrality \cite{rubinov2010}. Given that pathologies without a
+as the average path length between any two nodes or the local clustering
+coefficients \cite{rubinov2010}. Given that pathologies without a
 localized focus, such
@@
 \cite{kjems2002, kriegeskorte2006}.  When combined with reproducibility, prediction accuracy
-provides a metric for evaluating experimental tradeoffs for data acquisition,
+provides a metric for evaluating experimental trade-offs for data acquisition,
 preprocessing, and analysis \cite{strother2002, laconte2003}.  Multivariate
 predictive modeling (MPM)
-are attractive in connectomics because they are sensitive to dependencies
-between features and avoid the need to correct for multiple comparisons since
+is attractive in connectomics because it is sensitive to dependencies
+between features and avoids the need to correct for multiple comparisons since
 the significance of an entire pattern is evaluated using a single statistical
 test. 
-Additionally many modern MPM techniques exist which are specifically
+Additionally many MPM techniques exist which are specifically
 formulated to deal with high dimensional datasets with few observations.
@@
 
-% CAMERON condense below ALOT, focus on "where" the i information is
-% and how it is used ...
-
 % A bit of technical details
@@
 connectomes, features used in the predictive model correspond to bivariate
-measures of connectivity, or any of the previously discussed summary metrics.  
+measures of connectivity, or any of the previously discussed graph summary metrics.  
 %
@@
 generalization ability) which is measured using one or more iterations of
-cross-validation. Cross-validation iteratively seperates available data into a
+cross-validation. Cross-validation iteratively subdivides available data into a
 subset used for training the classifier and a dataset for evaluating classifier
-performance. Several strategies exist for performing cross-valdiaiton and the commonly
+performance. Several strategies exist for performing cross-validation and the commonly
 used approach of using only a single observation for testing (leave-one-out
@@
 Although MPM techniques are extremely well suited at measuring whether
-information exists in the connectome about a phenotypic variable, indentifying
+information exists in the connectome about a phenotypic variable, identifying
 the connections most relevant to the predictive model (feature selection) is
@@
 predictive modeling is used to identify candidate connections that are later
-tested in followon experiments better suited to elucidating their relationship
+tested in follow-on experiments better suited to elucidating their relationship
 to the variable of interest.
@@
 covariance matrices and the loss of statistical power due to multiple
-% CAMERON = integrating powerfulr a priori information?
-comparisons. Better algorithms integrating powerful a priori are required
+comparisons. Better algorithms integrating powerful a priori information are required
 to push the limits of covariance estimation. Better characterization of

### 2013-01-04 paper.tex
Small changes

--- 2013-01-04 paper.tex
@@
 Predictive modeling is concerned with learning (or fitting) a model that is
-capable of decoding or \emph{predicting} information from new unseen data
+capable of \emph{predicting} information from new unseen data
 \cite{pereira2009}.  In the context of connectomes, predictive modeling provides
@@
 preprocessing, and analysis \cite{strother2002, laconte2003}.  Multivariate
-predictive modeling (MPM)
-are attractive in connectomics because they are sensitive to dependencies
+predictive models are attractive in connectomics because they are sensitive to dependencies
 between features and avoid the need to correct for multiple comparisons since
@@
 test. 
-Additionally many modern MPM techniques exist which are specifically
-formulated to deal with high dimensional datasets with few observations.
-Predictive modeling techniques have been
+Additionally modern predictive modeling techniques draw from the
+statistical learning literature, which specifically addresses
+ high dimensional datasets with few observations.
+Predictive modeling has been
 successfully applied to identify connectome-based biomarkers of Alzheimer's
@@
 \cite{dosenbach2010}, as well as to classify mental operations
-\cite{richiardi2011,shirer2012}. The growing interest for applying MPM 
-to connectivity analysis was highlighted by the ADHD200
+\cite{richiardi2011,shirer2012}. The growing interest for applying
+predictive modeling to connectivity analysis was highlighted by the ADHD200
 Global Competition, in which the object was to identify a connectivity based
@@
 generalization ability) which is measured using one or more iterations of
-cross-validation. Cross-validation iteratively seperates available data into a
+cross-validation. Cross-validation iteratively separates available data into a
 subset used for training the classifier and a dataset for evaluating classifier
-performance. Several strategies exist for performing cross-valdiaiton and the commonly
+performance. Several strategies exist for performing cross-validation and the commonly
 used approach of using only a single observation for testing (leave-one-out
@@
 
-Although MPM techniques are extremely well suited at measuring whether
-information exists in the connectome about a phenotypic variable, indentifying
-the connections most relevant to the predictive model (feature selection) is
-less straight forward.  These problems can be somewhat mitigated by carefully
-previously described sparse inverse covariance estimation techniques to minimize
-the number of connections. Feature selection \cite{guyon2003} can be performed by filtering out
+Although predictive modeling techniques are well suited at measuring whether
+information exists in the connectome about a phenotypic variable, they do
+not directly identify the connections that are most relevant to the prediction.  These problems can be somewhat mitigated  by
+relying on previously described sparse inverse covariance estimation techniques to minimize
+the number of connections. In addition, feature selection \cite{guyon2003} 
+can be performed by filtering out
 features based on their statistical relationship with the variable of interest

### 2013-01-04 paper.tex

--- 2013-01-04 paper.tex
@@
 analysis techniques are necessary. Clustering approaches extract
-full-brain parcellations \cite{craddock2012, bellec2010, yeo2011,
-thirion2006}, and have been shown to segment well-known functional
+full-brain parcellations \cite{craddock2012,bellec2010,yeo2011,thirion2006}, and have been shown to segment well-known functional
 structures from rest data. Alternatively, decompositions
@@
 techniques leads to contrasted maps that outline many different
-structures \cite{craddock2012, varoquaux2012} (see fig.\,\ref{fig:parcellations}).
+structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
+structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
 
@@
 suggest summarizing the signal in an ROI by a mean of the different voxels
-weighted by the subject-specific gray matter probabilistic segmentation, as
-output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.
+weighted by the subject-specific gray matter probabilistic segmentation, 
+as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005} or
+FSL's FAST program \cite{zhang2001}.
 
@@
 preprocessing, and analysis \cite{strother2002, laconte2003}.  Multivariate
-predictive modeling (MPM)
-is attractive in connectomics because it is sensitive to dependencies
-between features and avoids the need to correct for multiple comparisons since
+predictive models are attractive in connectomics because they are sensitive to dependencies
+between features and avoid the need to correct for multiple comparisons since
 the significance of an entire pattern is evaluated using a single statistical
 test. 
-Additionally many MPM techniques exist which are specifically
-formulated to deal with high dimensional datasets with few observations.
-Predictive modeling techniques have been
+Additionally modern predictive modeling techniques draw from the
+statistical learning literature, which specifically addresses
+ high dimensional datasets with few observations.
+Predictive modeling has been
 successfully applied to identify connectome-based biomarkers of Alzheimer's
@@
 
-Although MPM techniques are extremely well suited at measuring whether
-information exists in the connectome about a phenotypic variable, identifying
-the connections most relevant to the predictive model (feature selection) is
-less straight forward.  These problems can be somewhat mitigated by carefully
-previously described sparse inverse covariance estimation techniques to minimize
-the number of connections. Feature selection \cite{guyon2003} can be performed by filtering out
+Although predictive modeling techniques are well suited at measuring whether
+information exists in the connectome about a phenotypic variable, they do
+not directly identify the connections that are most relevant to the prediction.  These problems can be somewhat mitigated  by
+relying on previously described sparse inverse covariance estimation techniques to minimize
+the number of connections. Feature selection \cite{guyon2003} 
+can be performed by filtering out
 features based on their statistical relationship with the variable of interest
-\cite{craddock2009, shen2010},
-selecting features based on cross-validation \cite{craddock2009, deshpande2010}, or by employing sparse modeling
-methods that force weights for non-essential features to be zero
-\cite{tibshirani1994, michel2009, ryali2010}.
-Filtering features based on a univariate criterion such as t-test should be
-avoided, since they are insensitive to multivariate information and may exclude
-features that could be important to a multivariate model \cite{guyon2003,
-	craddock2009}. No matter which
-feature selection strategy is employed, it must be performed within
+\cite{craddock2009, shen2010}. Importantly, it must be performed within
 cross-validation to avoid biasing estimates of prediction accuracy.
-
-The interpretation of connections implicated by MPM and their relationship with
-a phenotypic outcome is complicated and requires insight into the mechanisms
-underlying the modeling approach. If features are appropriately standardized
-prior to training, the magnitude of model weights can be interpreted to reflect
-the relative importance of the corresponding feature to the model, similar to
-beta values from a standard regression model. But due to the multivariate nature
-of the MPMs, the sign of the weight cannot necessarily be interpreted to
-indicate the relationship between a connection and a phenotypic variable.
+% 
+The interpretation of connections used in predictive models and their
+relationship with
+a phenotypic outcome is difficult and requires insight into the mechanisms
+underlying the modeling approach. For linear models, the weights of the
+model are similar to the weights of
+a ordinary linear regression. If features are appropriately standardized
+prior to training, the magnitude of weights can be interpreted to reflect
+the relative importance of the feature to the model, for instance the
+corresponding edge in the connectome. However,
+interpreting how the connections differs between classes or relates to a
+phenotypic variable can be more complicated given the multivariate nature
+of their involvement.
 Indeed, it is possible for the sign of a model weight to change based on the

### 2013-01-04 paper.tex
Submitted

@@
 	measured during rest, they map the intrinsic functional architecture of
-	the brain. With task-drive experiments they represent integration
-	mechanisms between specialized brain areas. Analyzing the variability in
-	the functional connectome across subjects and conditions can reveal
+	the brain. With task-driven experiments they represent integration
+	mechanisms between specialized brain areas. Analyzing their variability
+	across subjects and conditions can reveal
 	markers of brain pathologies and mechanisms underlying cognition.
@@
 	strategies for comparing them. This review aims to clarify links across
-	functional-connectivity methods and expose different steps in performing
-	a group study of functional connectomes.
+	functional-connectivity methods and to expose different steps 
+	to perform a group study of functional connectomes.
 \end{abstract}
@@
 mathematical sense: a set of \emph{nodes} connected together by \emph{edges}.
-Graph nodes (brain region) correspond to a spatially contiguous and functionally
-coherent patchs of cortex and edges describe large range synchronizations between nodes
+Graph nodes (brain regions) correspond to spatially-contiguous and 
+functionally-coherent patches of gray matter and edges describe long-range synchronizations between nodes
 that are putatively subtended by large fiber pathways \cite{marrelec2006b}.  A
@@
 
-In addition to standard preprocessing performed for task based analyses
+In addition to standard preprocessing performed for task based analysis
 (slice-timing correction, realignment, spatial normalization, and possibly
-smoothing), connectivity based analyses require additional denoising 
+smoothing), connectivity based analysis require additional denoising 
 to separate intrinsic activity from confounding signals. This process involves
@@
 spatial specificity of connectivity results \cite{fox2005, fox2009}. This practice
-has become controversial since the global mean has been shown to primarily reflect neuronal
-signal and the fact that global signal regression introduces negative correlations
+has become controversial since the global signal regression introduces negative correlations
 \cite{murphy2009,chang2009,saad2012}. 
@@
 accounted for in preprocessing
-\cite{vandijk2012,power2011,satterthwaite2012}. Special care must be taken to
+\cite{vandijk2012,power2011,satterthwaite2013}. Special care must be taken to
 adequately control for residual impact of head motion in the group model
-\cite{satterthwaite2012, vandijk2012}.
+\cite{satterthwaite2013,vandijk2012}.
 
@@
 choices are the Automatic Anatomic Labeling (AAL) atlas \cite{tzourio-mazoyer2002a}, 
-which benefits from an SPM toolbox or the ubiquitous Talaraich-Tournoux
+which benefits from an SPM toolbox, or the ubiquitous Talaraich-Tournoux
 atlas \cite{talairach1988}. 
@@
 shortcomings; namely \emph{i)} they were defined on a single subject
-and thus does does not reflect inter-subject variability, and \emph{ii)}
+and thus do not reflect inter-subject variability, and \emph{ii)}
 they focus on labeling large anatomical structures and do not match
 functional layout --for instance only two regions describe the medial
-part of the frontal lobe. Multi-subject probabilistic altases such as the
+part of the frontal lobe in the AAL atlas. Multi-subject probabilistic altases such as the
 Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
@@
 regional definition will result in more homogenous regions that better represent
-connectivity present at the voxel level then anatomically defined atlases such
+connectivity present at the voxel level then anatomically-defined atlases such
 as AAL or Harvard-Oxford \cite{craddock2012}. The simplest approach to define task-specific
@@
 combinations of multiple effects and separate out overlapping spatial maps
-capturing functional networks or confounding effects. At high model
+that capture functional networks or confounding effects. At high model
 order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
@@
 structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
-structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).
 
@@
 %
-Defining an optimal number of regions to use for whole brain connectivity analysis bears
+Defining an optimal number of regions to use for whole-brain connectivity analysis bears
 careful consideration. On one hand we desire a sufficiently large number of
@@
 represent the connectivity information present in the data. On the other hand
-too many regions will result in an explosion in computational complexity 
+too many regions will render statistical inference challenging, 
+result in an explosion in computational complexity,
 and interfere with the interpretability of observed connections. For functional
-parcellation, cross validation methods can be employed to estimate an optimal 
+parcellation, cross-validation methods can be employed to estimate an optimal 
 number of regions based on homogeneity, the ability to reproduce 
@@
 %
-Given ROIs defining nodes the nodes of the functional-connectome graph,
-one need to estimate the corresponding edges connecting them.
+Given ROIs defining the nodes of the functional-connectome graph,
+one needs to estimate the corresponding edges connecting them.
 Functional connectivity between the ROIs can be measured by computing the
@@
 which, sparse inverse covariance estimators have been found to be
-efficient \cite{varoquaux2010c, ryali2011, smith2011}. The intuition for relying on
+efficient \cite{varoquaux2010c,smith2011,ryali2012}. The intuition for relying on
 inverse covariance rather than correlation stems from that fact that
@@
 \cite{marrelec2006a}. In the small sample limit, this removal is
-challenging from the statistical standpoint, and an assumption of sparsity,
+challenging from the statistical standpoint. This is why an assumption 
+of sparsity,
 \emph{i.e.}\ that only few variables need to be considered at a time, is
@@
 negative correlations \cite{murphy2009,chang2009,fox2009}, and these may seem
-% CAMERON "doing the opposite of the other" is a bit odd
-surprising: one network is doing the opposite of the other. However,
+surprising: one network appears as having opposite fluctuations to
+another. However,
 correlation between two signals only takes its meaning with the
@@
 with possibly the inclusion of confounding effects, and statistical tests
-(T tests or F tests) on contrast vector. Importantly, in order to work
+(T tests or F tests) on contrast vectors. Importantly, in order to work
 with Gaussian-distributed variables, it is necessary to apply a Fisher
@@
 a parametrization intermediate between correlation matrix and inverse
-covariance matrix, that decouples effects and noise.
+covariance matrix, as it can decouple effects and noise.
 
@@
 \cite{marrelec2008} introduce the use of entropy and mutual information
-as a measure of network integration\footnote{See \cite{varoquaux2010c}
+as a measure of network-level functional integration\footnote{See \cite{varoquaux2010c}
 for simplified formulas for network integration and mutual information.}.
@@
 mean, as it might seem natural, discards the relationship between the
-signals, while using the integration tells us how much two signals can be
+signals, while using the integration, defined as the Gaussian entropy, tells us how much two signals can be
 combined to form the third (see fig.\,\ref{fig:integration}). 
@@
 Predictive modeling is concerned with learning (or fitting) a model that is
-capable of \emph{predicting} information from new unseen data
-\cite{pereira2009}.  In the context of connectomes, predictive modeling provides
-a means for delineating connectivity based biomarkers of disease diagnosis,
+capable of \emph{predicting} information from unseen data
+\cite{pereira2009}.  In the context of connectomes, predictive modeling
+can extract connectivity-based biomarkers of disease diagnosis,
 prognosis, or other phenotypic outcomes \cite{craddock2009, dosenbach2010}. The
@@
 subset used for training the classifier and a dataset for evaluating classifier
-performance. Several strategies exist for performing cross-validation and the commonly
+performance\footnote{Several strategies exist for performing cross-validation and the commonly
 used approach of using only a single observation for testing (leave-one-out
 cross-validation) results in highly variable estimates of prediction accuracy
-\cite{hastie2003}.
-Alternative approaches such as (5 or 10)-fold cross-validation, split half
-resampling, or $0.632+$ bootstrap should be preferred \cite{hastie2003}. The significance of
+\cite{friedman2001}.
+Alternative approaches such as (5 or 10)-fold cross-validation,
+or $0.632+$ bootstrap should be preferred \cite{friedman2001}.} 
+ \cite{pereira2009}.
+The significance of
 achieved prediction accuracy can be assessed using permutation tests
@@
 \cite{cherkassky2004}, or optimized using a second level cross validation procedure
-\cite{cherkassky1998}.
+\cite{friedman2001}.
 
@@
 information exists in the connectome about a phenotypic variable, they do
-not directly identify the connections that are most relevant to the prediction.  These problems can be somewhat mitigated  by
+not directly identify the connections that are most relevant to the
+prediction.  This limitation can be somewhat mitigated  by
 relying on previously described sparse inverse covariance estimation techniques to minimize
-the number of connections. Feature selection \cite{guyon2003} 
+the number of connections. Additionally, feature selection \cite{guyon2003} 
 can be performed by filtering out
@@
 model are similar to the weights of
-a ordinary linear regression. If features are appropriately standardized
-prior to training, the magnitude of weights can be interpreted to reflect
+an ordinary linear regression. If features are appropriately standardized
+prior to training, the magnitude of the weights can be interpreted to reflect
 the relative importance of the feature to the model, for instance the
 corresponding edge in the connectome. However,
-interpreting how the connections differs between classes or relates to a
+interpreting how the connections differs between classes or relate to a
 phenotypic variable can be more complicated given the multivariate nature
 of their involvement.
-Indeed, it is possible for the sign of a model weight to change based on the
-inclusion or exclusion of another feature in the model \cite{craddock2009}.  It
+Indeed, the inclusion or exclusion of a connection in the model
+can induce a change of the sign of another model weight \cite{craddock2009}.
+ It
 is perhaps most reasonable to adapt a conservative interpretation in which
@@
 that describes observed correlations in terms of an independence
-structure and conditional relations \cite{lauritzen1996,varoquaux2011}.
+structure and conditional relations \cite{lauritzen1996,varoquaux2012}.
 In such settings, the inverse covariance graph or the partial
@@
 based on the Neyman-Pearson lemma, cross-validation is less powerful than
-likelihood ratio tests relying on the full dataset. However, it is
+likelihood ratio tests using the full dataset. However, it is
 important to keep in mind that these approaches only test for
 self-consistence, as the Neyman-Pearson lemma requires that 
-the model likelihood describes the data well which may not always be the
+the model likelihood describes the data well, which may not always be the
 case \cite{lohmann2012}.}.

### 2013-02-21 paper.tex
Fix the citation ordering
Cleanup before addressing reviews

@@
 
+\biboptions{sort}
+
 \definecolor{deep_blue}{rgb}{0,.2,.5}
@@
 function, that complements the localizationist picture emerging from the
-systematic mapping of regions recruited in tasks\cite{sporns2004}. However,
+systematic mapping of regions recruited in tasks \cite{sporns2004}. However,
 while there exists a well-defined standard analysis framework for activation
@@
 
-%% XXX number of regions
-% CAMERON added this since it was left to do, I don't know if it really says
-% anything 
 \paragraph{Optimal number of regions}
@@
 \end{minipage}%
-
-% XXX: need to give details on the dataset used here
 
@@
 
-% XXX: must comment on the estimator figure
-
 \paragraph{Network structure extracted}
@@
 brain regions easier and more robust to the choice of confounds.
-
-% XXX: where to insert this in the above paragraph: cite the
-% Fransson/Marrelec paper on the role of the PCC
 
@@
 %\clearpage
-\section*{References} \small \bibliographystyle{elsarticle-num-names}
+\section*{References}
+\small
+%\bibliographystyle{elsarticle-num-names}
+\bibliographystyle{model1b-num-names}
 \bibliography{biblio} }

### 2013-02-21 paper.tex
Easy comments by reviewers addressed

@@
 %------------------------------------------------------------------------------
-\subsection{Preprocessing Considerations}
+\subsection{Preprocessing considerations}
 
@@
 spatial variation in noise by incorporating voxel specific regressors of
-neighboring WM (ANATICOR \cite{jo2010}) or the top components from a principle
+neighboring WM (ANATICOR \cite{jo2010}) or the top components from a
+principal
 components analysis of WM signal (CompCor \cite{behzadi2007}). Head motion
@@
 full spectrum of observed frequencies \cite{smith2012,vanoort2012}. Regressing
-out a good choice of confound signals is more specific than frequency filter,
+out a good choice of confound signals is more specific than frequency
+filtering,
 and in our experience gives more contrasted correlation matrices\footnote{Note
@@
 %
-Different strategies to define suitable ROIs coexist. While dense parcellations approaches cover
+Different strategies to define suitable ROIs coexist. While dense 
+parcellation approaches cover
 a large fraction of the brain \cite{achard2006, varoquaux2010c,
@@
 regional definition will result in more homogenous regions that better represent
-connectivity present at the voxel level then anatomically-defined atlases such
+connectivity present at the voxel level than anatomically-defined atlases such
 as AAL or Harvard-Oxford \cite{craddock2012}. The simplest approach to define task-specific
@@
 full-brain parcellations \cite{craddock2012,bellec2010,yeo2011,thirion2006}, and have been shown to segment well-known functional
-structures from rest data. Alternatively, decompositions
+structures from rest data. Alternatively, decomposition
 methods, such as ICA \cite{beckmann2004}, can unmix linear
@@
 \begin{figure}
-\includegraphics[height=.482\linewidth]{group_l21_prec_no_confounds.pdf}%
-\hspace*{1pt}%
-\includegraphics[height=.482\linewidth]{group_l21_prec_global_mean.pdf}%
-\hspace*{1pt}%
-\includegraphics[height=.482\linewidth]{cmap.pdf}%
-
-\caption{Inverse covariance matrices for different choice of
+\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds.pdf}%
+\hfill%
+\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean.pdf}%
+
+\caption{Inverse-covariance matrices for different choice of
 confound regressors --
@@
 correlation matrix is computed on standardized (zero mean, unit variance) signals.}
-matrix captures
+matrix (also called \emph{precision matrix} captures
 partial correlations, removing the effect of other variables
@@
 regularization parameter which controls the sparsity of the estimate. A
-good rule of thumb to choose this parameter is via cross-validation
+good procedure to choose this parameter is via cross-validation
 \cite{varoquaux2010c}.
@@
 been used as a way to summarize anatomical brain connectivity graphs
-\cite{hagmann2008}, here it has a clear-cut meaning with regards to
+\cite{hagmann2008}, here it has a clear-cut meaning with regard to
 the BOLD signal: it gives the conditional independence structure between
@@
 between a subject and the remaining others -- \textbf{c}:
-single-subject precision matrices -- \textbf{d}: Corresponding Z-score
-for the precision matrices -- \textbf{e}:
+single-subject inverse-covariance matrices -- \textbf{d}: Corresponding Z-score
+for the inverse-covariance matrices -- \textbf{e}:
 Corresponding Z-score for the subject residuals, as defined in 
@@
 A specific challenge of connectivity analysis is that the connectivity
-strength between different regions tend to covary. For instance, with
+strength between different regions tends to covary. For instance, with
 resting-state data, functional networks comprising many nodes can appear
 as more or less connected across subjects (see for instance
-fig.\,\ref{fig:inter_subject}.a, showing variability in a control
+fig.\,\ref{fig:inter_subject}, showing variability in a control
 population at rest). In other words, non-specific variability is
@@
 $\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$. Summarizing these by their
-mean, as it might seem natural, discards the relationship between the
-signals, while using the integration, defined as the Gaussian entropy, tells us how much two signals can be
+mean, as might seem natural, discards the relationship between the
+signals, while using the integration metric, defined as the Gaussian entropy, tells us how much two signals can be
 combined to form the third (see fig.\,\ref{fig:integration}). 
@@
 system. The functional-connectivity structure, or its representation in
-form of a correlation matrix, can thus be characterized via the
-integration and cross-talk of some of its subs-systems. This approach
+the form of a correlation matrix, can thus be characterized via the
+integration and cross-talk of some of its sub-systems. This approach
 gives a simplified representation with a small number of metrics that can
@@
 \begin{minipage}{.2\linewidth}
-    \includegraphics[width=\linewidth]{correlation_ex1.pdf}
+    \includegraphics[width=1.07\linewidth]{correlation_ex1.pdf}
 \end{minipage}%
@@
 \begin{minipage}{.033\linewidth}
+    \rule{0pt}{6.487\linewidth}%
     \includegraphics[width=\linewidth]{correlation_cmap.pdf}%
@@
 \begin{minipage}{.2\linewidth}
-    \includegraphics[width=\linewidth]{correlation_ex2.pdf}
+    \hspace*{-.07\linewidth}%
+    \includegraphics[width=1.07\linewidth]{correlation_ex2.pdf}
 \end{minipage}%
@@
 and $c$ as different from each other as possible, given $\rho_{ab} +
-\rho_{bc} + \rho{ac} = 1.35$; it thus has a small integration value. On
+\rho_{bc} + \rho_{ac} = 1.35$; it thus has a small integration value. On
 the opposite, for the matrix on the right, signal $b$ can almost be fully
@@
 
-\paragraph{Graph-topology metrics}
+\paragraph{Graph-topological metrics}
 %
@@
 as schizophrenia, are thought to have a global impact on brain
-connectivity \cite{liu2008,bassett2008}, the graph-topology metrics are
+connectivity \cite{liu2008,bassett2008}, the graph-topological metrics are
 promising markers to perform inter-subject comparison. Such an
@@
 beyond empirical correlation matrices, as discuss in the previous section.
-% CAMERON What about regional summary measures such as centrality??? Xinian's work
-% maybe a paragraph that covers ReHo, degree centrality, eigenvector centrality, pagerank etc...
 
@@
 
-Although predictive modeling techniques are well suited at measuring whether
+Although predictive modeling techniques are well suited for measuring whether
 information exists in the connectome about a phenotypic variable, they do
@@
 corresponding edge in the connectome. However,
-interpreting how the connections differs between classes or relate to a
+interpreting how the connections differ between classes or relate to a
 phenotypic variable can be more complicated given the multivariate nature
@@
 predictive modeling is used to identify candidate connections that are later
-tested in follow-on experiments better suited to elucidating their relationship
+tested in follow-up experiments better suited to elucidating their relationship
 to the variable of interest.
@@
 comparison, we would like to stress that while machine learning algorithms are
-powerful tools, they work best if they are provided with discriminant and
+powerful tools, they work best if they are provided with discriminanting and
 noiseless features. In other words, as with all other connectome comparison
@@
 also expressed in \cite{mcintosh2010}).
-% CAMERON should we mention follow on discussion from the first brain 
-% connectivity meeting
 
@@
 however, as George Box famously said, ``all models are wrong; some models
-are useful''. Depending on the question and the data at hand, the cursor
-should be set between complex models based on a bio-physical description,
+are useful''. Depending on the question and the data at hand, a trade-off 
+should be chosen between complex models based on a bio-physical description,
 and simple phenomenological models such as correlation matrices. In
@@
 Methodological challenges to functional-connectome-based group studies
-arise from the dimensionality and the of variability the connectome. With
+arise from the dimensionality and the variability of the connectome. With
 the current tools, inter-subject comparison of connectomes comprising
@@
 
+% Acknowledgments: Bertrand, Andreas, NiConnect
+
 {

### 2013-02-21 paper.tex
iter

@@
 mapping that enables statistically-controlled comparisons across subjects
-\cite{friston1995}, group-level analyses of functional connectivity still face
+\cite{friston1995}, group-level analysis of functional connectivity still face
 many open methodological challenges. Deriving a picture of a single subject's
@@
 signal fluctuations \cite{fox2005, lund2006}. More complex models account for
-spatial variation in noise by incorporating voxel specific regressors of
+spatial variation in noise by incorporating voxel-specific regressors of
 neighboring WM (ANATICOR \cite{jo2010}) or the top components from a
@@
 topological properties\footnote{In the neuroscience world, these
-descriptions are grouped under the terms of ``graph theoretical
+descriptions are grouped under the terms of ``graph-theoretical
 approaches'', however graph theory is an entire division of mathematics
@@
 predictive modeling to connectivity analysis was highlighted by the ADHD200
-Global Competition, in which the object was to identify a connectivity based
+Global Competition, in which the object was to identify a connectivity-based
 biomarker of ADHD \cite{adhd2002012}. Recent work has illustrated the utility
@@
 requirements \cite{cherkassky1998}, determined using an analytical approach
-\cite{cherkassky2004}, or optimized using a second level cross validation procedure
+\cite{cherkassky2004}, or optimized using a second-level cross validation procedure
 \cite{friedman2001}.

### 2013-02-24 paper.tex
Address more comments

@@
 	strategies for comparing them. This review aims to clarify links across
-	functional-connectivity methods and to expose different steps 
+	functional-connectivity methods as well as to expose different steps 
 	to perform a group study of functional connectomes.
@@
 While the notion of functional
-connectomics is often associated with the study of resting-state
+connectomics is often associated with the study of resting state
 \cite{biswal2010}, the methods presented in this paper are also relevant
@@
 well as ongoing activity, present in the absence of specific tasks or in the
-background during task and often studied in so-called \emph{resting-state}
+background during task and often studied in so-called \emph{resting state}
 experiments \cite{raichle2010}. Another important notion that arises from the
@@
 
-In addition to standard preprocessing performed for task based analysis
+In addition to standard preprocessing performed for task-based analysis
 (slice-timing correction, realignment, spatial normalization, and possibly
-smoothing), connectivity based analysis require additional denoising 
+smoothing), connectivity-based analysis require additional denoising 
 to separate intrinsic activity from confounding signals. This process involves
@@
 principal
-components analysis of WM signal (CompCor \cite{behzadi2007}). Head motion
+components analysis of high-variance signals (CompCor \cite{behzadi2007}). Head motion
 induced signal fluctuations are accounted for by incorporating movement
@@
 Filtering to remove high frequencies is often performed, based on the initial
-observation that fluctuations implicated in resting state functional
+observation that fluctuations implicated in resting-state functional
 connectivity are predominately slower than 0.1\,Hz \cite{cordes2001,biswal1995}.
@@
 	\cite{davey2012}.}.
+In addition, the recent developments of very rapid acquisition 
+protocols prevent aliasing of the physiological noise with the neural 
+signal and give access to more specific noise confounds than traditional
+low-TR sequences \cite{boyaciouglu2012}.
 
@@
 connectomes, features used in the predictive model correspond to bivariate
-measures of connectivity, or any of the previously discussed graph summary metrics.  
+measures of connectivity \cite{richiardi2011,dosenbach2010,shirer2012}, or any of the previously discussed graph
+summary metrics \cite{cecchi2009,ekman2012}.  
 %
@@
 assumptions\footnote{This is to be contrasted to Bayesian model
-comparison, which will give correct results only if the true generative
+comparison, which will give well-controlled results only if the true generative
 model is in the list of models compared. \cite{friston2012} argues that,
@@
 important to keep in mind that these approaches only test for
-self-consistence, as the Neyman-Pearson lemma requires that 
-the model likelihood describes the data well, which may not always be the
-case \cite{lohmann2012}.}.
+self-consistence, as the Neyman-Pearson lemma is established under the
+hypothesis that model used to define the test is indeed the 
+data-generating process
+\cite{neyman1933}, while in practice it is often the case that the model
+gives poor fits to the data \cite{lohmann2012}. Applying test procedures
+on different data than that used to fit the model, as in
+cross-validation, is much more resilient to modeling errors.}.
 

### 2013-02-24 paper.tex
Address most of reviewer 2's points

@@
 methods, such as ICA \cite{beckmann2004}, can unmix linear
-combinations of multiple effects and separate out overlapping spatial maps
-that capture functional networks or confounding effects. At high model
+combinations of multiple effects and separate out partially-overlapping
+spatial maps
+that capture functional networks or confounding effects, as for instance
+with the presence of vascular structure in functional networks. At high model
 order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
@@
 which the number of regions can be chosen based on the needs of the analysis at
-hand.
+hand. Finally, it is important to keep in mind that there is no
+universally better parcellation and associated number of regions. From a
+practical standpoint, these choices will depend on the task at hand, and
+more fundamentally, a good description of brain function should cover
+multiple scales. Given that it is not clear that an optimal parcellation
+can be identified from the sample size of a typical study, randomized
+parcellation, as used in structural connectomes \cite{zalesky2010a} or
+activation mapping \cite{varoquaux2012a}, may also be considered.
 
@@
 
-To study connectivity from \emph{evoked} activity with task-driven studies it
+Studying connectivity from \emph{evoked} activity with task-driven studies 
+it requires disambiguating task-specific connectivity effects from
+intrinsic connectivity mediated by shared neuromodulatory/task 
+inputs, anatomical pathways, \emph{etc}. In this regard, it
 can be beneficial to run a GLM-based first-level analysis, enforcing specificity
@@
 if, in a second-level analysis, an effect is detected on a connection
-that lies in a network of strongly connected nodes, the whole network is
+that lies in a network of strongly connected nodes, a large sub-network is
 likely to carry an effect. Thus, they adapt cluster-level inference to
@@
 self-consistence, as the Neyman-Pearson lemma is established under the
-hypothesis that model used to define the test is indeed the 
+hypothesis that the model used to define the test is indeed the 
 data-generating process
-\cite{neyman1933}, while in practice it is often the case that the model
+\cite{neyman1933}, while in practice it is often the case that this model
 gives poor fits to the data \cite{lohmann2012}. Applying test procedures

### 2013-02-24 paper.tex
Address more points

@@
 interpretation of each option, in order to match the method to the
-question.
-
-% Acknowledgments: Bertrand, Andreas, NiConnect
+question. Similarly, the idealized notion of an unique \emph{functional
+connectome} to describe connections in brain function is probably an
+utopia, and various connectomes should be considered in different
+settings, such as the study of varying phenotypic conditions, or that of
+on-going activity versus activity related to specific tasks.
+
+\subsection*{Acknowledgments}
+
+GV acknowledges funding from the NiConnect grant, as well as many
+insightful discussions with Andreas Kleinschmidt on on-going activity and
+Bertrand Thirion on statistical data processing.
 

### 2013-02-24 paper.tex
All comments addressed

@@
 % Define terms
+``Functional connectivity'' is defined as a measure of synchronization in 
+brain signals \cite{friston1994}. More generally, it is interesting as a 
+window on underlying synchrony in neural processes \cite{lee2003}.
 By ``functional connectome'', here we specifically denote a graph representing
@@
 \begin{figure}
-\includegraphics[width=.5\linewidth]{aal_atlas.pdf}%
+\includegraphics[width=.5\linewidth]{aal_atlas}%
 \hfill%
-\includegraphics[width=.5\linewidth]{ho_atlas.pdf}%
-
-\includegraphics[width=.5\linewidth]{sulci_atlas.pdf}%
+\includegraphics[width=.5\linewidth]{ho_atlas}%
+
+\includegraphics[width=.5\linewidth]{sulci_atlas}%
 \hfill%
-\includegraphics[width=.5\linewidth]{ncuts_atlas.pdf}%
-
-\includegraphics[width=.5\linewidth]{smith_atlas.pdf}%
+\includegraphics[width=.5\linewidth]{ncuts_atlas}%
+
+\includegraphics[width=.5\linewidth]{smith_atlas}%
 \hfill%
-\includegraphics[width=.5\linewidth]{msdl_atlas.pdf}%
+\includegraphics[width=.5\linewidth]{msdl_atlas}%
 
@@
 \begin{minipage}{.666\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_cov.pdf}%
+    \includegraphics[width=\linewidth]{group_emp_cov}%
     \raisebox{.606\linewidth}{%
@@
 \begin{minipage}{.33\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds.pdf}%
-
-    \includegraphics[width=\linewidth]{group_emp_cov_global_mean.pdf}%
+    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds}%
+
+    \includegraphics[width=\linewidth]{group_emp_cov_global_mean}%
 \end{minipage}%
@@
 \begin{minipage}{.666\linewidth}%
-    \includegraphics[width=\linewidth]{group_l21_prec.pdf}%
+    \includegraphics[width=\linewidth]{group_l21_prec}%
     \raisebox{.606\linewidth}{%
@@
 \begin{minipage}{.33\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_prec.pdf}%
-
-    \includegraphics[width=\linewidth]{group_l1_prec.pdf}%
+    \includegraphics[width=\linewidth]{group_emp_prec}%
+
+    \includegraphics[width=\linewidth]{group_l1_prec}%
 \end{minipage}%
@@
 \begin{figure}
-\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds.pdf}%
+\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds}%
 \hfill%
-\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean.pdf}%
+\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean}%
 
@@
 \hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53.pdf}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53}%
 \hspace*{.1ex}%
 \raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
+    \includegraphics[width=.0186\linewidth]{cmap_00}%
     \llap{
@@
 \hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53.pdf}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53}%
 \hspace*{.1ex}%
 \raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
+    \includegraphics[width=.0186\linewidth]{cmap_01}%
     \llap{
@@
 \hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53.pdf}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53}%
 \hspace*{.1ex}%
 \raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_00.pdf}%
+    \includegraphics[width=.0186\linewidth]{cmap_00}%
     \llap{
@@
 \hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53.pdf}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53}%
 \hspace*{.1ex}%
 \raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
+    \includegraphics[width=.0186\linewidth]{cmap_01}%
     \llap{
@@
 \hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub00.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub29.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub01.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub07.pdf}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub53.pdf}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub00}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub29}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub01}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub07}%
+\hspace*{-.2ex}%
+\includegraphics[width=.196\linewidth]{inter_subj/res_sub53}%
 \hspace*{.1ex}%
 \raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_01.pdf}%
+    \includegraphics[width=.0186\linewidth]{cmap_01}%
     \llap{
@@
 \begin{minipage}{.2\linewidth}
-    \includegraphics[width=1.07\linewidth]{correlation_ex1.pdf}
+    \includegraphics[width=1.07\linewidth]{correlation_ex1}
 \end{minipage}%
@@
     \rule{0pt}{6.487\linewidth}%
-    \includegraphics[width=\linewidth]{correlation_cmap.pdf}%
+    \includegraphics[width=\linewidth]{correlation_cmap}%
     \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
@@
     \hspace*{-.07\linewidth}%
-    \includegraphics[width=1.07\linewidth]{correlation_ex2.pdf}
+    \includegraphics[width=1.07\linewidth]{correlation_ex2}
 \end{minipage}%

### 2013-02-24 paper.tex
Forgotten acknowledgment

@@
 
+% For review: line numbers
+\usepackage[pagewise]{lineno}
+
 \biboptions{sort}
@@
 
+% Modification tracking
+\usepackage{xcolor}
+\usepackage[normalem]{ulem}
+\newcommand{\ADDED}[1]{\textcolor{blue}{\uline{#1}}}
+\newcommand{\DELETED}[1]{\textcolor{red}{\sout{#1}}}
+
+% Show the old version
+%\renewcommand{\ADDED}[1]{}
+%\renewcommand{\DELETED}[1]{#1}
+
+% Show the new version
+%\renewcommand{\ADDED}[1]{#1}
+%\renewcommand{\DELETED}[1]{}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
+% Show line numbers
+\linenumbers
+\linenumbersep 3pt\relax
+\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{black!50}}
 
@@
 
-GV acknowledges funding from the NiConnect grant, as well as many
-insightful discussions with Andreas Kleinschmidt on on-going activity and
-Bertrand Thirion on statistical data processing.
+GV acknowledges funding from the NiConnect grant and the Dynamic
+Diaschisis project DEQ20100318254 from \emph{Fondation pour la Recherche
+M\'edicale}, as well as many insightful discussions with Andreas
+Kleinschmidt on on-going activity and Bertrand Thirion on statistical
+data processing.
 

### 2013-02-25 paper.tex
Ready to be submitted
Add cameron's acknowledgements

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Modification tracking
@@
 \usepackage[normalem]{ulem}
-\newcommand{\ADDED}[1]{\textcolor{blue}{\uline{#1}}}
+\colorlet{markercolor}{purple!50!black}
+\newcommand{\ADDED}[1]{\textcolor{markercolor}{\uline{#1}}}
 \newcommand{\DELETED}[1]{\textcolor{red}{\sout{#1}}}
+
+% For highlighting changes for reviewer
+\usepackage{MnSymbol}
+\def\marker{%
+    \vadjust{{%
+	\llap{\smash{%
+	    \color{purple}%
+	    \scalebox{1.8}{$\filledmedtriangleright$}}\;}%
+    }}\hspace*{-.1ex}%
+}%
+\def\hl#1{\textcolor{markercolor}{%
+   \protect\marker%
+  #1%
+}}%
 
@@
 % Show line numbers
-\linenumbers
-\linenumbersep 3pt\relax
-\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{black!50}}
+%\linenumbers
+%\linenumbersep 3pt\relax
+%\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{black!50}}
 
@@
 % Define terms
-``Functional connectivity'' is defined as a measure of synchronization in 
+\hl{``Functional connectivity'' is defined as a measure of synchronization in 
 brain signals \cite{friston1994}. More generally, it is interesting as a 
-window on underlying synchrony in neural processes \cite{lee2003}.
+window on underlying synchrony in neural processes \cite{lee2003}.}
 By ``functional connectome'', here we specifically denote a graph representing
@@
 	\cite{davey2012}.}.
+\hl{%
 In addition, the recent developments of very rapid acquisition 
@@
 signal and give access to more specific noise confounds than traditional
-low-TR sequences \cite{boyaciouglu2012}.
+low-TR sequences \cite{boyaciouglu2012}.}
 
@@
 spatial maps
-that capture functional networks or confounding effects, as for instance
-with the presence of vascular structure in functional networks. At high model
+that capture functional networks or confounding effects, \hl{as for instance
+with the presence of vascular structure in functional networks}. At high model
 order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
@@
 which the number of regions can be chosen based on the needs of the analysis at
-hand. Finally, it is important to keep in mind that there is no
+hand. \hl{Finally, it is important to keep in mind that there is no
 universally better parcellation and associated number of regions. From a
@@
 parcellation, as used in structural connectomes \cite{zalesky2010a} or
-activation mapping \cite{varoquaux2012a}, may also be considered.
+activation mapping \cite{varoquaux2012a}, may also be considered.}
 
@@
 
-Studying connectivity from \emph{evoked} activity with task-driven studies 
+\hl{Studying connectivity from \emph{evoked} activity with task-driven studies 
 it requires disambiguating task-specific connectivity effects from
 intrinsic connectivity mediated by shared neuromodulatory/task 
-inputs, anatomical pathways, \emph{etc}. In this regard, it
+inputs, anatomical pathways, \emph{etc}. In this regard,} it
 can be beneficial to run a GLM-based first-level analysis, enforcing specificity
@@
 correlation matrix is computed on standardized (zero mean, unit variance) signals.}
-matrix (also called \emph{precision matrix} captures
+matrix \hl{(also called \emph{precision matrix})} captures
 partial correlations, removing the effect of other variables
@@
 
-% CAMERON I really like this section, but would change it slightly to reflect
-% that preprocessing has been moved to its own sectoin.
 There have been debates on whether to
@@
 if, in a second-level analysis, an effect is detected on a connection
-that lies in a network of strongly connected nodes, a large sub-network is
+that lies in a network of strongly connected nodes, a \hl{large
+sub-network} is
 likely to carry an effect. Thus, they adapt cluster-level inference to
@@
 connectomes, features used in the predictive model correspond to bivariate
-measures of connectivity \cite{richiardi2011,dosenbach2010,shirer2012}, or any of the previously discussed graph
-summary metrics \cite{cecchi2009,ekman2012}.  
+measures of connectivity \hl{\cite{richiardi2011,dosenbach2010,shirer2012}}, or any of the previously discussed graph
+summary metrics \hl{\cite{cecchi2009,ekman2012}}.
 %
@@
 however, as George Box famously said, ``all models are wrong; some models
-are useful''. Depending on the question and the data at hand, a trade-off 
-should be chosen between complex models based on a bio-physical description,
+are useful''. Depending on the question and the data at hand, \hl{a trade-off 
+should be chosen} between complex models based on a bio-physical description,
 and simple phenomenological models such as correlation matrices. In
@@
 assumptions\footnote{This is to be contrasted to Bayesian model
-comparison, which will give well-controlled results only if the true generative
+comparison, which will give \hl{well-controlled} results only if the true generative
 model is in the list of models compared. \cite{friston2012} argues that,
@@
 important to keep in mind that these approaches only test for
-self-consistence, as the Neyman-Pearson lemma is established under the
+self-consistence, \hl{as the Neyman-Pearson lemma is established under the
 hypothesis that the model used to define the test is indeed the 
@@
 on different data than that used to fit the model, as in
-cross-validation, is much more resilient to modeling errors.}.
+cross-validation, is much more resilient to modeling errors.}}.
 
@@
 interpretation of each option, in order to match the method to the
-question. Similarly, the idealized notion of an unique \emph{functional
+question. \hl{Similarly, the idealized notion of an unique \emph{functional
 connectome} to describe connections in brain function is probably an
@@
 settings, such as the study of varying phenotypic conditions, or that of
-on-going activity versus activity related to specific tasks.
+on-going activity versus activity related to specific tasks.}
 
@@
 Kleinschmidt on on-going activity and Bertrand Thirion on statistical
-data processing.
+data processing. RCC would like to acknowledge support by a NARSAD Young
+Investigator Grant from the Brain \& Behavior Research Foundation.
+The authors would like to thank the anonymous reviewers
+for their suggestions that improved the manuscript.
 

### 2013-02-26 paper.tex
Edits to revisions

@@
 brain signals \cite{friston1994}. More generally, it is interesting as a 
-window on underlying synchrony in neural processes \cite{lee2003}.}
+window on underlying synchrony on neural processes \cite{lee2003}.}
 By ``functional connectome'', here we specifically denote a graph representing
@@
 \hl{Studying connectivity from \emph{evoked} activity with task-driven studies 
-it requires disambiguating task-specific connectivity effects from
+requires disambiguating task-specific connectivity effects from
 intrinsic connectivity mediated by shared neuromodulatory/task 
@@
 (fig.\,\ref{fig:correlation_matrices} upper right and lower right), on
-inverse covariance it only changes very slightly the resulting matrices
+inverse covariance it only changes the resulting matrices very slightly 
 (fig.\,\ref{fig:icov_regressors}).
@@
 The authors would like to thank the anonymous reviewers
-for their suggestions that improved the manuscript.
+for their suggestions, which improved the manuscript.
 

### 2013-03-26 paper.tex
Remove highlighting markers

--- 2013-02-24 paper.tex
@@
 brain signals \cite{friston1994}. More generally, it is interesting as a 
-window on underlying synchrony in neural processes \cite{lee2003}.
+window on underlying synchrony on neural processes \cite{lee2003}.
 By ``functional connectome'', here we specifically denote a graph representing
@@
 Studying connectivity from \emph{evoked} activity with task-driven studies 
-it requires disambiguating task-specific connectivity effects from
+requires disambiguating task-specific connectivity effects from
 intrinsic connectivity mediated by shared neuromodulatory/task 
@@
 correlation matrix is computed on standardized (zero mean, unit variance) signals.}
-matrix (also called \emph{precision matrix} captures
+matrix (also called \emph{precision matrix}) captures
 partial correlations, removing the effect of other variables
@@
 (fig.\,\ref{fig:correlation_matrices} upper right and lower right), on
-inverse covariance it only changes very slightly the resulting matrices
+inverse covariance it only changes the resulting matrices very slightly 
 (fig.\,\ref{fig:icov_regressors}).
 
-% CAMERON I really like this section, but would change it slightly to reflect
-% that preprocessing has been moved to its own sectoin.
 There have been debates on whether to
@@
 if, in a second-level analysis, an effect is detected on a connection
-that lies in a network of strongly connected nodes, a large sub-network is
+that lies in a network of strongly connected nodes, a large
+sub-network is
 likely to carry an effect. Thus, they adapt cluster-level inference to
@@
 Kleinschmidt on on-going activity and Bertrand Thirion on statistical
-data processing.
+data processing. RCC would like to acknowledge support by a NARSAD Young
+Investigator Grant from the Brain \& Behavior Research Foundation.
+The authors would like to thank the anonymous reviewers
+for their suggestions, which improved the manuscript.
 

### 2013-03-26 paper.tex
Use the latex preview package to avoid having latex hacks for figures

@@
 \def\slantfrac#1#2{\kern.1em^{#1}\kern-.1em/\kern-.1em_{#2}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% For the final version: to output PDF figures from latex
+%\usepackage[tightpage,active]{preview}
 
@@
 \begin{figure}
-\includegraphics[width=.5\linewidth]{aal_atlas}%
-\hfill%
-\includegraphics[width=.5\linewidth]{ho_atlas}%
-
-\includegraphics[width=.5\linewidth]{sulci_atlas}%
-\hfill%
-\includegraphics[width=.5\linewidth]{ncuts_atlas}%
-
-\includegraphics[width=.5\linewidth]{smith_atlas}%
-\hfill%
-\includegraphics[width=.5\linewidth]{msdl_atlas}%
+%PRE%\begin{preview}
+%PRE%\includegraphics[width=.5\linewidth]{aal_atlas}%
+%PRE%\hfill%
+%PRE%\includegraphics[width=.5\linewidth]{ho_atlas}%
+%PRE%
+%PRE%\includegraphics[width=.5\linewidth]{sulci_atlas}%
+%PRE%\hfill%
+%PRE%\includegraphics[width=.5\linewidth]{ncuts_atlas}%
+%PRE%
+%PRE%\includegraphics[width=.5\linewidth]{smith_atlas}%
+%PRE%\hfill%
+%PRE%\includegraphics[width=.5\linewidth]{msdl_atlas}%
+%PRE%\end{preview}
+\includegraphics[width=\linewidth]{pg_0001}%
 
@@
 \begin{figure}
-\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
-{\color{black!70}\fbox{#1}\color{black}}}%
-\begin{minipage}{.666\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_cov}%
-    \raisebox{.606\linewidth}{%
-	\hspace*{-.462\linewidth}%
-	\photoframe{%
-	%\setlength\fboxsep{1pt}%
-	\colorbox{white}{%
-	\raisebox{.003\linewidth}{%
-	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_labels}}%
-	\rule{0pt}{.387\linewidth}%
-	}}%
-    }
-\end{minipage}%
-\hspace*{1pt}%
-\begin{minipage}{.33\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds}%
-
-    \includegraphics[width=\linewidth]{group_emp_cov_global_mean}%
-\end{minipage}%
+%PRE%\begin{preview}
+%PRE%\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
+%PRE%{\color{black!70}\fbox{#1}\color{black}}}%
+%PRE%\begin{minipage}{.666\linewidth}%
+%PRE%    \includegraphics[width=\linewidth]{group_emp_cov}%
+%PRE%    \raisebox{.606\linewidth}{%
+%PRE%	\hspace*{-.462\linewidth}%
+%PRE%	\photoframe{%
+%PRE%	%\setlength\fboxsep{1pt}%
+%PRE%	\colorbox{white}{%
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \includegraphics[width=.455\linewidth]{group_emp_cov_3d_labels}}%
+%PRE%	\rule{0pt}{.387\linewidth}%
+%PRE%	}}%
+%PRE%    }
+%PRE%\end{minipage}%
+%PRE%\hspace*{1pt}%
+%PRE%\begin{minipage}{.33\linewidth}%
+%PRE%    \includegraphics[width=\linewidth]{group_emp_cov_no_confounds}%
+%PRE%
+%PRE%    \includegraphics[width=\linewidth]{group_emp_cov_global_mean}%
+%PRE%\end{minipage}%
+%PRE%\end{preview}
+\includegraphics[width=\linewidth]{pg_0002}%
 
@@
 \begin{figure}
-\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
-{\color{black!70}\fbox{#1}\color{black}}}%
-\begin{minipage}{.666\linewidth}%
-    \includegraphics[width=\linewidth]{group_l21_prec}%
-    \raisebox{.606\linewidth}{%
-	\hspace*{-.462\linewidth}%
-	\photoframe{%
-	%\setlength\fboxsep{1pt}%
-	\colorbox{white}{%
-	\raisebox{.003\linewidth}{%
-	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_labels}}%
-	\rule{0pt}{.387\linewidth}%
-	}}%
-    }
-\end{minipage}%
-\hspace*{1pt}%
-\begin{minipage}{.33\linewidth}%
-    \includegraphics[width=\linewidth]{group_emp_prec}%
-
-    \includegraphics[width=\linewidth]{group_l1_prec}%
-\end{minipage}%
+%PRE%\begin{preview}
+%PRE%\newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
+%PRE%{\color{black!70}\fbox{#1}\color{black}}}%
+%PRE%\begin{minipage}{.666\linewidth}%
+%PRE%    \includegraphics[width=\linewidth]{group_l21_prec}%
+%PRE%    \raisebox{.606\linewidth}{%
+%PRE%	\hspace*{-.462\linewidth}%
+%PRE%	\photoframe{%
+%PRE%	%\setlength\fboxsep{1pt}%
+%PRE%	\colorbox{white}{%
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \includegraphics[width=.455\linewidth]{group_l21_prec_3d_labels}}%
+%PRE%	\rule{0pt}{.387\linewidth}%
+%PRE%	}}%
+%PRE%    }
+%PRE%\end{minipage}%
+%PRE%\hspace*{1pt}%
+%PRE%\begin{minipage}{.33\linewidth}%
+%PRE%    \includegraphics[width=\linewidth]{group_emp_prec}%
+%PRE%
+%PRE%    \includegraphics[width=\linewidth]{group_l1_prec}%
+%PRE%\end{minipage}%
+%PRE%\end{preview}
+\includegraphics[width=\linewidth]{pg_0003}%
 
@@
 \begin{figure}
-\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds}%
-\hfill%
-\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean}%
+%PRE%\begin{preview}
+%PRE%\includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds}%
+%PRE%\hfill%
+%PRE%\includegraphics[height=.499\linewidth]{group_l21_prec_global_mean}%
+%PRE%\end{preview}
+\includegraphics[width=\linewidth]{pg_0004}%
 
@@
 \begin{figure}
-\hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53}%
-\hspace*{.1ex}%
-\raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_00}%
-    \llap{
-	\raisebox{.003\linewidth}{%
-	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
-    }%
-    \llap{
-	\raisebox{.17\linewidth}{%
-	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
-    }%
-}%
-\llap{\rlap{
-    \setlength\fboxsep{1pt}%
-    \raisebox{.16\linewidth}{%
-	\colorbox{black!10}{%
-	    \sffamily\small\textbf{a}. Correlation matrices}}%
-	}%
-    \hspace*{.993\linewidth}%
-}
-
-\hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53}%
-\hspace*{.1ex}%
-\raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_01}%
-    \llap{
-	\raisebox{.003\linewidth}{%
-	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
-    }%
-    \llap{
-	\raisebox{.168\linewidth}{%
-	    \bfseries\tiny 4\hspace*{.1ex}}%
-    }%
-}%
-\llap{\rlap{
-    \setlength\fboxsep{1pt}%
-    \raisebox{.16\linewidth}{%
-	\colorbox{black!10}{%
-	    \sffamily\small\textbf{b}. Z score on difference}}%
-	}%
-    \hspace*{.993\linewidth}%
-}
-
-\hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53}%
-\hspace*{.1ex}%
-\raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_00}%
-    \llap{
-	\raisebox{.003\linewidth}{%
-	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
-    }%
-    \llap{
-	\raisebox{.17\linewidth}{%
-	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
-    }%
-}%
-\llap{\rlap{
-    \setlength\fboxsep{1pt}%
-    \raisebox{.16\linewidth}{%
-	\colorbox{black!10}{%
-	    \sffamily\small\textbf{c}. Inverse-covariance matrices}}%
-	}%
-    \hspace*{.993\linewidth}%
-}
-
-\hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53}%
-\hspace*{.1ex}%
-\raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_01}%
-    \llap{
-	\raisebox{.003\linewidth}{%
-	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
-    }%
-    \llap{
-	\raisebox{.168\linewidth}{%
-	    \bfseries\tiny 4\hspace*{.1ex}}%
-    }%
-}%
-\llap{\rlap{
-    \setlength\fboxsep{1pt}%
-    \raisebox{.16\linewidth}{%
-	\colorbox{black!10}{%
-	    \sffamily\small\textbf{d}. Z score on inverse-covariance}}%
-	}%
-    \hspace*{.993\linewidth}%
-}
-
-\hspace*{.5ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub00}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub29}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub01}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub07}%
-\hspace*{-.2ex}%
-\includegraphics[width=.196\linewidth]{inter_subj/res_sub53}%
-\hspace*{.1ex}%
-\raisebox{.005\linewidth}{%
-    \includegraphics[width=.0186\linewidth]{cmap_01}%
-    \llap{
-	\raisebox{.003\linewidth}{%
-	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
-    }%
-    \llap{
-	\raisebox{.168\linewidth}{%
-	    \bfseries\tiny 4\hspace*{.1ex}}%
-    }%
-}%
-\llap{\rlap{
-    \setlength\fboxsep{1pt}%
-    \raisebox{.16\linewidth}{%
-	\colorbox{black!10}{%
-	    \sffamily\small\textbf{e}. Z score on residuals \scriptsize
-		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
-	}%
-    \hspace*{.993\linewidth}%
-}
+%PRE%\begin{preview}
+%PRE%\hspace*{.5ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub00}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub29}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub01}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub07}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/cov_sub53}%
+%PRE%\hspace*{.1ex}%
+%PRE%\raisebox{.005\linewidth}{%
+%PRE%    \includegraphics[width=.0186\linewidth]{cmap_00}%
+%PRE%    \llap{
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
+%PRE%    }%
+%PRE%    \llap{
+%PRE%	\raisebox{.17\linewidth}{%
+%PRE%	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
+%PRE%    }%
+%PRE%}%
+%PRE%\llap{\rlap{
+%PRE%    \setlength\fboxsep{1pt}%
+%PRE%    \raisebox{.16\linewidth}{%
+%PRE%	\colorbox{black!10}{%
+%PRE%	    \sffamily\small\textbf{a}. Correlation matrices}}%
+%PRE%	}%
+%PRE%    \hspace*{.993\linewidth}%
+%PRE%}
+%PRE%
+%PRE%
+%PRE%\hspace*{.5ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub00}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub29}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub01}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub07}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_sub53}%
+%PRE%\hspace*{.1ex}%
+%PRE%\raisebox{.005\linewidth}{%
+%PRE%    \includegraphics[width=.0186\linewidth]{cmap_01}%
+%PRE%    \llap{
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
+%PRE%    }%
+%PRE%    \llap{
+%PRE%	\raisebox{.168\linewidth}{%
+%PRE%	    \bfseries\tiny 4\hspace*{.1ex}}%
+%PRE%    }%
+%PRE%}%
+%PRE%\llap{\rlap{
+%PRE%    \setlength\fboxsep{1pt}%
+%PRE%    \raisebox{.16\linewidth}{%
+%PRE%	\colorbox{black!10}{%
+%PRE%	    \sffamily\small\textbf{b}. Z score on difference}}%
+%PRE%	}%
+%PRE%    \hspace*{.993\linewidth}%
+%PRE%}
+%PRE%
+%PRE%\hspace*{.5ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub00}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub29}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub01}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub07}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/prec_sub53}%
+%PRE%\hspace*{.1ex}%
+%PRE%\raisebox{.005\linewidth}{%
+%PRE%    \includegraphics[width=.0186\linewidth]{cmap_00}%
+%PRE%    \llap{
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \bfseries\tiny\color{white} -\!1\hspace*{-.2ex}}%
+%PRE%    }%
+%PRE%    \llap{
+%PRE%	\raisebox{.17\linewidth}{%
+%PRE%	    \bfseries\tiny\color{white} 1\hspace*{.1ex}}%
+%PRE%    }%
+%PRE%}%
+%PRE%\llap{\rlap{
+%PRE%    \setlength\fboxsep{1pt}%
+%PRE%    \raisebox{.16\linewidth}{%
+%PRE%	\colorbox{black!10}{%
+%PRE%	    \sffamily\small\textbf{c}. Inverse-covariance matrices}}%
+%PRE%	}%
+%PRE%    \hspace*{.993\linewidth}%
+%PRE%}
+%PRE%
+%PRE%\hspace*{.5ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub00}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub29}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub01}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub07}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/z_score_prec_sub53}%
+%PRE%\hspace*{.1ex}%
+%PRE%\raisebox{.005\linewidth}{%
+%PRE%    \includegraphics[width=.0186\linewidth]{cmap_01}%
+%PRE%    \llap{
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
+%PRE%    }%
+%PRE%    \llap{
+%PRE%	\raisebox{.168\linewidth}{%
+%PRE%	    \bfseries\tiny 4\hspace*{.1ex}}%
+%PRE%    }%
+%PRE%}%
+%PRE%\llap{\rlap{
+%PRE%    \setlength\fboxsep{1pt}%
+%PRE%    \raisebox{.16\linewidth}{%
+%PRE%	\colorbox{black!10}{%
+%PRE%	    \sffamily\small\textbf{d}. Z score on inverse-covariance}}%
+%PRE%	}%
+%PRE%    \hspace*{.993\linewidth}%
+%PRE%}
+%PRE%
+%PRE%
+%PRE%
+%PRE%\hspace*{.5ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub00}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub29}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub01}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub07}%
+%PRE%\hspace*{-.2ex}%
+%PRE%\includegraphics[width=.196\linewidth]{inter_subj/res_sub53}%
+%PRE%\hspace*{.1ex}%
+%PRE%\raisebox{.005\linewidth}{%
+%PRE%    \includegraphics[width=.0186\linewidth]{cmap_01}%
+%PRE%    \llap{
+%PRE%	\raisebox{.003\linewidth}{%
+%PRE%	    \bfseries\tiny -\!\hspace*{-.1ex}4\hspace*{-.1ex}}%
+%PRE%    }%
+%PRE%    \llap{
+%PRE%	\raisebox{.168\linewidth}{%
+%PRE%	    \bfseries\tiny 4\hspace*{.1ex}}%
+%PRE%    }%
+%PRE%}%
+%PRE%\llap{\rlap{
+%PRE%    \setlength\fboxsep{1pt}%
+%PRE%    \raisebox{.16\linewidth}{%
+%PRE%	\colorbox{black!10}{%
+%PRE%	    \sffamily\small\textbf{e}. Z score on residuals \scriptsize
+%PRE%		\raisebox{.2ex}{\cite{varoquaux2010b}}}}%
+%PRE%	}%
+%PRE%    \hspace*{.993\linewidth}%
+%PRE%}
+%PRE%\end{preview}
+\includegraphics[width=\linewidth]{pg_0005}%
 
@@
 \begin{figure}
-\hspace*{2ex}%
-\begin{minipage}{.19\linewidth}
-    \center\sffamily
-    {\small Integration:}
-
-    0.554
-\end{minipage}%
-\begin{minipage}{.2\linewidth}
-    \includegraphics[width=1.07\linewidth]{correlation_ex1}
-\end{minipage}%
-\hfill%
-\begin{minipage}{.033\linewidth}
-    \rule{0pt}{6.487\linewidth}%
-    \includegraphics[width=\linewidth]{correlation_cmap}%
-    \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
-    \llap{\raisebox{10.1ex}{\scriptsize\sffamily\bfseries\color{white} 1}%
-	    \hspace*{.54ex}}
-\end{minipage}%
-\hfill%
-\begin{minipage}{.2\linewidth}
-    \hspace*{-.07\linewidth}%
-    \includegraphics[width=1.07\linewidth]{correlation_ex2}
-\end{minipage}%
-\begin{minipage}{.19\linewidth}
-    \center\sffamily
-    {\small Integration:}
-
-    2.422
-\end{minipage}%
-\hspace*{2ex}%
+%PRE%\begin{preview}
+%PRE%\hspace*{2ex}%
+%PRE%\begin{minipage}{.19\linewidth}
+%PRE%    \center\sffamily
+%PRE%    {\small Integration:}
+%PRE%
+%PRE%    0.554
+%PRE%\end{minipage}%
+%PRE%\begin{minipage}{.2\linewidth}
+%PRE%    \includegraphics[width=1.07\linewidth]{correlation_ex1}
+%PRE%\end{minipage}%
+%PRE%\hfill%
+%PRE%\begin{minipage}{.033\linewidth}
+%PRE%    \rule{0pt}{6.487\linewidth}%
+%PRE%    \includegraphics[width=\linewidth]{correlation_cmap}%
+%PRE%    \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
+%PRE%    \llap{\raisebox{10.1ex}{\scriptsize\sffamily\bfseries\color{white} 1}%
+%PRE%	    \hspace*{.54ex}}
+%PRE%\end{minipage}%
+%PRE%\hfill%
+%PRE%\begin{minipage}{.2\linewidth}
+%PRE%    \hspace*{-.07\linewidth}%
+%PRE%    \includegraphics[width=1.07\linewidth]{correlation_ex2}
+%PRE%\end{minipage}%
+%PRE%\begin{minipage}{.19\linewidth}
+%PRE%    \center\sffamily
+%PRE%    {\small Integration:}
+%PRE%
+%PRE%    2.422
+%PRE%\end{minipage}%
+%PRE%\hspace*{2ex}%
+%PRE%\end{preview}
+\includegraphics[width=\linewidth]{pg_0006}
 

### 2013-03-26 paper.tex
Make the paper suitable for compilation in postscript
A few typos

--- 2013-03-26 paper.tex
@@
 % End kindle
+\usepackage{graphicx}
 \usepackage{amsmath,amsfonts,amssymb}
@@
 \def\slantfrac#1#2{\kern.1em^{#1}\kern-.1em/\kern-.1em_{#2}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% For the final version: to output PDF figures from latex
+\newif\iffinal
+\finaltrue
+%\finalfalse
+\iffinal\else
+\usepackage[tightpage,active]{preview}
+\fi
 
@@
 \begin{figure}
+\iffinal
+    % Final version
+    \includegraphics[width=\linewidth]{pg_0001}%
+\else
+    % Commented on figure generation
+    \begin{preview}
     \includegraphics[width=.5\linewidth]{aal_atlas}%
@@
     \includegraphics[width=.5\linewidth]{msdl_atlas}%
+    \end{preview}
+\fi
 
@@
 \begin{figure}
+\iffinal
+    % Final version
+    \includegraphics[width=\linewidth]{pg_0002}%
+\else
+    % Commented out figure generation
+    \begin{preview}
     \newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
@@
     \end{minipage}%
+    \end{preview}
+\fi
 
@@
 \begin{figure}
+\iffinal
+    % Final version
+    \includegraphics[width=\linewidth]{pg_0003}%
+\else
+    % Commented out figure generation
+    \begin{preview}
     \newcommand{\photoframe}[1]{\setlength\fboxsep{0pt}%
@@
 \begin{figure}
+\iffinal
+    % Final version
+    \includegraphics[width=\linewidth]{pg_0004}%
+\else
+    % Commented out figure generation
+    \begin{preview}
     \includegraphics[height=.499\linewidth]{group_l21_prec_no_confounds}%
@@
     \includegraphics[height=.499\linewidth]{group_l21_prec_global_mean}%
+    \end{preview}
+\fi
 
@@
 \begin{figure}
+\iffinal
+    % Final version
+    \includegraphics[width=\linewidth]{pg_0005}%
+\else
+    % Commented out figure generation
+    \begin{preview}
     \hspace*{.5ex}%
@@
     }
+    \end{preview}
+\fi
 
@@
 \begin{figure}
+\iffinal
+    % Final version
+    \includegraphics[width=\linewidth]{pg_0006}
+\else
+    % Commented out figure generation
+    \begin{preview}
     \hspace*{2ex}%
@@
     \hspace*{2ex}%
+    \end{preview}
+\fi
 
@@
 and computer science that is concerned with much more than topology of
-random graphs.} that are characteristic of small-word networks
+random graphs.} that are characteristic of small-world networks
 \cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
@@
 specific to brain function: correlation matrices display
-small-word properties such as local clustering by construction. Indeed, if two
+small-world properties such as local clustering by construction. Indeed, if two
 nodes are strongly correlated to a third, they are highly likely to be
@@
 but also for controlled recovery of brain functional connectivity going
-beyond empirical correlation matrices, as discuss in the previous section.
+beyond empirical correlation matrices, as discussed in the previous section.
 
@@
 test. 
-Additionally modern predictive modeling techniques draw from the
+Additionally, modern predictive modeling techniques draw from the
 statistical learning literature, which specifically addresses
